---
title: "GEDI"
author: "Louis Goodall"
date: "2025-05-27"
output: pdf_document
---

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(rGEDI)
library(lidR)
library(pbmcapply)
library(gstat)
library(educate)
library(minpack.lm)
library(lubridate)
library(exactextractr)
library(ellipse)
library(caret)
library(randomForest)
library(glcm)
library(CAST)
library(mgcv)
library(mclust)
#library(blockCV)
#library(cluster)
#library(factoextra)
#library(ConsensusClusterPlus)

library(segmented)

library(pls)

BWCA.shp <- st_read("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/BWCA/boundary_waters_canoe_area_wilderness.shp") %>%
  st_transform(., crs = "epsg:4326")
fortypcdBWCA_UTM <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/TreeMap/fortypcdBWCA.tif") %>%
  project(., "epsg:26915", method = "near", res = c(30,30))
options(scipen = 999)
templateRaster <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/B1_p10_2026_01_02_11_01_35.tif')
gc()


```

# GEDI 1B

```{r}
# For loop to process all the GEDI_1B waveforms as a sf dataframe and then bind into
# one large sfdf. Write out as a shapefile. Saves SO much data
directory1B <- "/Volumes/Crucial X6/GEDI/GEDI 1B"
gediFiles <- list.files(path = directory1B)
gedi1BList <- list()

for (i in seq_along(gediFiles)) {
  gedi1B <- readLevel1B(level1Bpath = file.path(directory1B, gediFiles[i]))
  # gedi1B <- getLevel1BGeo(level1b = gedi1B, select = c("elevation_bin0"))   # IT'S PROBABLY THIS FILTERING OUT OTHER COLUMNS
  gedi1B <- getLevel1BGeo(level1b = gedi1B)
  gedi1B$shot_number <- as.character(gedi1B$shot_number)
  gedi1B$ID <- gediFiles[i]
  dateTimeCode <- regmatches(gedi1B$ID, regexpr("20\\d{11}", gedi1B$ID))
  year <- substr(dateTimeCode, 1, 4)
  doy <- substr(dateTimeCode, 5, 7)
  gedi1B$Date <- as.Date(as.integer(doy) - 1, origin = paste0(year, "-01-01"))
  gedi1B <- gedi1B %>% dplyr::select(-ID)
  # gedi1B <- st_as_sf(gedi1B, coords = c("longitude_bin0", "latitude_bin0"), crs = "epsg:4326")
  gedi1BList[[i]] <- gedi1B
}

gedi1BAll <- do.call(rbind, gedi1BList)

# st_write(gedi1BAll,
#          dsn = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/BWCA/GEDI1B/gedi1BAll.shp")

names(gedi1BAll)

# x <- st_read("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/BWCA/GEDI1B/gedi1BAll.shp")
# 
# names(x)
```

# GEDI 2A

```{r}
directory2A <- '/Volumes/Crucial X6/GEDI/GEDI 2A'
gediFiles <- list.files(path = directory2A)
gedi2AList <- list()

for (i in seq_along(gediFiles)) {
  gedi2A <- readLevel2A(level2Apath = file.path(directory2A, gediFiles[i]))
  gedi2A <- getLevel2AM(level2a = gedi2A)
  gedi2A$shot_number <- as.character(gedi2A$shot_number)
  gedi2A$ID <- gediFiles[i]
  dateTimeCode <- regmatches(gedi2A$ID, regexpr("20\\d{11}", gedi2A$ID))
  year <- substr(dateTimeCode, 1, 4)
  doy <- substr(dateTimeCode, 5, 7)
  gedi2A$Date <- as.Date(as.integer(doy) - 1, origin = paste0(year, "-01-01"))
  gedi2A <- gedi2A %>% select(-ID)
  # gedi2A <- st_as_sf(gedi2A, coords = c("lon_lowestmode", "lat_lowestmode"), crs = "epsg:4326")
  gedi2AList[[i]] <- gedi2A
}

gedi2AAll <- do.call(rbind, gedi2AList)
gedi2AAll <- gedi2AAll %>% filter(quality_flag == 1)

# st_write(gedi2AAll,
#          dsn = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/BWCA/GEDI2A/gedi2AAll.shp")

y <- st_read("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/BWCA/GEDI2A/gedi2AAll.shp")

names(y)
```

# GEDI 2B

```{r}
directory2B <- '/Volumes/Crucial X6/GEDI/GEDI 2B'
gediFiles <- list.files(path = directory2B)
gedi2BList <- list()

dropList <- c("GEDI02_B_2022089212114_O18672_02_T00721_02_003_01_V002_subsetted.h5",
              "GEDI02_B_2022146024621_O19544_03_T10057_02_003_01_V002_subsetted.h5",
              "GEDI02_B_2022158180539_O19740_02_T04990_02_003_01_V002_subsetted.h5",
              "GEDI02_B_2022173153335_O19971_03_T09965_02_003_02_V002_subsetted.h5",
              "GEDI02_B_2022193042801_O20274_02_T02144_02_003_02_V002_subsetted.h5",
              "GEDI02_B_2022219175619_O20686_02_T10682_02_003_01_V002_subsetted.h5",
              "GEDI02_B_2022292124902_O21815_02_T02052_02_003_01_V002_subsetted.h5",
              "GEDI02_B_2024139003534_O30756_02_T10284_02_004_01_V002_subsetted.h5",
              "GEDI02_B_2024170155920_O31247_03_T02942_02_004_01_V002_subsetted.h5",
              "GEDI02_B_2024217174101_O31977_02_T04990_02_004_02_V002_subsetted.h5",
              "GEDI02_B_2024235141708_O32254_03_T07211_02_004_02_V002_subsetted.h5",
              "GEDI02_B_2024290161126_O33108_03_T04273_02_004_01_V002_subsetted.h5")

for (i in seq_along(gediFiles)) {
  fileName <- gediFiles[i]
  if (fileName %in% dropList) {
    next
  }
  gedi2B <- readLevel2B(level2Bpath = file.path(directory2B, gediFiles[i]))
  gedi2B_PAI <- getLevel2BPAIProfile(level2b = gedi2B)
  gedi2B_PAI$shot_number <- as.character(gedi2B_PAI$shot_number)
  gedi2B_PAI$ID <- gediFiles[i]
  dateTimeCode <- regmatches(gedi2B_PAI$ID, regexpr("20\\d{11}", gedi2B_PAI$ID))
  year <- substr(dateTimeCode, 1, 4)
  doy <- substr(dateTimeCode, 5, 7)
  gedi2B_PAI$Date <- as.Date(as.integer(doy) - 1, origin = paste0(year, "-01-01"))
  gedi2B_PAI <- gedi2B_PAI %>% select(-ID)
  gedi2B_PAVD <- getLevel2BPAVDProfile(level2b = gedi2B)
  gedi2B_PAVD$shot_number <- as.character(gedi2B_PAVD$shot_number)
  gedi2B_PAVD$ID <- gediFiles[i]
  dateTimeCode <- regmatches(gedi2B_PAVD$ID, regexpr("20\\d{11}", gedi2B_PAVD$ID))
  year <- substr(dateTimeCode, 1, 4)
  doy <- substr(dateTimeCode, 5, 7)
  gedi2B_PAVD$Date <- as.Date(as.integer(doy) - 1, origin = paste0(year, "-01-01"))
  gedi2B_PAVD <- gedi2B_PAVD %>% select(-ID)
  gedi2B_BVPM <- getLevel2BVPM(level2b = gedi2B)
  gedi2B_BVPM$shot_number <- as.character(gedi2B_BVPM$shot_number)
  gedi2B_BVPM$ID <- gediFiles[i]
  dateTimeCode <- regmatches(gedi2B_BVPM$ID, regexpr("20\\d{11}", gedi2B_BVPM$ID))
  year <- substr(dateTimeCode, 1, 4)
  doy <- substr(dateTimeCode, 5, 7)
  gedi2B_BVPM$Date <- as.Date(as.integer(doy) - 1, origin = paste0(year, "-01-01"))
  gedi2B_BVPM <- gedi2B_BVPM %>% select(-ID)
  gedi2B <- inner_join(gedi2B_PAI, gedi2B_PAVD, by = c("shot_number", "beam", "algorithmrun_flag",
                                                       "l2b_quality_flag", "delta_time", "lat_lowestmode",
                                                       "lon_lowestmode", "elev_highestreturn", "elev_lowestmode",
                                                       "height_lastbin", "height_bin0"))
  gedi2B <- inner_join(gedi2B, gedi2B_BVPM, by = c("shot_number", "algorithmrun_flag", "l2b_quality_flag", "delta_time",
                                         "elev_highestreturn", "elev_lowestmode"))
  gedi2BList[[i]] <- gedi2B
}


gedi2BAll <- do.call(rbind, gedi2BList)
gedi2BAll <- gedi2BAll %>% filter(l2b_quality_flag == 1)


```

# Data wrangling

```{r}
# Combine all the data into one big GEDI dataframe
gediAll <- inner_join(gedi1BAll, gedi2AAll, by = c("shot_number", "Date"))
gediAll <- inner_join(gediAll, gedi2BAll, by = c("shot_number", "delta_time", "sensitivity", "solar_elevation", "lat_lowestmode", "lon_lowestmode", "elev_highestreturn", "elev_lowestmode", "Date"))

# Clean up the dataframe a bit
gediAll <- gediAll %>%
  select(-beam.y, -beam.x, -latitude_lastbin.y, -latitude_bin0.y,
         -longitude_bin0.y, -longitude_lastbin.y, -rh100.y,
         -Date.x, -Date.y) %>%
  rename("latitude_bin0" = "latitude_bin0.x",
         "latitude_lastbin" = "latitude_lastbin.x",
         "longitude_bin0" = "longitude_bin0.x",
         "longitude_lastbin" = "longitude_lastbin.x",
         "rh100" = "rh100.x")

# write_csv(gediAll, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/GEDI_ALL/gediAll.csv")

gediAll <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/GEDI_ALL/gediAll.csv")

# Turn into an sf object
gediAll_sf <- st_as_sf(gediAll, coords = c("longitude_lastbin", "latitude_lastbin"), crs = "epsg:4326")


class(gediAll_sf$geometry)
# rm(gediAll, gediAll_sf)
```

# UNDERSTORY LADDER FUELS STUFF

```{r}
gediAll_sf %>%
  filter(rh100 >= 5,
         sensitivity >= 0.9,
         format(Date, "%m-%d") >= "04-30" &
         format(Date, "%m-%d") <= "08-06")


# MODIS MCD12Q2.006 Land Cover Dynamics 500m
# This product is used to determine the leaf up and leaf out dates for the BWCA in days since
# Jan 1 1970. This is the year 2023. Can be changed in the future for a more recent representation
sos <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/Greenup_1_2025_08_03_15_37_26.tif')
eos <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/Senescence_1_2025_08_03_15_37_36.tif')
los <- eos - sos

# Convert to a dataframe and then get the mode for leaf up and leaf down. Then get the julian date for that year
# This is so that we can filter for GEDI shots that are within these dates
sosNoZeros <- sos %>% as.data.frame() %>% filter(Greenup_1 > 0)
eosNoZeros <- eos %>% as.data.frame() %>% filter(Senescence_1 > 0)
sosMode <- DescTools::Mode(sosNoZeros$Greenup_1)[1]
eosMode <- DescTools::Mode(eosNoZeros$Senescence_1)[1]

sosDate <- as.Date(sosMode, origin = "1970-01-01")
sosJulian <- as.integer(format(sosDate, "%j"))
eosDate <- as.Date(eosMode, origin = "1970-01-01")
eosJulian <- as.integer(format(eosDate, "%j"))






gc()
```














# What files to download?

```{r}
# Read in the list of the LAZ files. There are so many and the data allocation to download
# and read all of them in would be too much, so I will try and find if any of our GEDI locations
# fall within the 1km grid cell that each of them represent. Once I have that figured out I can
# then calculate tree metrics
lazFiles <- data.table::fread('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/LAZ files.txt')

# Function to get easting and northing from the LAZ file names
parse_tile_coords <- function(tile_name) {
  tile_id <- str_extract(tile_name, "15[A-Z]{3}[0-9]{6}")
  zone <- as.numeric(str_sub(tile_id, 1, 2))
  mgrs <- str_sub(tile_id, 3, 5)
  east <- as.numeric(str_sub(tile_id, 6, 8)) * 1000
  north <- as.numeric(str_sub(tile_id, 9, 11)) * 1000 + 5000000
  data.frame(zone = zone, mgrs = mgrs, easting = east, northing = north)
}

# Bind together
tile_meta <- do.call(rbind, lapply(lazFiles$Files, parse_tile_coords)) %>% drop_na()

# Function to create square polygons
make_tile <- function(easting, northing, size = 1000) {
  st_polygon(list(rbind(
    c(easting, northing),
    c(easting + size, northing),
    c(easting + size, northing + size),
    c(easting, northing + size),
    c(easting, northing)
  )))
}

# Apply to all elements and then convert to epsg 4326
tiles_polys <- mapply(make_tile, tile_meta$easting, tile_meta$northing, SIMPLIFY = FALSE)
tiles_sf <- st_sfc(tiles_polys, crs = 26915)
tiles_sf <- st_as_sf(tiles_sf)
tiles_sf$mgrs <- tile_meta$mgrs
tiles_sf$n <- 1:nrow(tiles_sf)
tiles_sfGedi <- st_transform(tiles_sf, crs = "epsg:4326")

# Plot for visual check (optional)
ggplot() +
  geom_sf(data = tiles_sfGedi, fill = NA, color = "black") +
  geom_sf(data = BWCA.shp[3], fill = NA, color = "red") +
  theme_minimal()

# Clip the tiles to the BWCA shapefile and then decipher which GEDI location fall in which grid cells
tilesBWCA <- st_intersection(tiles_sfGedi, BWCA.shp)
tilesBWCA <- st_as_sf(tilesBWCA, crs = "epsg:4326") %>%
  mutate(tileID = n)
# Transform intersected tiles back to UTM
tilesBWCA_UTM <- st_transform(tilesBWCA, crs = "epsg:26915")

# Extract xmin/ymin and carry tileID + mgrs
n <- nrow(tilesBWCA_UTM)
xmin_vals <- numeric(n)
ymin_vals <- numeric(n)
tileID_vals <- numeric(n)
mgrs_vals <- character(n)

for (i in 1:n) {
  bbox <- st_bbox(tilesBWCA_UTM[i, ])
  xmin_vals[i] <- bbox["xmin"]
  ymin_vals[i] <- bbox["ymin"]
  tileID_vals[i] <- tilesBWCA_UTM$tileID[i]
  mgrs_vals[i] <- tilesBWCA_UTM$mgrs[i]
}

# Final output data frame
coordsDf <- data.frame(
  tileID = tileID_vals,
  xmin = as.integer(xmin_vals) / 1000,
  ymin = (ymin_vals - 5000000) / 1000,
  mgrs = mgrs_vals,
  stringsAsFactors = FALSE
)

coordsDf <- coordsDf %>% mutate(xmin = round(xmin), ymin = round(ymin))
coordsDf <- coordsDf %>% mutate(code = paste0(mgrs, xmin, ymin))

# Now that we have the tiles/coordinates that we need, we can start filtering the original
# LAZ files to figure out which ones we need to download
# Mark dummy = 1 if the coordsDf$code is in laz_codes to test if they are in
coordsDf$dummy <- ifelse(coordsDf$code %in% lazCodes, 1, 0)
coordsDf <- coordsDf %>% filter(dummy == 1)

# Filter for the final LAZ files
lazFilesFinal <- lazFiles[map_lgl(lazFiles$Files, function(file) {
  any(str_detect(file, fixed(coordsDf$code)))
}), ]


# write_csv(lazFilesFinal,
#           file = "/Users/louisgoodall/Desktop/lazFilesFinal.csv")


#######################
gediAll_UTM <- st_transform(gediAll_sf, crs = "epsg:26915")

gediAll_joined <- st_join(gediAll_UTM, tilesBWCA_UTM[, c("tileID", "mgrs")], left = FALSE)

gediAll_joined <- gediAll_joined %>%
  mutate(xmin = floor(st_coordinates(.)[, 1] / 1000),
         ymin = floor((st_coordinates(.)[, 2] - 5000000) / 1000),
         code = paste0(mgrs, xmin, ymin))

gediAll_joined <- gediAll_joined %>% mutate(code = trimws(code))

gediMatched <- gediAll_joined %>% filter(code %in% coordsDf$code)


gediMatched <- gediMatched %>%
  filter(degrade_flag == 0,
         Date > "2023-12-31") %>%
  group_by(code) %>%
  arrange(code, shot_number) %>%
  mutate(shot_order = row_number(),
         uniqueID = paste0("uID_",code,"_",shot_order))

# gediMatched <- gediMatched %>%
#   filter(Date > "2023-12-31",
#          degrade_flag == 0) %>%
#   group_by(code) %>%
#   # select(shot_number, code) %>%
#   arrange(code, shot_number) %>%
#   mutate(shot_order = row_number(),
#          uniqueID = paste0("uID_",code,"_",shot_order))

st_write(gediMatched,
         dsn = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/gediMatched.shp")
```

# Tree metrics

```{r}
# Read in and set analysis parameters of the lidar point clouds
testLAS <- readLAScatalog("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Test_Data/", select = "xyzc")
opt_chunk_size(testLAS) <- 100
opt_chunk_buffer(testLAS) <- 15
testLAS@data$code <- str_extract(testLAS@data$filename, "[A-Z]{3}[0-9]{6}")

# Create a data frame of the rows that match the lidar point cloud locations by code
testGEDI <- gediMatched %>% filter(code %in% unique(testLAS@data$code))
source("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/lidarMetrics.R")
gediCodes <- unique(testGEDI$code)
matchedCodes <- testLAS@data$code[testLAS@data$code %in% gediCodes]
setdiff(gediCodes, matchedCodes)
testLAS <- testLAS[testLAS@data$code %in% gediCodes, ]
class(testGEDI) <- c("sf", "data.frame")

# Create folders for metricsDir, alsDir and FuelCalcDir
metricsDir = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Tree-Level Metrics"
alsDir = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/LAZ"
fcDir = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelCalc"
for (d in c(metricsDir, alsDir, fcDir)) if (!dir.exists(d)) dir.create(d, recursive = T)

# Create the metrics and LAS files
for (i in 1:nrow(testGEDI)) {
  process_tlm2(i, gedi = testGEDI, .ctg = testLAS, alsdir = alsDir, mdir = metricsDir)
}
```


```{r}
# Read in the metrics that have been created by the for loop above
#filesMetrics <- list.files(metricsDir, full.names = TRUE)
#filesALS <- list.files(alsDir, full.names = TRUE)
filesMetrics <- list.files("/Users/louisgoodall/Desktop/Tree-Level_Metrics", full.names = TRUE)
filesALS <- list.files("/Users/louisgoodall/Desktop/LAZ", full.names = TRUE)
idsMetrics <- parse_number(basename(filesMetrics))
idsALS <- parse_number(basename(filesALS))
identical(idsALS, idsMetrics)

# Function to load spatial df, add uniqueID column and renames Zmax to Z
read_with_id = function(path) {
  # Extract the full ID like TXP624306_1
  id = str_extract(basename(path), "(?<=uID_)[A-Za-z0-9_]+(?=\\.gpkg$)")
  
  m = st_read(path, quiet = TRUE)
  m$uniqueID = id
  
  return(select(m, uniqueID, treeID, Z = Zmax, everything()))
}

# Get metrics and then find the forest types beneath them
metrics <- map_dfr(filesMetrics, read_with_id) %>% `st_crs<-`("epsg:26915")
fortypGEDI <- extract(fortypcdBWCA_UTM, metrics)
metrics <- cbind(metrics, fortypGEDI) %>% rename("Species" = "Label")

# Here I handle the missing species labels
dominantSpp <- metrics %>%
  st_drop_geometry() %>%
  group_by(uniqueID) %>%
  count(Species) %>%
  summarise(Ndom = sum(n),
            domSpec = Species[which.max(n)],
            percDom = n[which.max(n)] / Ndom,
            Nna = sum(is.na(Species)),
            percNA = Nna/Ndom, .groups = "drop")

metricsDf <- inner_join(metrics, select(dominantSpp, uniqueID, domSpec), by = "uniqueID") %>%
  mutate(Species = case_when(is.na(Species) ~ domSpec, TRUE ~ Species)) %>%
  filter(sum(is.na(Species)) == 0, .by = uniqueID)


#----PREDICT DBH----#
# Gotta build the models for predicting DBH. I will use the height (Z) of the trees to 
# create models that express a hieght-diameter relationship
spcds <- c(105, 125, 129, 12, 94, 97, 95, 71, 241, 129, 100, 802, 833, 823, 972, 316, 543, 920, 461, 317, 318, 951, 746, 375,741, 761)
treeMN <- data.table::fread("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/MN_TREE.csv")
treeMN <- treeMN %>% filter(SPCD %in% spcds, INVYR  == 2023) %>% mutate(DIA_CM = DIA * 2.54, HT_M = HT * 0.3048) %>%
  mutate(Species = case_when(SPCD == 12 ~ "Balsam fir",SPCD == 71 ~ "Tamarack",SPCD == 94 ~ "White spruce",SPCD == 95 ~ "Black spruce",SPCD == 97 ~ "Red spruce",SPCD == 105 ~ "Jack pine",SPCD == 125 ~ "Red pine",SPCD == 129 ~ "Eastern white pine",SPCD == 241 ~ "Northern white-cedar",SPCD == 316 ~ "Red maple",SPCD == 317 ~ "Silver maple",SPCD == 318 ~ "Sugar maple",SPCD == 375 ~ "Paper birch",SPCD == 543 ~ "Black ash",SPCD == 741 ~ "Balsam poplar",SPCD == 746 ~ "Quaking aspen",SPCD == 802 ~ "White oak",SPCD == 823 ~ "Bur oak",SPCD == 833 ~ "Northern red oak",SPCD == 951 ~ "American basswood",TRUE ~ "American elm"))

# Crate a function to fit Chapman-Richards growth model. I couldn't find any good height-diameter
# relationships in the literature so I decided to estimate them using the nlsLM function.
# Below is the function to run the model and then a for loop to look at the residuals of
# each model.
fitChapman <- function(df) {
  tryCatch({
    nlsLM(DIA_CM ~ a * (1 - exp(-b * HT_M))^c,
          data = df,
          start = list(a = 30, b = 0.02, c = 1),
          control = nls.lm.control(maxiter = 1000))
  }, error = function(e) {
    # fallback to log-log linear
    lm(log(DIA_CM) ~ log(HT_M), data = df)
  })
}

fittedSpecies <- treeMN %>% group_by(Species) %>% group_map(~ fitChapman(.x), .keep = TRUE)
species_names <- treeMN %>% group_by(Species) %>% group_keys() %>% pull(Species)

# Residual plots to check the assumptions of the models I created. There are some assumptions
# being violated here and models will need improvement, but for now they are close enough
# plot_list <- list()
# for (i in seq_along(species_names)) {
#   species <- species_names[i]
#   model <- fittedSpecies[[i]]
#   df <- treeMN %>% filter(Species == species) %>% select(DIA_CM, HT_M) %>% drop_na()
#   if ("nls" %in% class(model) || "nlsLM" %in% class(model)) {
#     coefs <- coef(model)
#     df$predictor <- coefs[1] * (1 - exp(-coefs[2] * df$HT_M))^coefs[3]
#     lm_model <- lm(DIA_CM ~ predictor, data = df)
#     aug <- broom::augment(lm_model)
#     p1 <- ggplot(data = aug, aes(x = .std.resid)) +
#       educate::stat_density_confidence(model = "normal") +
#       stat_density(geom = "line") +
#       theme_bw() +
#       xlab("Standardized residuals") +
#       ylab("Probability density") +
#       ggtitle(paste("Density: Residuals for", species))
#     p2 <- ggplot(aug, aes(x = .fitted, y = .std.resid)) +
#       geom_point(alpha = 0.5) +
#       geom_smooth(se = FALSE, color = "blue") +
#       geom_hline(yintercept = 0, linetype = "dashed") +
#       xlab("Fitted Values") +
#       ylab("Standardized Residuals") +
#       theme_bw() +
#       ggtitle(paste("Residuals vs Fitted for", species))
#     plot_list[[species]] <- list(density_plot = p1, resid_plot = p2)
#   } else {
#     message(paste("Skipping", species, "- fallback model was used."))
#   }
# }

# Because I am trying to assign species height-diameter curves to forest type code there is
# sometimes a mismatch. To circumvent this I will assign species as appropriately as possible
# and for those that have more than one (e.g. Eastern white pine / northern red oak / white ash), 
# I will assign one species randomly
modelTable <- tibble(
  species = species_names,
  fitModel = fittedSpecies
)

uniqueMetricSpp <- unique(metricsDf$Species)
modelSpp <- unique(modelTable$species)

set.seed(33)
speciesMap <- tibble(
  metricsSpp = uniqueMetricSpp,
  matchedModelSpp = map_chr(unique(metricsDf$Species), function(ms) {
    components <- str_split(tolower(ms), " / |,| and | & ") %>% unlist() %>% str_trim()
    matches <- modelSpp[map_lgl(tolower(modelSpp), function(mod) {
      any(str_detect(mod, fixed(components)))
    })]
    if (length(matches) == 0) {
      NA_character_
    } else {
      sample(matches, 1)
    }
  })
)

# Join with metricsDf and then run the calculation for DBH
metricsDf <- metricsDf %>% left_join(speciesMap, by = c("Species" = "metricsSpp"))
for (i in 1:nrow(modelTable)) {
  S <- modelTable$species[i]
  # matchRows <- metricsDf$matchedModelSpp == S
  matchRows <- !is.na(metricsDf$matchedModelSpp) & metricsDf$matchedModelSpp == S
  
  if (any(matchRows)) {
    metricsDf$DBH[matchRows] <- predict(modelTable$fitModel[[i]], metricsDf[matchRows, ] %>% select(Z)) %>%
      round(2)
  }
}

#----CROWN CLASS----#
# Function to find crown class
crcl <- function(Z) {
  if (length(Z) == 1) {             # If only 1 value then D is assigned
    return(c(cl = as.factor("D")))
  } else {
    m <- mean(Z, na.rm = TRUE)
    s <- sd(Z, na.rm = TRUE)
    up <- m + s
    lo <- m - s
    cut(Z, breaks = c(0, lo, up, 100), labels = c("S", "C", "D"))  # C is found from lo -- up
  }
}
metricsDf$CrCl <- group_by(metricsDf, uniqueID) %>% group_map(~ crcl(.$Z)) %>% unlist()

# Check for any trees that have unrealistic CBHs. If the CBH is too high up, or if
# it is less than 2m. Any tree with an unralistic CBH is given the default value of 0.5
unrealistic <- sum(metricsDf$CBH > metricsDf$Z * 0.9 | metricsDf$CBH < 2)
unrealistic / nrow(metricsDf) # 36%
sum(metricsDf$DBH < 7) / nrow(metricsDf) # 20%

metricsDf <- metricsDf %>% mutate(CBH = ifelse(CBH > Z * 0.9 | CBH < 2, Z/2, CBH))



# THIS BIT MAY NOT BE NEEDED
# footprint_m2 <- pi * 12.5^2
# footprint_ha <- footprint_m2 / 10000
# 
# # I will need this later on
# geometry <- metricsDf$geom
# 
# acreExpansion <- 2.87
# hectareExpansion <- 4.51
# 
# treeN <- metricsDf %>% as.data.frame() %>%
#   group_by(uniqueID) %>%
#   summarise(n = n())
# 
# metricsDf <- metricsDf %>% left_join(treeN, by = "uniqueID") %>% as.data.frame()
# 
# metricsDf %>% as.data.frame() %>%
#   group_by(matchedModelSpp) %>%
#   summarise(n = n()) %>%
#   ggplot(., aes(x = matchedModelSpp, y = n, fill = matchedModelSpp)) +
#   geom_bar(stat = "identity") +
#   theme_classic() +
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
# 
# 
# metricsDf <- metricsDf %>%
#   group_by(uniqueID) %>%
#   mutate(matchedModelSpp = ifelse(is.na(matchedModelSpp), mode(matchedModelSpp), matchedModelSpp))
# 
# metricsDf <- metricsDf %>%
#   group_by(uniqueID, matchedModelSpp) %>%
#   mutate(local_values = list(DBH[!is.na(DBH)])) %>%
#   ungroup() %>%
#   group_by(matchedModelSpp) %>%
#   mutate(global_values = list(DBH[!is.na(DBH)])) %>%
#   ungroup() %>%
#   rowwise() %>%
#   mutate(
#     DBH = ifelse(
#       is.na(DBH),
#       if (length(local_values) > 0) {
#         sample(local_values, 1)
#       } else if (length(global_values) > 0) {
#         sample(global_values, 1)
#       } else {
#         NA_real_  # if no data at all for that species
#       },
#       DBH
#     )
#   ) %>%
#   ungroup() %>%
#   select(-local_values, -global_values)
# 
# x <- metricsDf %>%
#   drop_na() %>%
#   mutate(CrownDepth = Z - CBH) %>%
#   select(uniqueID, treeID, Z, CBH, canopy_volume, crown_area, volume_per_m2, Species, DBH, CrCl, CFL, CCover, CBD, CrownDepth) %>%
#   mutate(CBD_2 = CFL / CrownDepth)
# 
# hist(x$CBD_2)
# 
# 
# hist(metricsDf$CBH)
  
```


# FuelCalc

```{r}
#----TRE FILE----#
# NAs need to be filled in. Do that below.
fuelCalcDf <- data.frame(
  PlotID = metricsDf$uniqueID,
  MonitoringStatus = "Baseline",
  MonitoringStatusOrder = 1,
  TreesSpecies = metricsDf$matchedModelSpp,
  TreeExpansionFactor = acreExpansion,
  Diameter = metricsDf$DBH / 2.54,
  TreeHeight = metricsDf$Z * 3.281,
  CrownBaseHeight = metricsDf$CBH * 3.281,
  TreeStatus = "H",
  CrownClass = metricsDf$CrCl,
  CrownRatio = "",
  BoleCharHeight  = "",
  "CrownScorch%" = "",
  ScorchHeight = 0.1,
  CKR = "",
  BeetleDamage = "",
  EquationType = "CRNSCH",
  "FIHt/ScHt" = "",
  FS = "S",
  Severity = ""
)

# The meth0d below doesn't like factors so I need to make it a character
fuelCalcDf$TreesSpecies <- as.character(fuelCalcDf$TreesSpecies)

validSpp <- unique(fuelCalcDf$TreesSpecies[!is.na(fuelCalcDf$TreesSpecies)])
rowsNA <- which(is.na(fuelCalcDf$TreesSpecies))
sppTable <- table(fuelCalcDf$TreesSpecies[!is.na(fuelCalcDf$TreesSpecies)])
set.seed(33)
fuelCalcDf$TreesSpecies[rowsNA] <- sample(names(sppTable), length(rowsNA), replace = TRUE, prob = sppTable)

# Fill in NAs for DBH
fuelCalcDf <- fuelCalcDf %>%
  group_by(PlotID) %>%
  mutate(Diameter = ifelse(is.na(Diameter), median(Diameter, na.rm = TRUE), Diameter)) %>% ungroup()

# Now do crown class
mode <- function(x) {
  x <- na.omit(x)
  if (length(x) == 0) return(NA)
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

fuelCalcDf <- fuelCalcDf %>%
  group_by(PlotID) %>%
  mutate(CrownClass = ifelse(is.na(CrownClass), mode(CrownClass), CrownClass)) %>% ungroup()

# Now do tree status. This is for alive, sick or dead trees. I am unsure as to the actual status
# of all my LiDAR trees, so I will assume they are all healthy for simplicity. Dead ones are
# removed anyway
# fuelCalcDf$TS <- "L"


fuelMap <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/fuelRast.tif")
CN <- terra::extract(fuelMap[[1]], vect(geometry))
lookupCN <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/CN_lookup.csv")
treeMN <- data.table::fread("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/MN_TREE.csv")

treeMN$PLT_CN <- as.numeric(treeMN$PLT_CN)


crownRatioLookUp <- inner_join(lookupCN, CN, by = c("Value" = "FuelMapCN")) %>%
  inner_join(treeMN, by = c("PredCN" = "PLT_CN")) %>%
  select(Value, PredCN, UNCRCD) %>%
  unique()
cnRast <- fuelMap[[1]]


crownRatioLookUp <- crownRatioLookUp %>%
  group_by(Value) %>%
  mutate(UNCRCD = ifelse(is.na(UNCRCD), median(UNCRCD, na.rm = TRUE), UNCRCD)) %>%
  summarise(UNCRCD = mean(UNCRCD))


crownRatioRast <- classify(cnRast, rcl = crownRatioLookUp, others = NA)

crownRatioDf <- terra::extract(crownRatioRast, vect(geometry))
colnames(crownRatioDf)[2] <- "CRWN_RT"

fuelCalcDf$CrownRatio <- crownRatioDf$CRWN_RT

fuelCalcDf <- fuelCalcDf %>% mutate(CrownClass = case_when(CrownClass == 3 ~ "D", CrownClass == 2 ~ "C", TRUE ~ "S"))

# Not all of these species match with the species coded into FuelCalc and as such I will
# have to add in the nearest phylogenetic replacement
fuelCalcDf <- fuelCalcDf %>%
  mutate(TreesSpecies = case_when(
    TreesSpecies == "American basswood" ~ "QURU",       # Should be TIAM
    TreesSpecies == "Balsam fir" ~ "ABBA",
    TreesSpecies == "Balsam poplar" ~ "BEPA",           # Should be POBA2
    TreesSpecies == "Black ash" ~ "BEAL2",              # Should be FRNI
    TreesSpecies == "Black spruce" ~ "PIMA",
    TreesSpecies == "Bur oak" ~ "QURU",                 # Should be QUMA2
    TreesSpecies == "Eastern white pine" ~ "PIST",
    TreesSpecies == "Jack pine" ~ "PICO",               # Should be PIBA2
    TreesSpecies == "Northern red oak" ~ "QURU",
    TreesSpecies == "Northern white-cedar" ~ "CHTH2",    # Should be THOC2
    TreesSpecies == "Paper birch" ~ "BEPA",
    TreesSpecies == "Quaking aspen" ~ "POTR5",
    TreesSpecies == "Red maple" ~ "ACRU",
    TreesSpecies == "Red pine" ~ "PIJE",                # Should be PIRE
    TreesSpecies == "Sugar maple" ~ "ACSA3",
    TreesSpecies == "Tamarack" ~ "LAOC",                # Should be LALA
    TreesSpecies == "White spruce" ~ "PIGL",
    TRUE ~ TreesSpecies
  ))

fuelCalcDf <- fuelCalcDf %>%
  # Gather local crown ratio values per uniqueID/species
  group_by(PlotID, TreesSpecies) %>%
  mutate(local_crown = list(CrownRatio[!is.na(CrownRatio)])) %>%
  ungroup() %>%
  # Gather global crown ratio values per species
  group_by(TreesSpecies) %>%
  mutate(global_crown = list(CrownRatio[!is.na(CrownRatio)])) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(
    CrownRatio = ifelse(
      is.na(CrownRatio),
      if (length(local_crown) > 0) {
        sample(local_crown, 1)
      } else if (length(global_crown) > 0) {
        sample(global_crown, 1)
      } else {
        NA_real_
      },
      CrownRatio
    )
  ) %>%
  ungroup() %>%
  select(-local_crown, -global_crown)



fuelCalcDf <- fuelCalcDf %>% arrange(PlotID, TreesSpecies)

# write_csv(fuelCalcDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelCalc/treeFile.csv")

#----FFI FILE----#
# Now we need to get the fuel data that falls underneath each individual tree in the BWCA
fuelMap <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/fuelRast.tif")
duffRast <- fuelMap[[7]] * 0.0005
litterRast <- fuelMap[[6]] * 0.0005
hr1Rast <- fuelMap[[2]] * 0.0005
hr10Rast <- fuelMap[[3]] * 0.0005
hr100Rast <- fuelMap[[4]] * 0.0005
hr1000Rast <- fuelMap[[5]] * 0.0005

# Duff depth is not in these maps, but it is in the FIA MN_DWM_DUFF_LITTER_FUEL table
CN <- terra::extract(fuelMap[[1]], vect(geometry))
lookupCN <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/CN_lookup.csv")
duffFIA <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/MN_DWM_DUFF_LITTER_FUEL.csv")
lookupTable <- inner_join(lookupCN, CN, by = c("Value" = "FuelMapCN")) %>%
  inner_join(duffFIA, by = c("PredCN" = "PLT_CN")) %>%
  select(Value, PredCN, DUFFDEP)
cnRast <- fuelMap[[1]]
duffLookup <- as.data.frame(cbind(as.integer(lookupTable$Value), as.data.frame(lookupTable$DUFFDEP)))
duffDepRast <- terra::classify(cnRast, rcl = duffLookup, others = NA)

# Now do the same for decay classes
dwmFIA <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelMap/MN_DWM_COARSE_WOODY_DEBRIS.csv")
lookupTable <- inner_join(lookupCN, CN, by = c("Value" = "FuelMapCN")) %>%
  inner_join(dwmFIA, by = c("PredCN" = "PLT_CN")) %>%
  select(Value, PredCN, DECAYCD)
dwmLookup <- as.data.frame(cbind(as.integer(lookupTable$Value), as.data.frame(lookupTable$DECAYCD)))
decayRast <- classify(cnRast, rcl = dwmLookup, others = NA)

fuelStack <- c(duffDepRast, decayRast ,duffRast, litterRast, hr1Rast, hr10Rast, hr100Rast, hr1000Rast)

# Extract the data and then fill NAs with the mean value for each uniqueID
fuelDf <- terra::extract(fuelStack, vect(geometry))
fuelDf$uniqueID <- metricsDf$uniqueID
colnames(fuelDf)[2:3] <- c("DUFF_DEPTH", "DECAYCD")

fuelDf <- fuelDf %>%
  group_by(uniqueID) %>%
  mutate(across(where(is.numeric), ~ ifelse(is.na(.), mean(., na.rm = TRUE), .))) %>%
  ungroup()

fuelCalcDf

fuelDf %>%
  group_by(uniqueID) %>%
  summarise(DECAYCD = as.character(DECAYCD),
            across(where(is.numeric), ~mean(.x, na.rm = TRUE))) %>%
  ungroup() %>%
  group_by()
  

fuelDf <- fuelDf %>%
  group_by(uniqueID) %>%
  summarise(
    DECAYCD = as.integer(mode(DECAYCD)),                      # mode of DECAYCD
    across(where(is.numeric), ~mean(.x, na.rm = TRUE)), # mean of numeric columns
    .groups = "drop"
  ) %>%
  mutate(ID = 1:nrow(.))

ffiFileDf <- data.frame(
  PlotID = fuelDf$uniqueID,
  Monitoring_Status = "Baseline",
  Monitoring_Status_Order = 1,
  TotalDuffLoad = fuelDf$DUFF_CARBON,
  DuffDepth = fuelDf$DUFF_DEPTH,
  LitterLoad = fuelDf$LITTER_CARBON * 2,
  LichenLoad = 0,
  LiveMossLoad = 0,
  OneHour = fuelDf$FWD_SM_CARBON * 2,
  TenHour = fuelDf$FWD_MD_CARBON * 2,
  HundredHour = fuelDf$FWD_LG_CARBON * 2,
  ThousandHour = fuelDf$CWD_CARBON,
  ThousandHourDc1Sz1 = "",
  ThousandHourDc1Sz2 = "",
  ThousandHourDc1Sz3 = "",
  ThousandHourDc1Sz4 = "",
  ThousandHourDc1Sz5 = "",
  ThousandHourDc2Sz1 = "",
  ThousandHourDc2Sz2 = "",
  ThousandHourDc2Sz3 = "",
  ThousandHourDc2Sz4 = "",
  ThousandHourDc2Sz5 = "",
  ThousandHourDc3Sz1 = "",
  ThousandHourDc3Sz2 = "",
  ThousandHourDc3Sz3 = "",
  ThousandHourDc3Sz4 = "",
  ThousandHourDc3Sz5 = "",
  ThousandHourDc4Sz1 = "",
  ThousandHourDc4Sz2 = "",
  ThousandHourDc4Sz3 = "",
  ThousandHourDc4Sz4 = "",
  ThousandHourDc4Sz5 = "",
  ThousandHourDc5Sz1 = "",
  ThousandHourDc5Sz2 = "",
  ThousandHourDc5Sz3 = "",
  ThousandHourDc5Sz4 = "",
  ThousandHourDc5Sz5 = "",
  HerbLoadDead = "",
  HerbLoadLive = "",
  ShrubLoadDead = "",
  ShrubLoadLive = "",
  HerbSAV = "",
  GrassSAV = "",
  WoodySAVoneHour = "",
  FractionGroundAreaPileCovered = "",
  PileLoadWholePlot = "",
  EmisSTFS = "",
  EmisDuffRSC = "",
  EmisCWDRSC = ""
) %>% arrange(PlotID)


# write_csv(ffiFileDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelCalc/fuelsFile.csv")




# MAY NOT BE NEEDED ANY MORE
# metricsDf <- metricsDf %>%
#   group_by(uniqueID) %>%
#   summarise(Z = max(Z, na.rm = TRUE),
#             CBH = sum(CBH * canopy_volume, na.rm = TRUE) / sum(canopy_volume, na.rm = TRUE),
#             CBD = sum(CBD * canopy_volume, na.rm = TRUE) / sum(canopy_volume, na.rm = TRUE),
#             CC = mean(CCover, na.rm = TRUE),
#             N = n()) %>%
#   mutate(CD = Z - CBH,
#          CFL = CD * CBD)
```

# Initialize rGEE and GEE

```{r, warning = FALSE, message = FALSE, echo = FALSE}
# Weird order I know but run this in it's entirety and it'll be fine
library(reticulate)
use_condaenv("rgee_py", conda = "/opt/anaconda3/bin/conda", required = TRUE)
py_run_string("
import ee
ee.Initialize()
")
library(rgee)
ee_Initialize(drive = TRUE, project = "ee-gis712-2024", gcs = FALSE)
ee_clean_user_credentials()
ee_Authenticate()
library(reticulate)
use_condaenv("rgee_py", conda = "/opt/anaconda3/bin/conda", required = TRUE)
py_run_string("
import ee
ee.Initialize()
")
ee_Initialize(drive = TRUE, project = "ee-gis712-2024", gcs = FALSE)
```

# Earth Obervation Satellite Imagery download

```{r}
# Here I will download the satellite imagery that I will then use as the training data to
# help predict the wildfire risk potential
eeBWCA.shp <- sf_as_ee(BWCA.shp)
startDate <- "2024-06-01"
endDate <- "2024-09-01"

#----SENTINEL 2----#
# Band 1
# Read in the Sentinel-2 surface reflectance image collection which contains all the 
# images that we may want. Also ge the cloud band for masking purposes

# Load Sentinel-2 Surface Reflectance and Cloud Probability collections
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B1")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)

# Join SR and cloud collections by system:index
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)

# Cloud masking function (you must define this based on your needs)
# Example placeholder:
maskClouds <- function(joined) {
  sr <- ee$Image(joined$get("primary"))
  cloud <- ee$Image(joined$get("secondary"))
  cloudMask <- cloud$lt(10)  # Keep pixels with <10% cloud probability
  return(sr$updateMask(cloudMask))
}

# Apply cloud masking
sentinel2_band1_clean <- ee$ImageCollection(joinedCol$map(maskClouds))

# Optional: Resample to 30m and reproject to UTM Zone 15N (EPSG:26915)
resample30m <- function(image) {
  image$reproject(crs = "EPSG:26915", scale = 30)
}
sentinel2_band1 <- sentinel2_band1_clean$map(resample30m)

# Reduce across time to compute per-pixel percentiles (10th, 50th, 95th)
percentiles <- sentinel2_band1_clean$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)

# stats <- percentiles$select("B1_p50")$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)
# stats <- percentiles$select("B1_p10")$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)
# stats <- percentiles$select("B1_p95")$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)

# # Now you can use percentiles$select("B8A_p10"), "B8A_p50", or "B8A_p95" for display or export
# Map$centerObject(eeBWCA.shp)
# Map$addLayer(percentiles$select("B1_p50"),
#              list(min = 0, max = 16615, palette = c("black", "orange", "red")),
#              "Sentinel-2 B8A - 50th Percentile")
# 
# Map$addLayer(percentiles$select("B1_p10"),
#              list(min = 0, max = 16615, palette = c("black", "orange", "red")),
#              "Sentinel-2 B8A - 10th Percentile")
# 
# Map$addLayer(percentiles$select("B1_p95"),
#              list(min = 0, max = 16615, palette = c("black", "orange", "red")),
#              "Sentinel-2 B8A - 95th Percentile")

bandNames <- percentiles$bandNames()$getInfo()

for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 2
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B2")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band2 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band2 <- sentinel2_band2$map(resample30m)
percentiles <- sentinel2_band2$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 3
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B3")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band3 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band3 <- sentinel2_band3$map(resample30m)
percentiles <- sentinel2_band3$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 4
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B4")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band4 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band4 <- sentinel2_band4$map(resample30m)
percentiles <- sentinel2_band4$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 5
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B5")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band5 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band5 <- sentinel2_band5$map(resample30m)
percentiles <- sentinel2_band5$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 6
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B6")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band6 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band6 <- sentinel2_band6$map(resample30m)
percentiles <- sentinel2_band6$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 7
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B7")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band7 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band7 <- sentinel2_band7$map(resample30m)
percentiles <- sentinel2_band7$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 8
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B8")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band8 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band8 <- sentinel2_band8$map(resample30m)
percentiles <- sentinel2_band8$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 8A
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B8A")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band8A <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band8A <- sentinel2_band8A$map(resample30m)
percentiles <- sentinel2_band8A$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 11
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B11")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band11 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band11 <- sentinel2_band11$map(resample30m)
percentiles <- sentinel2_band11$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Band 12
s2Collection <- ee$ImageCollection("COPERNICUS/S2_SR")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("B12")
s2Clouds <- ee$ImageCollection("COPERNICUS/S2_CLOUD_PROBABILITY")$
  filterDate(startDate, endDate)
joinFilter <- ee$Filter$equals(leftField = "system:index", rightField = "system:index")
innerJoin <- ee$Join$inner()
joinedCol <- innerJoin$apply(s2Collection, s2Clouds, joinFilter)
sentinel2_band12 <- ee$ImageCollection(joinedCol$map(maskClouds))
sentinel2_band12 <- sentinel2_band12$map(resample30m)
percentiles <- sentinel2_band12$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
    image <- percentiles$select(band)$
    reproject(crs = "EPSG:26915", scale = 30)$
    clip(eeBWCA.shp)
    task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}


#----SENTINEL 1 SAR----#
# ASCENDING
# VH polarisation
# I downloaded the data using GEE and the script which can be found here (https://github.com/langoodall/Project-MN-Canopy-Fuels/blob/main/GEE.js)
# Uses and modified from Mullissa et al. (2021) https://doi.org/10.3390/rs13101954
# Here I am reading in the .tif files that I got from GEE and processing them

# So these are odd. The data is stored in linear which is great for the conversions and everything
# but needs to be in dB for plotting and comparison. To convert from linear to dB do the equation below
# dB = 10 * log10(x)
westBWCA_VH <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/VH_p50-0000000000-0000000000.tif")
eastBWCA_VH <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/VH_p50-0000000000-0000023296.tif")
stack <- sprc(list(westBWCA_VH, eastBWCA_VH))
VH <- mosaic(stack)
shapefile <- st_transform(BWCA.shp, crs = crs(VH))
VH <- crop(VH, shapefile) %>% mask(., shapefile)
VH <- project(VH, templateRaster, method = "near")
VH <- ifel(VH > 0, 10 * log10(VH), NA)
writeRaster(VH,
            filename = '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/VH_p50.tif',
            datatype = "FLT8S",
            NAflag = 0,
            overwrite = TRUE)

# VV polarisation
westBWCA_VV <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/VV_p50-0000000000-0000000000.tif")
eastBWCA_VV <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/VV_p50-0000000000-0000023296.tif")
stack <- sprc(list(westBWCA_VV, eastBWCA_VV))
VV <- mosaic(stack)
shapefile <- st_transform(BWCA.shp, crs = crs(VV))
VV <- crop(VV, shapefile) %>% mask(., shapefile)
VV <- project(VV, templateRaster, method = "near")
VV <- ifel(VV > 0, 10 * log10(VV), NA)
writeRaster(VV,
            filename = '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/VV_p50.tif',
            datatype = "FLT8S",
            NAflag = 0,
            overwrite = TRUE)

#----JAXA PALSAR----#
HV <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/HV_BWCA_PALSAR_2024.tif')
HH <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/HH_BWCA_PALSAR_2024.tif')

gc()

plot(HV)
plot(HH)

HH %>% min()
HH %>% min()
HV %>% min()
HV %>% min()

ifel(HH > 0, 10 * log10(HH), NA) %>% min()
ifel(HV > 0, 10 * log10(HV), NA) %>% min()
ifel(HV > 0, 10 * log10(HV), NA) %>% min()
ifel(HH > 0, 10 * log10(HH), NA) %>% min()


plot(ifel(HV > 0, 10 * log10(HV^2) - 83, NA))
plot(ifel(HH > 0, 10 * log10(HH^2) - 83, NA))



x <- ifel(HV > 0, 10 * log10(HV^2) - 83, NA) %>% as.data.frame() %>% drop_na()

hist(x$HV, breaks = 100)

?hist
```

# Old SAR stuff

```{r}
#----SENTINEL 1 SAR----#
# ASCENDING
# VH polarisation
# Here I am downloading the Sentinel-1 SAR data for the BWCA. I will choose the ASCENDING
# data because to use both ASCENDING and DESCENDING requires more processing. So, for now,
# I will use one direction consistently
s1VHCollection <- ee$ImageCollection("COPERNICUS/S1_GRD")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  filter(ee$Filter$eq("instrumentMode", "IW"))$
  filter(ee$Filter$listContains("transmitterReceiverPolarisation", "VH"))$
  filter(ee$Filter$eq("orbitProperties_pass", "ASCENDING"))$
  select("VH")

maskEdges <- function(img) {
  edge <- img$lt(-30)
  img$updateMask(edge$Not())
}

s1VHCollection <- s1VHCollection$map(maskEdges)

percentiles <- s1VHCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)

bandNames <- percentiles$bandNames()$getInfo()

for (band in bandNames) {
  image <- percentiles$select(band)$reproject(crs = "EPSG:26915", scale = 30)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF")
  cat("Starting export for:", band, "\n")
  task$start()
}

###########################################

s1VH <- ee$ImageCollection("COPERNICUS/S1_GRD")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  filter(ee$Filter$eq("instrumentMode", "IW"))$
  filter(ee$Filter$listContains("transmitterReceiverPolarisation", "VH"))$
  filter(ee$Filter$eq("orbitProperties_pass", "ASCENDING"))$
  select("VH")

s1VH$size()$getInfo()
s1VH$aggregate_array("system:id")$getInfo()

maskEdges <- function(img) {
  img$updateMask(img$gt(-30))
}
s1VH <- s1VH$map(maskEdges)

toLinear <- function(img) {
  ee$Image(10)$pow(img$divide(10))$copyProperties(img, img$propertyNames())
}
s1VH <- s1VH$map(toLinear)

leeFilter <- function(img) {

  # 3x3 kernel
  kernel <- ee$Kernel$square(1)

  # Local mean and variance
  mean <- img$reduceNeighborhood(ee$Reducer$mean(), kernel)
  variance <- img$reduceNeighborhood(ee$Reducer$variance(), kernel)

  # Noise variance (estimated locally)
  noiseVar <- variance$reduceNeighborhood(
    reducer = ee$Reducer$mean(),
    kernel = kernel
  )

  # Lee filter coefficient
  b <- variance$subtract(noiseVar)$divide(variance)

  # Filtered image
  mean$add(
    b$multiply(img$subtract(mean))
  )$rename(img$bandNames())$
    copyProperties(img, img$propertyNames())
}



lee_gee <- function(img, L = 1, win = 3) {

  kernel <- ee$Kernel$square(
    radius = win %/% 2,
    units = "pixels",
    normalize = TRUE
  )

  mean <- img$reduceNeighborhood(
    reducer = ee$Reducer$mean(),
    kernel = kernel
  )

  variance <- img$reduceNeighborhood(
    reducer = ee$Reducer$variance(),
    kernel = kernel
  )

  sigma_n2 <- 1 / L

  k <- variance$
    subtract(mean$pow(2)$multiply(sigma_n2))$
    divide(variance)$
    clamp(0, 1)

  mean$add(k$multiply(img$subtract(mean)))
}



s1VH <- s1VH$map(leeFilter)
s1_filt <- lee_gee(s1VH$select("VH"), L = 4)


median_s1VH <- s1VH$median()
median_s1VH <- median_s1VH$clip(eeBWCA.shp)

stats <- median_s1VH$reduceRegion(
  reducer = ee$Reducer$minMax(),
  geometry = eeBWCA.shp$geometry(),
  scale = 30,  # Sentinel-1 pixel size ~10m, 30m is usually fine for regional stats
  maxPixels = 1e13
)

# Print stats
stats$getInfo()



Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(median_s1VH,
             list(min = 0, max = 1, palette = c("#ff1b6b", "black", "#45caff")), "VH Median")


# VV polarization
s1VVCollection <- ee$ImageCollection("COPERNICUS/S1_GRD")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  filter(ee$Filter$eq("instrumentMode", "IW"))$
  filter(ee$Filter$listContains("transmitterReceiverPolarisation", "VV"))$
  filter(ee$Filter$eq("orbitProperties_pass", "ASCENDING"))$
  select("VV")
percentiles <- s1VVCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
  image <- percentiles$select(band)$reproject(crs = "EPSG:26915", scale = 30)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF")
  cat("Starting export for:", band, "\n")
  task$start()
}

# HH polarization
s1HHCollection <- ee$ImageCollection("COPERNICUS/S1_GRD")$
  # filterDate("2012-01-01", endDate)$
  # filterBounds(eeBWCA.shp)$
  filter(ee$Filter$eq("instrumentMode", "IW"))$
  filter(ee$Filter$listContains("transmitterReceiverPolarisation", "HH"))$
  filter(ee$Filter$eq("orbitProperties_pass", "DESCENDING"))$
  select("HH")
percentiles <- s1HHCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 95)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
  image <- percentiles$select(band)$reproject(crs = "EPSG:26915", scale = 30)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF")
  cat("Starting export for:", band, "\n")
  task$start()
}

# HV polarization
s1HVCollection <- ee$ImageCollection("COPERNICUS/S1_GRD")$
  filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  filter(ee$Filter$eq("instrumentMode", "IW"))$
  filter(ee$Filter$listContains("transmitterReceiverPolarisation", "HV"))$
  filter(ee$Filter$eq("orbitProperties_pass", "ASCENDING"))$
  select("HV")
percentiles <- s1HVCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)
bandNames <- percentiles$bandNames()$getInfo()
for (band in bandNames) {
  image <- percentiles$select(band)$reproject(crs = "EPSG:26915", scale = 30)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(image = image, description = paste0(band, "_export"), folder = "GEDI_BWCA", fileNamePrefix = band, region = eeBWCA.shp$geometry(), scale = 30, maxPixels = 1e13, fileFormat = "GeoTIFF")
  cat("Starting export for:", band, "\n")
  task$start()
}

# Load ALOS PALSAR HH yearly mosaics
alosHHCollection <- ee$ImageCollection("JAXA/ALOS/PALSAR/YEARLY/SAR_EPOCH")$
  # filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("HH")


# Reduce to percentiles (10, 50, 90)
percentiles <- alosHHCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)

# Get the percentile band names (HH_p10, HH_p50, HH_p95)
bandNames <- percentiles$bandNames()$getInfo()

# Export each band separately
for (band in bandNames) {
  image <- percentiles$select(band)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(
    image = image,
    description = paste0(band, "_export"),
    folder = "GEDI_BWCA",
    fileNamePrefix = band,
    region = eeBWCA.shp$geometry(),
    scale = 30,  # ALOS resolution is ~25 m
    maxPixels = 1e13,
    fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# Load ALOS PALSAR HH yearly mosaics
alosHVCollection <- ee$ImageCollection("JAXA/ALOS/PALSAR/YEARLY/SAR_EPOCH")$
  # filterDate(startDate, endDate)$
  filterBounds(eeBWCA.shp)$
  select("HV")

# Reduce to percentiles (10, 50, 95)
percentiles <- alosHVCollection$
  reduce(ee$Reducer$percentile(c(10, 50, 90)))$
  clip(eeBWCA.shp)$
  reproject(crs = "EPSG:26915", scale = 30)

# Get the percentile band names (HH_p10, HH_p50, HH_p95)
bandNames <- percentiles$bandNames()$getInfo()

# Export each band separately
for (band in bandNames) {
  image <- percentiles$select(band)$clip(eeBWCA.shp)
  task <- ee_image_to_drive(
    image = image,
    description = paste0(band, "_export"),
    folder = "GEDI_BWCA",
    fileNamePrefix = band,
    region = eeBWCA.shp$geometry(),
    scale = 30,  # ALOS resolution is ~25 m
    maxPixels = 1e13,
    fileFormat = "GeoTIFF"
  )
  cat("Starting export for:", band, "\n")
  task$start()
}

# DESCENDING
# I had a go at finding descending data for the BWCA but could not find any. No matter.
# VH polarization = NONE
# s1VHCollection <- ee$ImageCollection("COPERNICUS/S1_GRD")$
#   filterDate(startDate, endDate)$
#   filterBounds(eeBWCA.shp)$
#   filter(ee$Filter$eq("instrumentMode", "IW"))$
#   filter(ee$Filter$listContains("transmitterReceiverPolarisation", "VH"))$
#   select("VH")
# desc <- s1VHCollection$filter(ee$Filter$eq("orbitProperties_pass", "DESCENDING"))
# desc <- desc$median()$clip(eeBWCA.shp)
# stats <- desc$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 10, maxPixels = 1e13)$getInfo()
# print(stats)
# Map$centerObject(eeBWCA.shp)
# Map$addLayer(desc, 
#              list(min = -30, max = 0, palette = c("black", "orange", "red")),
#              "Sentinel 1 - SAR (Descending)")
# Map$addLayer(desc, {}, "Descending VH - Raw")
# 
# # Check to see if the BWCA has any descending data. If not then == 0
# desc_col <- s1VHCollection$filter(ee$Filter$eq("orbitProperties_pass", "DESCENDING"))
# desc_col$size()$getInfo()
```

# Final bits of data acquisition

```{r}
#----MODIS----#
# Phenology Start of Season
# Because we only need the one image of yearly phenology, we can do the cloud masking
# a bit differently than previous cloud masking in this script. First let's make a
# function that masks clouds in MODIS
maskMODISClouds <- function(image) {
  qa <- image$select("QA_Overall_1")
  qualityMask <- qa$bitwiseAnd(3)$eq(0)   # Keep only the good cells
  image$updateMask(qualityMask)
}

sosMODIS <- ee$ImageCollection("MODIS/061/MCD12Q2")$
  filterDate("2023-01-01", "2023-12-31")$
  filterBounds(eeBWCA.shp)$
  map(maskMODISClouds)$
  select("Greenup_1")
sosImage <- sosMODIS$first()$clip(eeBWCA.shp)
sosImage <- resample30mNN(sosImage)
# stats <- sosImage$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)
Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(sosImage,
             list(min = 19380, max = 19507, palette = c("black", "orange", "red")),
             "MODIS Phenology - Start of Season")


band_name <- sosImage$bandNames()$get(0)$getInfo()
task <- ee_image_to_drive(
  image = sosImage,
  description = paste0(band_name, "_export"),
  folder = "GEDI_BWCA",
  fileNamePrefix = band_name,
  region = eeBWCA.shp$geometry(),
  scale = 30,
  maxPixels = 1e13,
  fileFormat = "GeoTIFF"
)
task$start()

# Phenology End of Season
sosMODIS <- ee$ImageCollection("MODIS/061/MCD12Q2")$
  filterDate("2023-01-01", "2023-12-31")$
  filterBounds(eeBWCA.shp)$
  map(maskMODISClouds)$
  select("Senescence_1")
sosImage <- sosMODIS$first()$clip(eeBWCA.shp)
sosImage <- resample30mNN(sosImage)
# stats <- sosImage$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)
Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(sosImage,
             list(min = 19528, max = 19660, palette = c("black", "orange", "red")),
             "MODIS Phenology - End of Season")

band_name <- sosImage$bandNames()$get(0)$getInfo()
task <- ee_image_to_drive(
  image = sosImage,
  description = paste0(band_name, "_export"),
  folder = "GEDI_BWCA",
  fileNamePrefix = band_name,
  region = eeBWCA.shp$geometry(),
  scale = 30,
  maxPixels = 1e13,
  fileFormat = "GeoTIFF"
)
task$start()

#----STATIC LANDSCAPE VARIABLES----#
# Elevation
srtmDEM <- ee$Image("USGS/SRTMGL1_003")$
  clip(eeBWCA.shp)
# stats <- srtmDEM$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)
Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(srtmDEM,
             list(min = 335, max = 700, palette = c("black", "orange", "red")),
             "Elevation")

# Slope
slope <- ee$Terrain$slope(srtmDEM)
# stats <- slope$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)

# Aspect
aspect <- ee$Terrain$aspect(srtmDEM)
# stats <- aspect$reduceRegion(reducer = ee$Reducer$minMax(), geometry = eeBWCA.shp, scale = 30, maxPixels = 1e13)$getInfo()
# print(stats)

Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(srtmDEM,
             list(min = 335, max = 700, palette = c("black", "orange", "red")),
             "Elevation")
Map$addLayer(slope,
             list(min = 0, max = 52.55262, palette = c("black", "orange", "red")),
             "Slope")
Map$addLayer(aspect,
             list(min = 0, max = 358.2852, palette = c("black", "orange", "red")),
             "Elevation")

################
# Load SRTM DEM clipped to AOI
srtmDEM <- ee$Image("USGS/SRTMGL1_003")$
  clip(eeBWCA.shp)

# Visualize DEM
Map$centerObject(eeBWCA.shp)
Map$addLayer(eeBWCA.shp)
Map$addLayer(
  srtmDEM,
  list(min = 335, max = 700, palette = c("black", "orange", "red")),
  "Elevation"
)

# Terrain products
slope <- ee$Terrain$slope(srtmDEM)
aspect <- ee$Terrain$aspect(srtmDEM)

Map$addLayer(slope, list(min = 0, max = 45, palette = c("blue", "yellow", "red")), "Slope")
Map$addLayer(aspect, list(min = 0, max = 360, palette = c("purple", "cyan", "green")), "Aspect")

# --- EXPORTS ---
# Helper function
export_to_drive <- function(image, band_name) {
  task <- ee_image_to_drive(
    image = image,
    description = paste0(band_name, "_export"),
    folder = "GEDI_BWCA",
    fileNamePrefix = band_name,
    region = eeBWCA.shp$geometry(),
    scale = 30,
    maxPixels = 1e13,
    fileFormat = "GeoTIFF"
  )
  task$start()
}

# DEM
band_name_dem <- srtmDEM$bandNames()$get(0)$getInfo()
export_to_drive(srtmDEM, band_name_dem)

# Slope
band_name_slope <- slope$bandNames()$get(0)$getInfo()
export_to_drive(slope, band_name_slope)

# Aspect
band_name_aspect <- aspect$bandNames()$get(0)$getInfo()
export_to_drive(aspect, band_name_aspect)

```

# Other data needed

```{r}
#----TREEMAP----#
# AGB DRYBIO_L
# biomassRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/TreeMap/BIOMASS/TreeMap2016_DRYBIO_L.tif")
# BWCA.shp_Clip <- st_transform(BWCA.shp_Clip, crs = crs(biomassRast))
# biomassRast <- crop(biomassRast, BWCA.shp_Clip) %>% mask(., BWCA.shp_Clip)
# biomassRast <- project(biomassRast, fortypcdBWCA_UTM, method = 'bilinear')
# plot(biomassRast)
# writeRaster(biomassRast,
#             filename = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/TreeMap/biomassBWCA.tif",
#             NAflag = 0,
#             overwrite = TRUE)

biomassRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/TreeMap/biomassBWCA.tif")
plot(biomassRast)

#----MODIS----#
# To calculate some of these MODIS values I will need to utilise several different data sources.
# Below are 4 maps that come from the calibration of TRY plant trait data to MODIS images. Because
# all of these come from a global raster, I will be cropping them to the BWCA and then writing them
# back out as smaller sized raster files to save computation in the future.

# Leaf Dry Matter Content
# ldmcRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/LDMC_1km_v1.tif")
# BWCA.shp_Clip <- st_transform(BWCA.shp_Clip, crs = crs(ldmcRast))
# ldmcRast <- crop(ldmcRast, BWCA.shp_Clip) %>% mask(., BWCA.shp_Clip)
# ldmcRast <- project(ldmcRast, fortypcdBWCA_UTM, method = 'bilinear')
# writeRaster(ldmcRast,
#             filename = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/ldmcRast.tif",
#             NAflag = 0,
#             overwrite = TRUE)
ldmcRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/ldmcRast.tif")

# Leaf Nitrogen Content
# lncRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/LNC_1km_v1.tif")
# lncRast <- crop(lncRast, BWCA.shp_Clip) %>% mask(., BWCA.shp_Clip)
# lncRast <- project(lncRast, fortypcdBWCA_UTM, method = 'bilinear')
# writeRaster(lncRast,
#             filename = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/lncRast.tif",
#             NAflag = 0,
#             overwrite = TRUE)
lncRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/lncRast.tif")

# Leaf Phosphorus Content
# lpcRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/LPC_1km_v1.tif")
# lpcRast <- crop(lpcRast, BWCA.shp_Clip) %>% mask(., BWCA.shp_Clip)
# lpcRast <- project(lpcRast, fortypcdBWCA_UTM, method = 'bilinear')
# writeRaster(lpcRast,
#             filename = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/lpcRast.tif",
#             NAflag = 0,
#             overwrite = TRUE)
lpcRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/lpcRast.tif")

# Specific Leaf Area
# slaRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/SLA_1km_v1.tif")
# slaRast <- crop(slaRast, BWCA.shp_Clip) %>% mask(., BWCA.shp_Clip)
# slaRast <- project(slaRast, fortypcdBWCA_UTM, method = 'bilinear')
# writeRaster(slaRast,
#             filename = "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/slaRast.tif",
#             NAflag = 0,
#             overwrite = TRUE)
slaRast <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/MODIS/slaRast.tif")

```

# CBD SAR paper 

```{r}
directory <- '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Maybe This Is The Way'
files <- list.files(directory)

rasterList <- list()
for (file in files) {
  filePath <- file.path(directory, file)
  r <- rast(filePath)
  name <- basename(filePath) %>% str_extract("^[^_]+_[^_]+_[^_]+_[^_]+")
  rasterList[[name]] <- r
  plot(r)
}


#####################################

# ---------------------------
# 1) Load VH & VV rasters (in dB, same CRS/resolution)
# ---------------------------
vh <- rasterList[[1]]  # VH (dB)
vv <- rasterList[[8]]  # VV (dB)

# ---------------------------
# 2) 5x5 and 7x7 low-pass filters (mean)
# ---------------------------
w5 <- matrix(1, 5, 5) / 25
w7 <- matrix(1, 7, 7) / 49

vh5 <- focal(vh, w = w5, fun = "mean", na.policy = "omit")
vh7 <- focal(vh, w = w7, fun = "mean", na.policy = "omit")
vv5 <- focal(vv, w = w5, fun = "mean", na.policy = "omit")
vv7 <- focal(vv, w = w7, fun = "mean", na.policy = "omit")

# ---------------------------
# 3) VH:VV ratio in dB space = VH_dB - VV_dB
#    (equivalent to log10(VH_lin/VV_lin) scaled; this matches the usual treatment in dB)
# ---------------------------
vhvv   <- vh  - vv      # unfiltered ratio (dB)
vhvv5  <- vh5 - vv5     # 5x5 ratio (dB)
vhvv7  <- vh7 - vv7     # 7x7 ratio (dB)

# ---------------------------
# 4) Coefficients from your Table for CBD models
#    (ONLY VH and VH:VV terms are included here, per your request)
# ---------------------------

# CBD1  (zenith 0–7°)
b0_cbd1    <- 0.00      # <-- PUT THE PAPER'S INTERCEPT HERE
b_vh_cbd1  <-  0.0066   # VH
b_vh5_cbd1 <- -0.0349   # VH, 5x5
b_vh7_cbd1 <-  0.0291   # VH, 7x7
b_r_cbd1   <- -0.0005   # VH:VV
b_r5_cbd1  <-  0.0027   # VH:VV, 5x5
# VH:VV, 7x7 was "—" for CBD1 -> 0

CBD1 <- b0_cbd1 +
        b_vh_cbd1  * vh  +
        b_vh5_cbd1 * vh5 +
        b_vh7_cbd1 * vh7 +
        b_r_cbd1   * vhvv +
        b_r5_cbd1  * vhvv5

# CBD12 (zenith 0–23°)
b0_cbd12    <- 0.00     # <-- INTERCEPT
b_vh_cbd12  <-  0.0141
b_vh5_cbd12 <- -0.1061
b_vh7_cbd12 <-  0.0645
# VH:VV (unfiltered) for CBD12 was "—"
b_r5_cbd12  <-  0.0108  # VH:VV, 5x5
# VH:VV, 7x7 for CBD12 was "—"

CBD12 <- b0_cbd12 +
         b_vh_cbd12  * vh  +
         b_vh5_cbd12 * vh5 +
         b_vh7_cbd12 * vh7 +
         b_r5_cbd12  * vhvv5

# CBD123 (zenith 0–38°)
b0_cbd123    <- 0.00    # <-- INTERCEPT
b_vh_cbd123  <-  0.0332
b_vh5_cbd123 <- -0.2172
b_vh7_cbd123 <-  0.0961
b_r_cbd123   <- -0.0013  # VH:VV
b_r5_cbd123  <-  0.0278  # VH:VV, 5x5
b_r7_cbd123  <-  0.0185  # VH:VV, 7x7

CBD123 <- b0_cbd123 +
          b_vh_cbd123  * vh   +
          b_vh5_cbd123 * vh5  +
          b_vh7_cbd123 * vh7  +
          b_r_cbd123   * vhvv +
          b_r5_cbd123  * vhvv5 +
          b_r7_cbd123  * vhvv7

# CBDFC (FuelCalc-derived CBD)
b0_cbcfc    <- 0.00     # <-- INTERCEPT
b_vh_cbcfc  <-  0.0259
b_vh5_cbcfc <- -0.1708
# VH, 7x7 for CBDFC was "—"
b_r_cbcfc   <- -0.0028  # VH:VV
b_r5_cbcfc  <-  0.0319  # VH:VV, 5x5
# VH:VV, 7x7 for CBDFC was "—"

CBDFC <- b0_cbcfc +
         b_vh_cbcfc  * vh  +
         b_vh5_cbcfc * vh5 +
         b_r_cbcfc   * vhvv +
         b_r5_cbcfc  * vhvv5

# ---------------------------
# 5) Inspect / plot / write
# ---------------------------
plot(CBD123 / 10, main = "CBD123 from S1 VH & VH:VV (kg m^-3)")
# writeRaster(CBD123, "CBD123_from_S1_VH_ratio.tif", overwrite = TRUE)

metricsDf$x <- st_coordinates(metricsDf$geom)[,1]
metricsDf$y <- st_coordinates(metricsDf$geom)[,2]

metricsDf <- st_as_sf(metricsDf, coords = c("x", "y"), crs = 26915)

plot(CBD123 / 10, main = "CBD123 from S1 VH & VH:VV (kg m^-3)")
plot(metricsDf, add = TRUE)


cbdvalues <- extract(CBD123 / 10, metricsDf) %>% rename("CDB" = "VH")

metricsDf$CBD <- cbdvalues[,2]

ggplot(metricsDf, aes(x = Z, y = canopy_volume, colour = matchedModelSpp)) +
  geom_point(alpha = 0.1) +
  # geom_smooth(method = "lm") +
  theme_bw() +
  facet_wrap(~ matchedModelSpp)

metricsDf %>%
  ggplot(., aes(x = matchedModelSpp, y = Z, fill = matchedModelSpp)) +
  geom_boxplot() +
  theme_classic()


metricsDf <- metricsDf %>%
  group_by(matchedModelSpp) %>%
  mutate(canopy_volume = ifelse(is.na(canopy_volume), median(canopy_volume, na.rm = TRUE), canopy_volume)) %>%
  ungroup()


cflvalues <- metricsDf[,c(18,5)] %>% mutate(CFL = CBD * canopy_volume)


canopyCoverRast <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/LANDFIRE/Canopy Cover/canopyCoverRast.tif')
ccvalues <- extract(canopyCoverRast, metricsDf)



cbhvalues <- metricsDf$CBH

chvalues <- metricsDf$Z


df <- cbind(cbdvalues[,2], cflvalues[,2], ccvalues[,2], cbhvalues, chvalues) %>%
  `colnames<-`(c("CBD", "CFL", "CC", "CBH", "CH", "geometry"))

df$Spp <- metricsDf$matchedModelSpp

gc()



metricsDf %>%
  group_by(uniqueID) %>%
  summarise(CBD = mean(CBD, na.rm = TRUE))

metricsDf %>% filter(uniqueID == "TWP552307_") %>%
  dplyr::select(CBD)

names(metricsDf)
```

# DBH Model

```{r}
ggplot(metricsDf, aes(x = Z, y = canopy_volume)) +
  geom_point() +
  theme_gray()

model <- mclust::Mclust(data_frame(metricsDf$Z, metricsDf$canopy_volume) %>% drop_na())
# plot(model, what = "classification")

lm(canopy_volume ~ Z, data = subset(metricsDf, cluster == 1))
lm(canopy_volume ~ Z, data = subset(metricsDf, cluster == 2))


gam_fit <- gam(canopy_volume ~ s(Z), data = metricsDf)
plot(gam_fit)


mix_fit <- flexmix::flexmix(canopy_volume ~ Z, data = metricsDf %>% drop_na(), k = 2)
flexmix::parameters(mix_fit)


ggplot(metricsDf %>% drop_na(), aes(x = Z, y = canopy_volume)) +
  geom_point() +
  theme_gray() +
  stat_function(fun = function(x){-18.113726 + 9.736706*x}, linetype = "dashed", color = "red") +
  stat_function(fun = function(x){-258.09794 + 42.11347*x}, linetype = "solid", color = "blue")
########################################

metricsDf %>%
  filter(matchedModelSpp != "Bur oak") %>%
  drop_na(Z, canopy_volume) %>%
  group_by(matchedModelSpp) %>%
  group_split() %>%
  map(function(df) {
    spp <- unique(df$matchedModelSpp)
    mclust_Model <- Mclust(df[, c("Z", "canopy_volume")])
    mix_fit <- flexmix(canopy_volume ~ Z, data = df, k = 2)
    gam_fit <- gam(canopy_volume ~ s(Z), data = df)
    list(
      species = spp,
      mclust = mclust_Model,
      mix = mix_fit,
      gam = gam_fit,
      params = parameters(mix_fit)
    )
  })


models <- metricsDf  %>%
  filter(matchedModelSpp != "Bur oak") %>%
  drop_na(Z, canopy_volume) %>%
  group_by(matchedModelSpp) %>%
  group_split() %>%
  map(function(df) {
    spp <- unique(df$matchedModelSpp)

    # Skip groups with too few points
    if (nrow(df) < 10) {
      message("Skipping ", spp, " (too few observations)")
      return(NULL)
    }

    # Try–catch to handle Mclust/flexmix errors gracefully
    tryCatch({
      mclust_model <- Mclust(df[, c("Z", "canopy_volume")])

      mix_fit <- flexmix(canopy_volume ~ Z, data = df, k = 2)

      gam_fit <- gam(canopy_volume ~ s(Z), data = df)

      list(
        species = spp,
        mclust = mclust_model,
        mix = mix_fit,
        gam = gam_fit,
        params = parameters(mix_fit)
      )
    }, error = function(e) {
      message("Error in ", spp, ": ", e$message)
      return(NULL)
    })
  }) %>%
  compact()





```


# BIGMAP Data

```{r}
directory <- '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/BIGMAP Rasters'
files <- list.files(directory, pattern = "\\.tif", full.names = TRUE)

bigmapRasters <- list()
for (file in files) {
  raster <- rast(file)
  name <- tools::file_path_sans_ext(basename(file))
  bigmapRasters[[name]] <- raster
  plot(raster, main = name)
}



bigmapRasters <- lapply(bigmapRasters, function(x) {
  project(x, templateRaster, method = "near") %>%
    crop(., templateRaster) %>%
    mask(., templateRaster)
})

gc()

stack <- rast(bigmapRasters)

topIDX <- app(stack, which.max, na.rm = TRUE)

plot(topIDX)

speciesLevel <- data.frame(
  value = seq_along(names(bigmapRasters)),
  species = names(bigmapRasters)
)

topSpp <- as.factor(topIDX)
levels(topSpp) <- speciesLevel

plot(topSpp)

topSpp %>%
  as.data.frame() %>%
  group_by(species) %>%
  summarise(n = n()) %>%
  ggplot(., aes(x = reorder(species, -n), y = log10(n))) +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))


```


# Raster Calculations

```{r}
directory <- '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters'
files <- list.files(directory, full.names = TRUE, pattern = "\\.tif")
rasters <- list()
for (file in files) {
  filename <-  basename(file)
  parts <- strsplit(filename, "_")[[1]]
  shortName <- paste(parts[1:2], collapse = "_")
  r <- rast(file)
  # if (startsWith(shortName, "B")) {
  #   r <- r / 10000
  # }
  rasters[[shortName]] <- r
}

VV <- rasters$VV_p50 %>% ifel(is.infinite(.), -99, .)
VH <- rasters$VH_p50 %>% ifel(is.infinite(.), -99, .)
VVVH_Plus <- VV + VH
names(VVVH_Plus) <- "VVVH_Plus"
VVVH_Minus <- VV - VH
names(VVVH_Minus) <- "VVVH_Minus"

VHVV_Ratio1 <- VH / VV
names(VHVV_Ratio1) <- "VHVV_Ratio1"

VV_Ratio1 <- VV / (VV + VH)
names(VV_Ratio1) <- "VV_Ratio1"
VH_Ratio1 <- VH / (VV + VH)
names(VH_Ratio1) <- "VH_Ratio1"

HH <- rasters$HH_BWCA %>% project(., templateRaster, method = "near")
names(HH) <- "HH"
HH <- ifel(HH > 0, 10 * log10(HH^2) - 83, NA)
HV <- rasters$HV_BWCA %>% project(., templateRaster, method = "near")
names(HV) <- "HV"
HV <- ifel(HV > 0, 10 * log10(HV^2) - 83, NA)

w5 <- matrix(1, 5, 5) / 25
w7 <- matrix(1, 7, 7) / 49

VH5 <- focal(VH, w = w5, fun = "mean", na.policy = "omit")
names(VH5) <- "VH5"
VH7 <- focal(VH, w = w7, fun = "mean", na.policy = "omit")
names(VH7) <- "VH7"
VV5 <- focal(VV, w = w5, fun = "mean", na.policy = "omit")
names(VV5) <- "VV5"
VV7 <- focal(VV, w = w7, fun = "mean", na.policy = "omit")
names(VV7) <- "VV7"
VHVV5 <- focal(VHVV_Ratio1, w = w5, fun = "mean", na.policy = "omit")
names(VHVV5) <- "VHVV5"
VHVV7 <- focal(VHVV_Ratio1, w = w7, fun = "mean", na.policy = "omit")
names(VHVV7) <- "VHVV7"

HH5 <- focal(HH, w = w5, fun = "mean", na.policy = "omit")
names(HH5) <- "HH5"
HH7 <- focal(HH, w = w7, fun = "mean", na.policy = "omit")
names(HH7) <- "HH7"
HV5 <- focal(HV, w = w5, fun = "mean", na.policy = "omit")
names(HV5) <- "HV5"
HV7 <- focal(HV, w = w7, fun = "mean", na.policy = "omit")
names(HV7) <- "HV7"

gc()

# Get GLCM variables from SAR data
# These need to be integers before I run the code, right now ratio values are continuous
x <- glcm(raster::raster(VHVV_Ratio1), statistics = c("contrast", "dissimilarity", "homogeneity", "variance", "correlation", "mean", "entropy"), n_grey = 8, window = c(21,21))


for (i in 1:raster::nlayers(x)) {
  plot(x[[i]], main = names(x)[i])
}

rastList <- raster::unstack(x)
rastList <- lapply(rastList, rast)
contrast <- rastList[[1]]
dissimilarity <- rastList[[2]]
homogeneity <- rastList[[3]]
variance <- rastList[[4]]
correlation <- rastList[[5]]
mean <- rastList[[6]]
entropy <- rastList[[7]]

# NDBI
ndbi <- (rasters$HH_p50 - rasters$HV_p50) / (rasters$HH_p50 + rasters$HV_p50)
names(ndbi) <- "ndbi"
plot(ndbi)

# NDVI (Normalized Vegetation Difference Index)
ndvi <- (rasters$B8_p50 - rasters$B4_p50) / (rasters$B8_p50 + rasters$B4_p50)
names(ndvi) <- "ndvi"
# EVI (Enhanced Vegetation Index: 1 & 2)
evi <- 2.5 * (((rasters$B8_p50 * 0.0001) - (rasters$B4_p50 * 0.0001)) / ((rasters$B8_p50 * 0.0001) + 6 * (rasters$B4_p50 * 0.0001) - 7.5 * (rasters$B2_p50 * 0.0001) + 1))
names(evi) <- "evi"
evi2 <- 2.5 * ((rasters$B8_p50 - rasters$B4_p50) / (rasters$B8_p50 + 2.4 * rasters$B4_p50 + 1))
names(evi2) <- "evi2"
# RVI (Radar Vegetation Index)
rvi <- rasters$B8_p50 / rasters$B4_p50
names(rvi) <- "rvi"
# PSSRac (Pigment Specific Simple Ratio a)
pssra <- rasters$B7_p50 / rasters$B4_p50
names(pssra) <- "pssra"
# SAVI (Soil Adjusted Vegetation Index)
savi <- ((rasters$B8_p50 - rasters$B4_p50) / (rasters$B8_p50 + rasters$B4_p50 + 0.428)) * (1 + 0.428)
names(savi) <- "savi"
# GNDVI (Green Normalized Difference Vegetation Index)
# Highly correlated with nitrogen, closer to 1 is more nitrogen
gndvi <- (rasters$B8_p50 - rasters$B3_p50) / (rasters$B8_p50 + rasters$B3_p50)
names(gndvi) <- "gndvi"
# NDWI (Normalized Difference Water Index)
ndwi <- (rasters$B3_p50 - rasters$B8_p50) / (rasters$B3_p50 + rasters$B8_p50)
names(ndwi) <- "ndwi"
# NDMI (Normalized Difference Moisture Index)
ndmi <- (rasters$B8_p50 - rasters$B11_p50) / (rasters$B8_p50 + rasters$B11_p50)
names(ndmi) <- "ndmi"

# MODIS
sos <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/Greenup_1_2025_08_03_15_37_26.tif')
eos <- rast('/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/Processed Rasters/Senescence_1_2025_08_03_15_37_36.tif')
los <- eos - sos

# Normalised Burn Ratio
nbr <- (rasters$B8_p50 - rasters$B12_p50) / (rasters$B8_p50 + rasters$B12_p50)
names(nbr) <- "nbr"
nbr2 <- (rasters$B11_p50 - rasters$B12_p50) / (rasters$B11_p50 + rasters$B12_p50)
names(nbr2) <- "nbr2"


plot(nbr)
plot(nbr2)
plot(ndmi)

plot(sos)
plot(eos)
plot(los)

plot(ndvi)
plot(evi)
plot(evi2)
plot(rvi)
plot(pssra)
plot(savi)
plot(gndvi)
plot(ndwi)


blue <- rasters$B2_p50
names(blue) <- "blue"
green <- rasters$B3_p50
names(green) <- "green"
red <- rasters$B4_p50
names(red) <- "red"
nir <- rasters$B8_p50
names(nir) <- "nir"
swir1 <- rasters$B11_p50
names(swir1) <- "swir1"
swir2 <- rasters$B12_p50
names(swir2) <- "swir2"

crs(rasters$B2_p50) == crs(gndvi)

gc()

fortypcdBWCA <- project(fortypcdBWCA_UTM, rasters$B1_p10, method = "near")
slaRast <- project(slaRast, fortypcdBWCA, method = "near")
ldmcRast <- project(ldmcRast, fortypcdBWCA, method = "near")
lpcRast <- project(lpcRast, fortypcdBWCA, method = "near")
lncRast <- project(lncRast, fortypcdBWCA, method = "near")

#----PRISM----#
pptPrism <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/PRISM/Precipitation/PRISM_ppt_30yr_normal_800mM4_annual_bil.bil")
shapefile <- BWCA.shp %>% st_transform(., crs(pptPrism))
pptPrism <- crop(pptPrism, shapefile) %>% mask(., shapefile)
pptPrism <- project(pptPrism, fortypcdBWCA, method = "near")
names(pptPrism) <- "ppt"

plot(pptPrism)

tempPrism <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/PRISM/Temperature/PRISM_tmean_30yr_normal_800mM5_annual_bil.bil")
tempPrism <- crop(tempPrism, shapefile) %>% mask(., shapefile)
tempPrism <- project(tempPrism, fortypcdBWCA, method = "near")
plot(tempPrism)
names(tempPrism) <- "temp"

#----TOPOGRAPHY----#
shapefile <- BWCA.shp %>% st_transform(., crs(fortypcdBWCA))
# Aspect
aspect <- rasters$aspect_2025
aspect <- project(aspect, fortypcdBWCA, method = "near")
aspect <- crop(aspect, shapefile) %>% mask(., shapefile)
aspect <- project(aspect, fortypcdBWCA, method = "near")

# Slope
slope <- rasters$slope_2025
slope <- project(slope, fortypcdBWCA, method = "near")
slope <- crop(slope, shapefile) %>% mask(., shapefile)
slope <- project(slope, fortypcdBWCA, method = "near")

# Elevation
elevation <- rasters$elevation_2025
elevation <- project(elevation, fortypcdBWCA, method = "near")
elevation <- crop(elevation, shapefile) %>% mask(., shapefile)
elevation <- project(elevation, fortypcdBWCA, method = "near")


plot(fortypcdBWCA)


metricsDf %>%
  group_by(uniqueID) %>%
  summarise(CBD = mean(CBD, na.rm = TRUE)) %>%
  ggplot(., aes(x = CBD)) +
  geom_histogram() +
  geom_vline(xintercept = 0.1048578, color = "red", linetype = "dashed")


metricsDf %>%
  mutate(Crown_Biomass_KG = canopy_volume * CBD) %>%
  group_by(uniqueID) %>%
  summarise(Footprint_Total_Biomass = sum(Crown_Biomass_KG, na.rm = T),
            CFL = Footprint_Total_Biomass / (pi * 12.5^2)) %>%
  ggplot(., aes(x = CFL)) +
  geom_histogram() +
  theme_classic()

gc()



metricsDf %>%
  mutate(Crown_Biomass_KG = canopy_volume * CBD) %>%
  group_by(uniqueID) %>%
  summarise(Footprint_Total_Biomass = sum(Crown_Biomass_KG, na.rm = T),
            CFL = Footprint_Total_Biomass / (pi * 12.5^2)) %>%
  arrange(CFL)



metricsDf %>%
  filter(uniqueID == "TWP571309_")


```



```{r}
# Stack that
# This gets to be too big for my RAM so I had to find an alternate way of writing it out
stack <- c(ndvi, gndvi, evi, blue, green, red, nir, swir1, swir2, ndmi, nbr, nbr2, VV, VH, VH5, VH7, VV5, VV7, VHVV5, VHVV7, VVVH_Plus, VVVH_Minus, VHVV_Ratio1, VV_Ratio1, VH_Ratio1, contrast, dissimilarity, homogeneity, entropy, pptPrism, tempPrism, aspect, slope, elevation, HH, HV, HH5, HH7, HV5, HV7)

coords <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/coordinates.csv")
names(coords)

points <- vect(coords, geom = c("x", "y"), crs  = crs(ndvi))
values <- terra::extract(stack, points, ID = FALSE)

stackDf <- cbind(coords, values) %>% drop_na()

data.table::fwrite(stackDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/stackDf.csv")

gc()


gediFootprintDf <- gediMatched %>% group_by(code) %>%
  summarise(across(contains(c("rh", "p_z", "pv")), ~ mean(.x, na.rm = TRUE))) %>%
  rename_with(~ ifelse(startsWith(., "p_z"), sub("^p_z", "pai_", .),
                       ifelse(startsWith(., "pv"), sub("^[^_]+", "pavd", .), .)))


write_csv(gediFootprintDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/gediFootprintDf.csv")


gediFootprintDf <- st_centroid(gediFootprintDf)

X <- st_coordinates(gediFootprintDf)[,1]
Y <- st_coordinates(gediFootprintDf)[,2]

gediFootprintDf$x <- X
gediFootprintDf$y <- Y

stackDf <- st_as_sf(stackDf, coords = c("x", "y"), crs = crs(ndvi))

# st_join(
#   gediFootprintDf,
#   stackDf,
#   join = st_is_within_distance,
#   dist = 100   # meters
# )
# 
# st_crs(gediFootprintDf) == st_crs(stackDf)


idx <- st_nearest_feature(gediFootprintDf, stackDf)

d <- st_distance(
  gediFootprintDf,
  stackDf[idx, ],
  by_element = TRUE
)

joined <- bind_cols(
  gediFootprintDf,
  stackDf[idx, ] |> st_drop_geometry()
) |>
  filter(d <= units::set_units(100, "m"))

write_csv(joined, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/featuresDf.csv")


# CBD values
cbdvalues <- metricsDf %>%
  group_by(uniqueID) %>%
  summarise(CBD = mean(CBD, na.rm = TRUE))

# CFL values
cflvalues <- metricsDf %>%
  mutate(CFL = CBD * canopy_volume) %>%
  group_by(uniqueID) %>%
  summarise(CFL = mean(CFL, na.rm = TRUE))

# CBH values
cbhvalues <- metricsDf %>%
  group_by(uniqueID) %>%
  summarise(CBH = mean(CBH, na.rm = TRUE))

# Z values
zvalues <- metricsDf %>%
  group_by(uniqueID) %>%
  summarise(H = mean(Z, na.rm = TRUE))

# Canopy cover values
ccvalues <- metricsDf %>%
  group_by(uniqueID) %>%
  summarise(CC = mean(CCover, na.rm = TRUE))
  


hist(as.numeric(cbdvalues$CBD), breaks = 30)
hist(as.numeric(cflvalues$CFL), breaks = 30)
hist(as.numeric(cbhvalues$CBH), breaks = 30)
hist(as.numeric(zvalues$H), breaks = 30)
hist(as.numeric(ccvalues$CC), breaks = 30)


targetDf <- st_join(cbdvalues, cflvalues, by = "uniqueID") %>%
  st_join(., cbhvalues, by = "uniqueID") %>%
  st_join(., zvalues, by = "uniqueID") %>%
  st_join(., ccvalues, by = "uniqueID")
targetDf <- targetDf[,-c(1,4,6,8)]
targetDf <- targetDf[,c(6,1,3,4,5,7,2)]

finalDf <- targetDf %>%
  mutate(uniqueID = str_remove(uniqueID, "_$")) %>%
  st_drop_geometry() %>%
  mutate(join_id = str_remove(uniqueID, "_$")) %>%
  left_join(joined %>%
              dplyr::select(-uniqueID), by = c("join_id" = "code")) %>%
  dplyr::select(-join_id)


X <- st_coordinates(finalDf$geometry)[,1]
Y <- st_coordinates(finalDf$geometry)[,2]

coordinates <- finalDf %>% dplyr::select(uniqueID, x, y)

write_csv(coordinates, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/coordinates.csv")

gc()

# # Get FORTYPCD values
# fortypcd <- extract(fortypcdBWCA, finalDf[,c("x", "y")]) %>% rename("FORTYPCD" = "Label") %>% dplyr::select(FORTYPCD)
# 
# finalDf <- cbind(finalDf, fortypcd)

cols_to_drop <- finalDf %>%
  dplyr::select(dplyr::contains(c("pai", "pavd"))) %>%
  dplyr::select(dplyr::where(~ mean(. == 0, na.rm = TRUE) > 0.95)) %>%
  names()

finalDf <- finalDf %>%
  dplyr::select(-dplyr::all_of(cols_to_drop))

rh_cols <- paste0("rh", 0:100)

finalDf <- finalDf %>%
  rowwise() %>%
  mutate(rh_vals = list(c_across(all_of(rh_cols))),
         rh_vals_ground = list(rh_vals[rh_vals >= 0]),
         rh_skewness = if (length(rh_vals_ground) > 2)
      e1071::skewness(unlist(rh_vals_ground), na.rm = TRUE)
    else NA_real_,
    rh_kurtosis = if (length(rh_vals_ground) > 3)
      e1071::kurtosis(unlist(rh_vals_ground), na.rm = TRUE)
    else NA_real_) %>%
  ungroup() %>%
  dplyr::select(-rh_vals, -rh_vals_ground)


finalDf %>%
  mutate(Skew = case_when(
    rh_skewness <= -0.5 ~ "Top",
    rh_skewness < 0.5   ~ "Ladder Fuel",
    TRUE                ~ "Understory"
  )) %>%
  group_by(Skew) %>%
  summarise(n = n(), .groups = "drop") %>%
  ggplot(., aes(x = Skew, y = n, fill = Skew)) +
  geom_bar(stat = "identity") +
  theme_classic()

# Mean PAI 0-10m (m2/m2)
# Like LAI but with the woody biomass thrown in too. Helps to describe understorys that have high biomass
finalDf %>%
  mutate(Mean_PAI_0_10 = base::rowMeans(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  dplyr::select(uniqueID, Mean_PAI_0_10) %>%
  ggplot(., aes(x = Mean_PAI_0_10)) +
  geom_histogram() +
  theme_classic()

# Sum PAI 0-10m
# Alternate way of looking at understory biomass values. DOES SUM MAKE SENSE, I DON'T THINK SO
finalDf %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  dplyr::select(uniqueID, Sum_PAI_0_10) %>%
  ggplot(., aes(x = Sum_PAI_0_10)) +
  geom_histogram() +
  theme_classic()

# Fuel continuity (m2/m3)
# Akin to the vertical distribution of PAI, describes the vertical packing and connectedness of ladder fuels
finalDf %>%
  mutate(
    Fuel_Continuity = rowMeans(dplyr::select(., pavd_0_5, pavd_5_10), na.rm = TRUE),
    Fuel_Continuity_SD = apply(dplyr::select(., pavd_0_5, pavd_5_10), 1, sd, na.rm = TRUE)) %>%
  dplyr::select(uniqueID, Fuel_Continuity, Fuel_Continuity_SD) %>%
  ggplot(., aes(x = Fuel_Continuity)) +
  geom_histogram() +
  theme_classic()

# Ladderfuel ratio
# This ratio quantifies the relative abundance of lower-canopy fuels (0-10m PAI) compared to canopy fuels (10-30m PAI),
# representing vertical fuel connectivity 
finalDf %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(LCR = Sum_PAI_0_10 / base::rowSums(dplyr::select(., pai_10_15:pai_30_35), na.rm = TRUE)) %>%
  dplyr::select(uniqueID, Sum_PAI_0_10, LCR) %>%
  filter(LCR < 50) %>%
  ggplot(., aes(x = LCR)) +
  geom_histogram() +
  theme_classic()

options(GGally.progress = FALSE)

finalDf %>%
  mutate(Mean_PAI_0_10 = base::rowMeans(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Fuel_Continuity = rowMeans(dplyr::select(., pavd_0_5, pavd_5_10), na.rm = TRUE),
         Fuel_Continuity_SD = apply(dplyr::select(., pavd_0_5, pavd_5_10), 1, sd, na.rm = TRUE)) %>%
  mutate(LCR = Sum_PAI_0_10 / base::rowSums(dplyr::select(., pai_10_15:pai_30_35), na.rm = TRUE)) %>%
  dplyr::select(Mean_PAI_0_10, Sum_PAI_0_10, Fuel_Continuity, LCR, rh_skewness, rh_kurtosis) %>%
  mutate(LCR = ifelse(is.infinite(LCR), median(LCR, na.rm = TRUE), LCR)) %>%
  GGally::ggpairs(progress = FALSE)


finalDf %>%
  mutate(Mean_PAI_0_10 = base::rowMeans(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Fuel_Continuity = rowMeans(dplyr::select(., pavd_0_5, pavd_5_10), na.rm = TRUE),
         Fuel_Continuity_SD = apply(dplyr::select(., pavd_0_5, pavd_5_10), 1, sd, na.rm = TRUE)) %>%
  mutate(LCR = Sum_PAI_0_10 / base::rowSums(dplyr::select(., pai_10_15:pai_30_35), na.rm = TRUE)) %>%
  mutate(LCR = ifelse(is.infinite(LCR), median(LCR, na.rm = TRUE), LCR)) %>%
  ggplot(., aes(x = pavd_0_5, y = Fuel_Continuity)) +
  geom_point() +
  geom_smooth() +
  theme_classic()


# LCR is ladder:canopy ratio
finalDf %>%
  mutate(Mean_PAI_0_10 = base::rowMeans(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Fuel_Continuity = rowMeans(dplyr::select(., pavd_0_5, pavd_5_10), na.rm = TRUE),
         Fuel_Continuity_SD = apply(dplyr::select(., pavd_0_5, pavd_5_10), 1, sd, na.rm = TRUE)) %>%
  mutate(LCR = Sum_PAI_0_10 / base::rowSums(dplyr::select(., pai_10_15:pai_30_35), na.rm = TRUE)) %>%
  mutate(LCR = ifelse(is.infinite(LCR), median(LCR, na.rm = TRUE), LCR))


names(finalDf)


finalDf %>%
  pivot_longer(
    cols = starts_with("pai_"),
    names_to = "height_bin",
    values_to = "pai"
  ) %>%
  mutate(
    height_bin = str_remove(height_bin, "pai_"),
    height_class = case_when(
      height_bin == "0_5m"  ~ 5,
      height_bin == "5_10"  ~ 10,
      height_bin == "10_15" ~ 15,
      height_bin == "15_20" ~ 20,
      height_bin == "20_25" ~ 25,
      height_bin == "25_30" ~ 30,
      height_bin == "30_35" ~ 35
    )
  ) %>%
  group_by(height_class) %>%
  summarise(mean_pai = mean(pai, na.rm = TRUE)) %>%
  ggplot(., aes(x = mean_pai, y = height_class)) +
  geom_line(linewidth = 1.2, color = "forestgreen") +
  geom_point(size = 2, color = "forestgreen") +
  scale_y_continuous(name = "Height (m)", limits = c(0, 35)) +
  scale_x_continuous(name = "Mean PAI") +
  theme_minimal()


# set.seed(NULL)  # for reproducibility

finalDf %>%
  filter(uniqueID %in% sample(unique(uniqueID), 10)) %>%
  pivot_longer(
    cols = starts_with("pavd_"),
    names_to = "height_bin",
    values_to = "pavd"
  ) %>%
  mutate(
    height_bin = str_remove(height_bin, "pavd_"),
    height_class = c(5, 10, 15, 20, 25, 30, 35, 40)[match(
      height_bin,
      c("0_5", "5_10", "10_15", "15_20", "20_25", "25_30", "30_35", "35_40")
    )]
  ) %>%
  ggplot(aes(x = pavd, y = height_class)) +
  geom_line(alpha = 0.6) +
  stat_summary(fun = mean, geom = "line", linewidth = 1.2, color = "black") +
  facet_wrap(~ uniqueID, ncol = 5) +
  scale_y_continuous("Height (m)") +
  scale_x_continuous("PAVD (m²/m³)") +
  theme_minimal()


finalDf %>%
  filter(uniqueID %in% sample(unique(uniqueID), 10)) %>%
  pivot_longer(
    cols = starts_with("rh"),
    names_to = "rh_bin",
    values_to = "height"
  ) %>%
  mutate(
    rh_pct = as.numeric(str_remove(rh_bin, "rh"))
  ) %>%
  ggplot(., aes(x = rh_pct, y = height)) +
  geom_path(linewidth = 1.2) +
  # scale_y_continuous("Height (m)") +
  # scale_x_continuous("RH percentile (%)", limits = c(0, 100)) +
  theme_minimal() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  facet_wrap(~ uniqueID, ncol = 5)

# LCR is ladder:canopy ratio
# PAI tells us overall fuel availability, akin to LAI but with woody matter in there too
# PAVD tells us where the fuel is in regards to it's vertical distribution
finalDf <- finalDf %>%
  mutate(Mean_PAI_0_10 = base::rowMeans(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Sum_PAI_0_10 = base::rowSums(dplyr::select(., pai_0_5m, pai_5_10), na.rm = TRUE)) %>%
  mutate(Fuel_Continuity = rowMeans(dplyr::select(., pavd_0_5, pavd_5_10), na.rm = TRUE),
         Fuel_Continuity_SD = apply(dplyr::select(., pavd_0_5, pavd_5_10), 1, sd, na.rm = TRUE)) %>%
  mutate(LCR = Sum_PAI_0_10 / base::rowSums(dplyr::select(., pai_10_15:pai_30_35), na.rm = TRUE)) %>%
  mutate(LCR = ifelse(is.infinite(LCR), median(LCR, na.rm = TRUE), LCR))



colSums(is.na(finalDf)) %>% as.data.frame()

finalDf <- finalDf %>%
  filter(!if_any(contains("rh"), is.na))



write_csv(finalDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/BWCA_All_Variables.csv")

#finalDf <- finalDf[,-c(8:31,33:56,58:81,83:96)]
#
#write_csv(finalDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/BWCA_Reduced_Variables.csv")



gc()

finalDf %>%
  filter(uniqueID %in% sample(unique(uniqueID), 10)) %>%
  pivot_longer(
    cols = starts_with("pavd_"),
    names_to = "pavd_bin",
    values_to = "pavd"
  ) %>%
  mutate(
    h_min = as.numeric(str_extract(pavd_bin, "(?<=_)[0-9]+")),
    h_max = as.numeric(str_extract(pavd_bin, "(?<=_)[0-9]+(?=$)")),
    height_mid = (h_min + h_max) / 2
  ) %>%
  ggplot(aes(x = pavd, y = height_mid)) +
  geom_path(linewidth = 1.2) +
  scale_y_continuous("Height (m)", expand = c(0, 0)) +
  scale_x_continuous("PAVD (m² m⁻³)", expand = c(0, 0)) +
  theme_minimal() +
  facet_wrap(~ uniqueID, ncol = 5)

# Here I convert total plant area into a gap fraction / transmittance using the Beer–Lambert law,
# assuming a fixed light extinction through the canopy.
thetaDegree <- 0:38
thetaRadians <- thetaDegree * pi / 180
finalDf <- finalDf %>%
  mutate(Total_PAI = rowSums(across(c("pai_30_35":"pai_0_5m"))),
         CGF = exp(-0.5 * 1 * Total_PAI))
  
# Here I calculate the CGF by the different zenith's like they do in Wolter et al. (2021), again using the
# Beer-Lambert transmittancde equation from above, but now for all the zeniths of interest
G <- 0.5
Omega <- 1
angleBins <- list(bin1 = 0:7, bin2 = 0:23, bin3 = 0:38)
CGFList <- list()

for (bin in names(angleBins)) {
  anglesDegree <- angleBins[[bin]]
  anglesRadians <- anglesDegree * pi /180
  CGFmatrix <- sapply(anglesRadians, function(theta) exp(-G * Omega * finalDf$Total_PAI / cos(theta)))
  CGFaverage <- rowMeans(CGFmatrix)
  CGFList[[bin]] <- CGFaverage
}

cgfBins <- as.data.frame(CGFList) %>%
  `colnames<-`(c("CGF_0-7", "CGF_0-23", "CGF_0-38"))

finalDf <- cbind(finalDf, cgfBins)

# I use the midpoint of the zenith angles to calculate CBD from each CGF interval,
# adjusting the CGF values based on viewing angle. This is based on equation 1 from
# Wolter et al. (2021)
theta <- c(
  "CGF_0-7"  = 3.5,
  "CGF_0-23" = 11.5,
  "CGF_0-38" = 19
) * pi / 180

finalDf <- finalDf %>%
  mutate(
    CBD_0_7 =
      (-log(`CGF_0-7`)  * sin(theta["CGF_0-7"])  * cos(theta["CGF_0-7"])) / 2,

    CBD_0_23 =
      (-log(`CGF_0-23`) * sin(theta["CGF_0-23"]) * cos(theta["CGF_0-23"])) / 2,

    CBD_0_38 =
      (-log(`CGF_0-38`) * sin(theta["CGF_0-38"]) * cos(theta["CGF_0-38"])) / 2
  )


finalDf %>%
  dplyr::select(CBD_0_7, CBD_0_23, CBD_0_38)%>%
  pivot_longer(
    cols = c(CBD_0_7, CBD_0_23, CBD_0_38),
    names_to = "group",
    values_to = "value"
  ) %>%
  ggplot(., aes(x = value, fill = group)) +
  geom_histogram(
    alpha = 0.5,
    position = "identity",
    bins = 30
  ) +
  theme_classic()

gc()


# Create matrices used to smooth the SAR rasters.
# TODO: MOVE TO IT'S RIGHTFUL PLACE SOMEWHERE ABOVE HERE FOR THE CLEAN VERSION
# INFACT MICH OF WHAT IS BELOW HERE WILL NEED TO BE REORGANISED
# w5 <- matrix(1, 5, 5) / 25
# w7 <- matrix(1, 7, 7) / 49
# 
# VH5 <- focal(VH, w = w5, fun = "mean", na.policy = "omit")
# VH7 <- focal(VH, w = w7, fun = "mean", na.policy = "omit")
# VV5 <- focal(VV, w = w5, fun = "mean", na.policy = "omit")
# VV7 <- focal(VV, w = w7, fun = "mean", na.policy = "omit")
# VHVV5 <- focal(VHVV_Ratio1, w = w5, fun = "mean", na.policy = "omit")
# VHVV7 <- focal(VHVV_Ratio1, w = w7, fun = "mean", na.policy = "omit")
# 
# HH5 <- focal(HH, w = w5, fun = "mean", na.policy = "omit")
# HH7 <- focal(HH, w = w7, fun = "mean", na.policy = "omit")
# HV5 <- focal(HV, w = w5, fun = "mean", na.policy = "omit")
# HV7 <- focal(HV, w = w7, fun = "mean", na.policy = "omit")


plot(VH)
plot(VH5)
plot(VH7)
plot(VV)
plot(VV5)
plot(VV7)
plot(VHVV_Ratio1)
plot(VHVV5)
plot(VHVV7)

plot(HH)
plot(HH5)
plot(HH7)
plot(HV)
plot(HV5)
plot(HV7)

gc()
# wolterSAR <- c(VH5, VH7, VV5, VV7, VHVV5, VHVV7, HH, HH5, HH7, HV, HV5, HV7) %>%
#   terra::extract(., vect(finalDf$geometry)) %>%
#   `colnames<-`(c("ID", "VH5", "VH7", "VV5", "VV7", "VHVV5", "VHVV7", "HH", "HH5", "HH7", "HV", "HV5", "HV7")) %>%
#   dplyr::select(-ID)

# finalDf <- cbind(finalDf, wolterSAR)

finalDf <- finalDf %>% drop_na()


scaledDf1 <- finalDf %>%
  dplyr::select(-uniqueID, -geometry, -x, -y, -CBD, -CFL, -CBH, -H, -CC, -CBD_0_7, -CBD_0_23, -CBD_0_38, -CGF, -`CGF_0-7`, -`CGF_0-23`, -`CGF_0-38`) %>%
  scale(.)
scaledDf1 <- cbind(finalDf$CBD_0_7, scaledDf1) %>% as.data.frame() %>% rename("CBD_0_7" = "V1")


scaledDf2 <- finalDf %>%
  dplyr::select(VH, VH5, VH7, VV, VV5, VV7, VHVV_Ratio1, VHVV5, VHVV7, HH, HH5, HH7, HV, HV5, HV7, glcm_contrast, glcm_dissimilarity, glcm_homogeneity, glcm_entropy) %>%
  scale(.)

gc()

# pls.1 <- plsr(finalDf$CBD_0_7 ~ as.matrix(scaledDf1), ncomp = 6, validation = "LOO")
pls.1 <- plsr(CBD_0_7 ~ ., 
              data = scaledDf1,
              ncomp = 1,
              validation = "LOO",
              scale = FALSE)
summary(pls.1)

pls.1 <- plsr(CBD_0_7 ~ ., 
              data = scaledDf1,
              ncomp = 1,
              validation = "CV",
              scale = FALSE,
              segments = 10)
summary(pls.1)

# A single latent component derived from your 164 predictors is enough to explain ~97% of the variation in CBD_0_7, 
# and it predicts new data very accurately (RMSEP ≈ 0.0043). This result is robust to different cross-validation 
# schemes and shows no obvious signs of overfitting.

validationplot(pls.1)
coef(pls.1) %>% as.data.frame() %>% arrange(desc(abs(`CBD_0_7.1 comps`)))
explvar(pls.1)
R2(pls.1)



# VIP Method, still lots of variables
vip <- function(pls.obj) {
  W <- pls.obj$loading.weights
  `T` <- pls.obj$scores
  Q <- pls.obj$Yloadings
  
  p <- nrow(W)
  h <- ncol(W)
  
  SSY <- colSums((T %*% diag(Q))^2)
  vip <- sqrt(p * rowSums(W^2 %*% diag(SSY)) / sum(SSY))
  
  return(vip)
}

vip_scores <- vip(pls.1)
keep_vars <- names(vip_scores[vip_scores >= 1])
scaledDf_vip <- scaledDf1[, c("CBD_0_7", keep_vars)]

```
pls.vip <- plsr(
  CBD_0_7 ~ ., 
  data = scaledDf_vip,
  ncomp = 1,
  validation = "CV",
  segments = 10,
  scale = FALSE
)

summary(pls.vip)

# Bootstrapping PLS fits
set.seed(33)
B <- 200
coef_mat <- matrix(NA, nrow = B, ncol = ncol(scaledDf1) - 1)
colnames(coef_mat) <- colnames(scaledDf1)[-1]

for (b in 1:B) {
  idx <- sample(1:nrow(scaledDf1), replace = TRUE)
  
  pls.b <- plsr(
    CBD_0_7 ~ ., 
    data = scaledDf1[idx, ],
    ncomp = 1,
    scale = FALSE
  )
  
  coef_mat[b, ] <- coef(pls.b)[, , 1]
}

coef_mean <- apply(coef_mat, 2, mean)
coef_sd   <- apply(coef_mat, 2, sd)
stability <- abs(coef_mean) / coef_sd

keep_vars <- names(stability[stability > 1])
scaledDf_stable <- scaledDf1[, c("CBD_0_7", keep_vars)]

pls.stable <- plsr(
  CBD_0_7 ~ ., 
  data = scaledDf_stable,
  ncomp = 1,
  validation = "CV",
  segments = 10,
  scale = FALSE
)

summary(pls.stable)

```

scaledDf1 %>% as.data.frame() %>% names()

rmse <- RMSEP(pls.1)$val[1, , ]
ncomp_opt <- which.min(rmse)


pls.2 <- plsr(finalDf$CBD_0_7 ~ as.matrix(scaledDf), ncomp = ncomp_opt)

summary(pls.2)

pred <- predict(pls.1, ncomp = 6)
R2 <- cor(pred, finalDf$CBD_0_7)^2
R2


hist(finalDf$CBD_0_7)

testDf <- cbind(finalDf$CBD_0_7, scaledDf1) %>%
  as.data.frame() %>%
  rename("CBD_0_7" = "V1")


write_csv(testDf, "/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/TEST_CBD_7.csv")
```
# ---------------------------
# 1) Load VH & VV rasters (in dB, same CRS/resolution)
# ---------------------------
vh <- rasterList[[1]]  # VH (dB)
vv <- rasterList[[8]]  # VV (dB)

# ---------------------------
# 2) 5x5 and 7x7 low-pass filters (mean)
# ---------------------------
w5 <- matrix(1, 5, 5) / 25
w7 <- matrix(1, 7, 7) / 49

vh5 <- focal(vh, w = w5, fun = "mean", na.policy = "omit")
vh7 <- focal(vh, w = w7, fun = "mean", na.policy = "omit")
vv5 <- focal(vv, w = w5, fun = "mean", na.policy = "omit")
vv7 <- focal(vv, w = w7, fun = "mean", na.policy = "omit")

# ---------------------------
# 3) VH:VV ratio in dB space = VH_dB - VV_dB
#    (equivalent to log10(VH_lin/VV_lin) scaled; this matches the usual treatment in dB)
# ---------------------------
vhvv   <- vh  - vv      # unfiltered ratio (dB)
vhvv5  <- vh5 - vv5     # 5x5 ratio (dB)
vhvv7  <- vh7 - vv7     # 7x7 ratio (dB)

```



#####################################

# DO NOT DELETE. I'm going try making a final df again above

```{r}
# Stack that
stack <- c(ndvi, gndvi, evi, blue, green, red, nir, swir1, swir2, ndmi, nbr, nbr2, HH, HV, pptPrism, tempPrism, aspect, slope, elevation)
stackDf <- stack %>% as.data.frame(xy = TRUE)

# Get all tbe data without any NAs, we will use this to train on later
stackDf <- stackDf %>% drop_na()

treDf <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelCalc/BWCA-Out.csv")
treDf <- treDf[-1,] %>% mutate(across(where(is.character), as.numeric)) %>% cbind(treDf[-1,], .)
treDf$PlotID <- gsub("-Baseline", "", treDf$PlotID)

# Average the values of individual trees back to the footprint level
gediFootprintDf <- gediMatched %>% group_by(code) %>%
  summarise(across(contains(c("rh", "p_z", "pv")), ~ mean(.x, na.rm = TRUE))) %>%
  rename_with(~ ifelse(startsWith(., "p_z"), sub("^p_z", "pai_", .),
                       ifelse(startsWith(., "pv"), sub("^[^_]+", "pavd", .), .)))

# Create a dataframe with all of the target data in it
targetDf <- inner_join(treDf[,c(1,2,4,6,10,18,24)],
           metricsDf %>% group_by(uniqueID) %>% summarise(HT = max(Z), CC = max(CCover)),
           by = c("PlotID" = "uniqueID"))
targetDf <- targetDf %>% filter(preCFL != 0)

# Create the final table and remove columns where they are all 0s
finalTable <- targetDf %>%
  mutate(PlotID = gsub("_", "", .$PlotID)) %>%
  inner_join(gediFootprintDf, by = c("PlotID" = "code"))
# finalTable <- finalTable %>% select(where(~ !is.numeric(.) || any(. != 0)))

# Get the centroid of the footprint from the trees in that footprint
finalTable$geometry <- st_centroid(finalTable$geometry.x)

data <- extract(stack, st_as_sf(finalTable$geometry))

finalTable <- cbind(finalTable, data[,-1])


##################
# Canopy Bulk Density
CBD <- finalTable[,-c(10, 172, 173)]
CBD <- CBD[, -c(1,2,4:9)]

CBD <- CBD %>% drop_na()

CBD <- CBD %>% mutate(across(where(is.numeric), scale),
               preCBD = as.numeric(preCBD))

CBD <- CBD[,-c(3:26,28:51,53:76,78:91)]

summarise(across(where(is.numeric), sum, na.rm = TRUE))

# coords <- cbind(st_coordinates(finalTable$geometry)[,1], st_coordinates(finalTable$geometry)[,2])
# groups <- kmeans(coords, centers = 10)$cluster
# CBD$cluster <- groups
# CBD$geometry <- finalTable$geometry
# CBD <- st_as_sf(CBD)

hist(CBD$preCBD)

target_var <- "preCBD"



hist(cbdvalues$CDB)

# Create formula
form <- as.formula(paste(target_var, "~ ."))

# --- Set up training control ---
set.seed(33)
ctrl <- trainControl(
  method = "cv",          # cross-validation
  number = 5,             # 5-fold CV
  verboseIter = TRUE
)

# --- Train random forest model ---
rf_model <- train(
  form,
  data = CBD,
  method = "rf",
  trControl = ctrl,
  tuneLength = 5,
  importance = TRUE
)

# --- Inspect results ---
print(rf_model)
varImp(rf_model)
plot(rf_model)

rf_model$trainingData %>% names()



control <- trainControl(method="cv", number=5)

grid <- expand.grid(mtry=c(2, 5, 10, 20, 40),
                    splitrule="variance",
                    min.node.size=c(1, 5, 10))

rf_model <- train(
  preCBD ~ ., data = CBD,
  method = "ranger",
  tuneGrid = grid,
  trControl = control,
  importance = 'impurity'
)

print(rf_model)
varImp(rf_model)
plot(rf_model)

hist(CBD$preCBD)

summary(CBD$preCBD)


gediMatched %>%
  as.data.frame()


BWCA_UTM.shp <- st_transform(BWCA.shp, 26915)
predpts <- spatSample(fortypcdBWCA, size = 2000, method = "regular", as.points = TRUE)
CBD <- st_transform(CBD, st_crs(predpts))
predpts_sf <- st_as_sf(predpts)

knndmFolds <- knndm(tpoints = CBD,
                    predpoints = predpts_sf,
                    k = 10,
                    samplesize = 5000)


ctrl <- trainControl(
  method = "cv",
  number = k,
  index = trainIndices,
  indexOut = testIndices,
  search = "grid"
)

grid <- expand.grid(mtry = c(5, 10, 15, 30))

model <- train(
  Z ~ ., 
  data = testZ,
  method = "rf",
  trControl = ctrl,
  importance = TRUE,
  ntree = 100
  # tuneGrid = grid
)

gediMatched
```




```{r}
RI <- c(3,2,2,3)

L_full <- 484
L_sim <- 100
lambda <- 1 / RI
lambdaTotal <- sum(lambda)
lambdaSim <- lambdaTotal * (L_sim / L_full)

k <- 0:10
prob <- dpois(0:10, lambdaSim)

round(prob, 2)
prob_cum <- ppois(k, lambdaSim)



probOld <- dpois(0:10, lambdaTotal)

cbind(prob, probOld) %>%
  as.data.frame() %>%
  mutate(ID = 0:10) %>%
  pivot_longer(cols = "prob":"probOld", values_to = "Value", names_to = "Name") %>%
  mutate(Name = case_when(
    Name == "prob" ~ "Simulated NC Coastline",
    TRUE ~ "Full NC Coastline"
  )) %>%
  ggplot(., aes(x = ID, y = Value, col = Name, shape = Name)) +
  geom_point(size = 2.5) +
  geom_line(size = 1) +
  theme_classic() +
  scale_x_continuous(name = "Number of Storm Events",
                     breaks = 0:10) +
  ylab("Probability of landfall") +
  labs(color = "Coastline Type", shape = "Coastline Type") +
  theme(legend.position = "bottom")
```


# Low r2 verison

```{r}
gediMatched <- st_read("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Shapefiles/gediMatched.shp")


# Some of the GEE files have slightly different dimensions so some files need to
# be projected so they can all be stacked
fortypcdBWCA <- project(fortypcdBWCA_UTM, rasters$B1_p10, method = "near")
slaRast <- project(slaRast, fortypcdBWCA, method = "near")
ldmcRast <- project(ldmcRast, fortypcdBWCA, method = "near")
lpcRast <- project(lpcRast, fortypcdBWCA, method = "near")
lncRast <- project(lncRast, fortypcdBWCA, method = "near")

#----PRISM----#
pptPrism <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/PRISM/Precipitation/PRISM_ppt_30yr_normal_800mM4_annual_bil.bil")
shapefile <- BWCA.shp %>% st_transform(., crs(pptPrism))
pptPrism <- crop(pptPrism, shapefile) %>% mask(., shapefile)
pptPrism <- project(pptPrism, fortypcdBWCA, method = "near")

plot(pptPrism)

tempPrism <- rast("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/PRISM/Temperature/PRISM_tmean_30yr_normal_800mM5_annual_bil.bil")
tempPrism <- crop(tempPrism, shapefile) %>% mask(., shapefile)
tempPrism <- project(tempPrism, fortypcdBWCA, method = "near")
plot(tempPrism)

rastList <- lapply(rastList, function(x) {
  project(x, fortypcdBWCA, method = "near")
})


contrast <- rastList[[1]]
dissimilarity <- rastList[[2]]
homogeneity <- rastList[[3]]
variance <- rastList[[4]]
correlation <- rastList[[5]]
mean <- rastList[[6]]
entropy <- rastList[[7]]


# Create the stack
fullStack <- c(rasters$B1_p50,
  rasters$B2_p50,
  rasters$B3_p50,
  rasters$B4_p50,
  rasters$B5_p50,
  rasters$B6_p50,
  rasters$B7_p50,
  rasters$B8_p50,
  rasters$B8A_p50,
  rasters$B11_p50,
  rasters$B12_p50,
  rasters$B1_p10,
  rasters$B2_p10,
  rasters$B3_p10,
  rasters$B4_p10,
  rasters$B5_p10,
  rasters$B6_p10,
  rasters$B7_p10,
  rasters$B8_p10,
  rasters$B8A_p10,
  rasters$B11_p10,
  rasters$B12_p10,
  rasters$B1_p95,
  rasters$B2_p95,
  rasters$B3_p95,
  rasters$B4_p95,
  rasters$B5_p95,
  rasters$B6_p95,
  rasters$B7_p95,
  rasters$B8_p95,
  rasters$B8A_p95,
  rasters$B11_p95,
  rasters$B12_p95,
  fortypcdBWCA,
 ndvi,
 evi,
 evi2,
 rvi,
 pssra,
 savi,
 gndvi,
 ndwi,
 ldmcRast,
 slaRast,
 lpcRast,
 lncRast,
 contrast,
 dissimilarity,
 homogeneity,
 variance,
 correlation,
 mean,
 entropy
 )

# fractionsDf <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/out_GEDI_PLOT.csv")
# fractionsDf <- fractionsDf %>% unique()
# fractionsDf <- fractionsDf %>% mutate(uniqueID = str_sub(uniqueID, end = -2)) %>%
#   group_by(uniqueID) %>% summarise(across(where(is.numeric), sum, na.rm = TRUE))


treDf <- read_csv("/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/FuelCalc/BWCA-Out.csv")
treDf <- treDf[-1,-1] %>% 
  mutate(across(where(is.character), as.numeric)) %>%
  cbind(treDf[-1,1], .)

# treDf %>% mutate(allID = paste0("uID_", PlotID)) %>%
#   inner_join(., fractionsDf, by = c("allID" = "PlotID"))
# 
# metricsDf <- metricsDf %>% mutate(allID = paste0("uID_", uniqueID)) %>%
#   inner_join(., fractionsDf, by = c("allID" = "uniqueID"))

gediFootprintDf <- gediMatched %>% group_by(code) %>%
  summarise(across(contains(c("rh", "p_z", "pv")), ~ mean(.x, na.rm = TRUE))) %>%
  rename_with(~ ifelse(startsWith(., "p_z"), sub("^p_z", "pai_", .),
                       ifelse(startsWith(., "pv"), sub("^[^_]+", "pavd", .), .)))

metricsDf

treDf$PlotID <- gsub("-Baseline", "", treDf$PlotID)

targetDf <- inner_join(treDf[,c(1,2,4,6,10,18,24)],
           metricsDf %>% group_by(uniqueID) %>% summarise(HT = max(Z), CC = max(CCover)),
           by = c("PlotID" = "uniqueID"))

targetDf <- targetDf %>% filter(preCFL != 0)

finalTable <- targetDf %>%
  mutate(PlotID = gsub("_", "", .$PlotID)) %>%
  inner_join(gediFootprintDf, by = c("PlotID" = "code"))

finalTable <- finalTable %>% select(where(~ !is.numeric(.) || any(. != 0)))

finalTable$geometry <- st_centroid(finalTable$geometry)

data <- extract(fullStack, st_as_sf(finalTable))

finalTable <- cbind(finalTable, data[,-1])


finalTable <- finalTable %>% mutate(glcm_correlation = ifelse(glcm_correlation == Inf | glcm_correlation == -Inf, mean(glcm_correlation), glcm_correlation))

finalTable <- finalTable %>% drop_na()

scaleTable <- finalTable[,-c(1,162)] %>% mutate(Label = as.numeric(Label)) %>% scale() %>% as.data.frame() %>% cbind(finalTable[,1],.) %>%
  rename("PlotID" = "finalTable[, 1]")



hist(finalTable$preCFL)

hist(finalTable$ndwi)
```


pcaTable <- scaleTable[, -c(1:9)]
pcaTable <- pcaTable[, -c(1:9)]

# non_constant_cols <- apply(as.matrix(pcaTable), 2, function(col) sd(col, na.rm = TRUE) != 0)
# non_constant_cols %>% as.data.frame() %>% filter(. == FALSE)

pcaOutput <- prcomp(pcaTable)
pcaDf <- as.data.frame(pcaOutput$x)
pcaDf$groups <- finalTable$Label
centroids <- aggregate(cbind(PC1,PC2) ~ groups, pcaDf, "mean")

valid_groups <- unique(pcaDf$groups[sapply(split(pcaDf, pcaDf$groups), function(df) {
  sum(complete.cases(df[, c("PC1", "PC2")])) >= 2
})])

# Generate ellipses
conf.rgn <- do.call(rbind, lapply(valid_groups, function(t) {
  subdf <- pcaDf[pcaDf$groups == t, c("PC1", "PC2")]
  if (nrow(subdf) < 2 || anyNA(subdf)) return(NULL)

  centre_row <- centroids[centroids$groups == t, c("PC1", "PC2")]
  if (nrow(centre_row) == 0 || anyNA(centre_row)) return(NULL)

  ell <- ellipse::ellipse(cov(subdf), centre = as.matrix(centre_row), level = 0.95)
  data.frame(groups = as.character(t), ell)
}))


# Plot PC1 and PC2
ggplot(data = pcaDf, aes(x = PC1, y = PC2, group = as.factor(groups), color = as.factor(groups))) + 
    # geom_polygon(data = conf.rgn, aes(fill = groups), alpha = 0.05) +
    geom_point(size = 1, alpha = 0.1) + 
  labs(title = "Principal Component Analysis of Scotland Tree Types: PC1 and PC2") +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
  theme(legend.position = "none") +
  ylim(-20,20) +
  xlim(-30,20)


summary(pcaOutput) # 31, 0.99
pcaOutput$rotation %>% as.data.frame() %>% select(PC26) %>% arrange(PC26)
# rh61, pai_70_75, B8A_p50, B2_p95, B4_p95, rh0, rh0, LNC_1km_v1, glcm_dissimilarity
# B6_p10, pavd_35_40, glcm_variance, pavd_30_35, B1_p10, glcm_correlation, glcm_correlation, Label, Label
# pavd_0_5, B1_p50, B1_p95, B4_p10, pavd_35_40, SLA_1km_v1, glcm_entropy

scaleTable1 <- scaleTable %>% select(preCFL, rh61, pai_70_75, B8A_p50, B2_p95, B4_p95, rh0, rh0, LNC_1km_v1, glcm_dissimilarity, B6_p10, pavd_35_40, glcm_variance, pavd_30_35, B1_p10, glcm_correlation, glcm_correlation, Label, Label, pavd_0_5, B1_p50, B1_p95, B4_p10, pavd_35_40, SLA_1km_v1, glcm_entropy)

# MACHINE LEARNING
ctrl <- trainControl(
  method = "cv",      # 10-fold cross-validation
  number = 5,
  verboseIter = FALSE
)

xgb_model <- train(
  preCFL ~ .,
  data = scaleTable1,
  method = "xgbTree",
  trControl = ctrl,
  # tuneGrid = grid,
  metric = "RMSE"
)


sum(is.na(scaleTable))


var(scaleTable$preCFL)
```

metricsDf <- metricsDf %>% mutate(allID = paste0("uID_", uniqueID)) %>%
  inner_join(., fractionsDf, by = c("allID" = "uniqueID"))

gediFootprintDf <- gediMatched %>% group_by(code) %>%
  summarise(across(contains(c("rh", "p_z", "pv")), ~ mean(.x, na.rm = TRUE))) %>%
  rename_with(~ ifelse(startsWith(., "p_z"), sub("^p_z", "pai_", .),
                       ifelse(startsWith(., "pv"), sub("^[^_]+", "pavd", .), .)))

finalTable <- left_join(metricsDf %>% mutate(uniqueID = str_sub(uniqueID, end = -2)),
          gediFootprintDf %>% st_drop_geometry(),
          by = c("uniqueID" = "code"))

# Because this is still in multipoint geometry for each indiviudal tree for each
# GEDI footprint I am taking the centroid of the trees in each footprint and that
# will be the singular point which defines each footprint in space
centroids <- st_centroid(finalTable$geom)

finalTable <- finalTable %>% st_drop_geometry()

finalTable <- cbind(finalTable, centroids)

finalTable <- st_as_sf(finalTable)

x <- extract(fullStack, finalTable) # still extracting tree points instead of footprint point. need to fix

mode <- function(x) {
  x <- na.omit(x)
  if (length(x) == 0) return(NA)
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

x <- x %>% group_by(ID) %>% summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)),
                                 Label = mode(Label)) %>%
  mutate(across(starts_with("B"), ~ .x / 10000))

finalTable <- cbind(finalTable, x[,-1])

glcmCols <- c("glcm_contrast", "glcm_dissimilarity", "glcm_homogeneity", "glcm_variance", "glcm_correlation", "glcm_mean", "glcm_entropy")

finalTable <- finalTable %>% filter(!if_all(all_of(glcmCols), is.na))

finalTable <- finalTable %>% 
  mutate(across(
    all_of(glcmCols),
    ~ {
      med <- median(.[!is.infinite(.) & !is.na(.)], na.rm = TRUE)
      ifelse(is.na(.) | is.infinite(.), med, .)
    }
  ))

# Here I am doing some extra cleaning by removing the columns that are only 0s
finalTable <- finalTable %>% select(-frac_Bur.oak, -frac_Elm...ash...black.locust, -frac_Lodgepole.pine, -frac_Other.hardwoods, -frac_Silver.maple...American.elm, -frac_Sugarberry...hackberry...elm...green.ash, -pai_130_135, -pai_135_140, -pai_140_145, -pai_145_150, -pavd_135_140, -pavd_140_145, -pavd_145_150) %>%
  drop_na()



pcaTable <- finalTable
pcaTable <- pcaTable[, -c(1:9)]
pcaTable <- pcaTable %>% mutate(LabelNumeric = as.numeric(Label)) %>% as.data.frame() %>% st_drop_geometry() %>% select(-Label, -geometry)


non_constant_cols <- apply(as.matrix(pcaTable), 2, function(col) sd(col, na.rm = TRUE) != 0)
non_constant_cols %>% as.data.frame() %>% filter(. == FALSE)


pcaOutput <- prcomp(pcaTable, scale = TRUE, center = TRUE)
pcaDf <- as.data.frame(pcaOutput$x)
pcaDf$groups <- finalTable$Label
centroids <- aggregate(cbind(PC1,PC2) ~ groups, pcaDf, "mean")

valid_groups <- unique(pcaDf$groups[sapply(split(pcaDf, pcaDf$groups), function(df) {
  sum(complete.cases(df[, c("PC1", "PC2")])) >= 2
})])

# Generate ellipses
conf.rgn <- do.call(rbind, lapply(valid_groups, function(t) {
  subdf <- pcaDf[pcaDf$groups == t, c("PC1", "PC2")]
  if (nrow(subdf) < 2 || anyNA(subdf)) return(NULL)

  centre_row <- centroids[centroids$groups == t, c("PC1", "PC2")]
  if (nrow(centre_row) == 0 || anyNA(centre_row)) return(NULL)

  ell <- ellipse::ellipse(cov(subdf), centre = as.matrix(centre_row), level = 0.95)
  data.frame(groups = as.character(t), ell)
}))


# Plot PC1 and PC2
ggplot(data = pcaDf, aes(x = PC1, y = PC2, group = as.factor(groups), color = as.factor(groups))) + 
    # geom_polygon(data = conf.rgn, aes(fill = groups), alpha = 0.05) +
    geom_point(size = 1, alpha = 0.1) + 
  labs(title = "Principal Component Analysis of Scotland Tree Types: PC1 and PC2") +
  theme_classic() +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", alpha = 0.2) +
  theme(legend.position = "none") +
  ylim(-20,20) +
  xlim(-30,20)


summary(pcaOutput) # 20, 0.95232
pcaOutput$rotation %>% as.data.frame() %>% arrange(PC1)
# rh60, pai_75_80m

finalStack <- fullStack[[c("B5_p50", "ndvi", "B11_p10", "glcm_dissimilarity", "LPC_1km_v1", "glcm_variance", "glcm_mean", "B1_p50", "glcm_correlation", "B1_p10", "SLA_1km_v1", "B1_p50", "B1_p95", "glcm_entropy")]]



```

# Random forest training

```{r}
# Canopy Height
CH <- finalTable

CH <- CH[,-c(1,3:9)] %>% st_drop_geometry()
coords <- cbind(st_coordinates(finalTable$geometry)[,1], st_coordinates(finalTable$geometry)[,2])
groups <- kmeans(coords, centers = 10)$cluster
CH$cluster <- groups

# Create a spatial cross validation and then visualise
plot_df <- data.frame(
  x = coords[,1],
  y = coords[,2],
  cluster = factor(groups)
)

ggplot(plot_df, aes(x = x, y = y, color = cluster)) +
  geom_point() +
  coord_equal() +
  scale_color_brewer(palette = "Set3") +
  theme_minimal()


uniqueClusters <- unique(CH$cluster)
trainIndex <- lapply(uniqueClusters, function(x) {which(CH$cluster != x)})
testIndex <- lapply(uniqueClusters, function(x) {which(CH$cluster == x)})

ctrl <- trainControl(
  method = "cv",
  number = length(uniqueClusters),
  index = trainIndex,
  indexOut = testIndex
)

ctrl_normal <- trainControl(
  method = "cv",
  number = 10       # standard k-fold
)

set.seed(33)
model <- train(
  Z ~ .,         
  data = CH[,-236],
  method = "xgbTree",
  trControl = ctrl
)

##################################
# Different spatial approach
coords
distMat <- dist(coords)
hcSpatial <- hclust(distMat, method = "ward.D2")
CH$spatialBlock <- cutree(hcSpatial, k = 10)

featureDist <- dist(scale(CH[, -c(1,235,236)]))
hcFeature <- hclust(featureDist, method = "ward.D2")
CH$featureBlock <- cutree(hcFeature, k = 10)

targetDist <- dist(scale(CH$Z))
hcTarget <- hclust(targetDist, method = "ward.D2")
CH$targetBlock <- cutree(hcTarget, k = 10)

combinedLabels <- paste(CH$spatialBlock, CH$featureBlock, CH$targetBlock, sep = "_")

combinedDf <- data.frame(
  spatial = factor(CH$spatialBlock),
  feature = factor(CH$featureBlock),
  target  = factor(CH$targetBlock))

combinedNumeric <- fastDummies::dummy_cols(combinedDf, remove_first_dummy = TRUE)
distMat <- dist(combinedNumeric)
consensus <- ConsensusClusterPlus(as.matrix(distMat),
                                  maxK = 5,
                                  reps = 50,
                                  clusterAlg = "hc",
                                  distance = "manhattan",
                                  plot = NULL)

CH$spcvFold <- consensus$consensusClass
#################################################
spatialFolds <- spatialBlock(
  speciesData = st_as_sf(cbind(CH, finalTable$geometry)),
  theRange = 5000,
  k = 10,
  selection = "random",
  iteration = 100,
  showBlocks = TRUE
)

CH$foldID <- spatialFolds$foldID
for(f in 1:10){
  trainData <- CH[CH$foldID != f, ]
  testData  <- CH[CH$foldID == f, ]
}

folds <- unique(CH$foldID)
trainIndex <- lapply(folds, function(f) which(CH$foldID != f))
testIndex <- lapply(folds, function(f) which(CH$foldID == f))

# Setup trainControl with custom folds
ctrl <- trainControl(
  method = "cv",
  number = 10,
  index = trainIndex,
  indexOut = testIndex,
  savePredictions = "final"
)

set.seed(123)
model <- train(
  Z ~ .,   # replace with your formula
  data = CH[,-c(236,237)],
  method = "rf",
  trControl = ctrl
)
###############################################
CH$geometry <- finalTable$geometry
CH <- st_as_sf(CH)
BWCA_UTM.shp <- st_transform(BWCA.shp, 26915)
predpts <- spatSample(fortypcdBWCA, size = 2000, method = "regular", as.points = TRUE)
CH <- st_transform(CH, st_crs(predpts))
predpts_sf <- st_as_sf(predpts)

knndmFolds <- knndm(tpoints = CH,
                    predpoints = predpts_sf,
                    k = 5,
                    samplesize = 5000,
                    clustering = "kmeans")



crs(predpts)




##################
# Canopy Bulk Density
CBD <- finalTable

CBD <- CBD[,-c(1,2,3,4:9)] %>% st_drop_geometry()
coords <- cbind(st_coordinates(finalTable$geometry)[,1], st_coordinates(finalTable$geometry)[,2])
groups <- kmeans(coords, centers = 10)$cluster
CBD$cluster <- groups

CBD$geometry <- finalTable$geometry
CBD <- st_as_sf(CBD)
BWCA_UTM.shp <- st_transform(BWCA.shp, 26915)
predpts <- spatSample(fortypcdBWCA, size = 2000, method = "regular", as.points = TRUE)
CBD <- st_transform(CBD, st_crs(predpts))
predpts_sf <- st_as_sf(predpts)

knndmFolds <- knndm(tpoints = CBD,
                    predpoints = predpts_sf,
                    k = 10,
                    samplesize = 5000)
```




folds <- unique(Z$cluster)

testZ <- finalTable[,c(57,2:34,36:54,69,76:108)] %>% drop_na()

clusters <- unique(Z$cluster)
k <- 5
clusters <- sample(clusters) # Shuffle clusters
foldList <- split(clusters, cut(seq_along(clusters), breaks = k, labels = FALSE))

trainIndices <- list()
testIndices <- list()

for (i in 1:k) {
  testCluster <- foldList[[i]]
  testIDX <- which(Z$cluster %in% testCluster)
  trainIDX <- which(!(Z$cluster %in% testCluster))  # <-- FIXED !
  trainIndices[[paste0("Fold", i)]] <- trainIDX
  testIndices[[paste0("Fold", i)]] <- testIDX
}

ctrl <- trainControl(
  method = "cv",
  number = k,
  index = trainIndices,
  indexOut = testIndices,
  search = "grid"
)

grid <- expand.grid(mtry = c(5, 10, 15, 30))

model <- train(
  Z ~ ., 
  data = testZ,
  method = "rf",
  trControl = ctrl,
  importance = TRUE,
  ntree = 100
  # tuneGrid = grid
)


#######################

# 1. Build training data with response named "Z"
testZ <- finalTable[,c(57,2:34,36:54,69,76:108, which(colnames(finalTable)=="cluster"))] %>%
  drop_na()
colnames(testZ)[1] <- "Z"  # ensure the response is named Z

# 2. Create spatial folds from testZ$cluster
clusters <- unique(testZ$cluster)
k <- 5
clusters <- sample(clusters)
foldList <- split(clusters, cut(seq_along(clusters), breaks = k, labels = FALSE))

trainIndices <- list()
testIndices <- list()

for (i in 1:k) {
  testCluster <- foldList[[i]]
  testIDX <- which(testZ$cluster %in% testCluster)
  trainIDX <- which(!(testZ$cluster %in% testCluster))
  trainIndices[[paste0("Fold", i)]] <- trainIDX
  testIndices[[paste0("Fold", i)]] <- testIDX
}

# 3. Train control
ctrl <- trainControl(
  method = "cv",
  number = k,
  index = trainIndices,
  indexOut = testIndices,
  search = "grid"
)

grid <- expand.grid(mtry = c(5, 10, 15, 30))
testZ <- scale(testZ[,-c(54,88)], center = TRUE, scale = TRUE)
testZ <- testZ[, colSums(is.na(testZ) | is.nan(testZ)) == 0]

# 4. Train RF model
model <- train(
  Z ~ .,  # exclude cluster column from predictors
  data = testZ ,
  method = "rf",
  trControl = ctrl,
  importance = TRUE,
  ntree = 100,
  tuneGrid = grid
)

# 5. Confirm no NA values
colSums(is.na(testZ))


write.csv(finalTable, '/Users/louisgoodall/Desktop/Portfolio_Projects/GEDI/Data/RF Tables/finalTableFull.csv')


testZ %>% as.data.frame()
```
# I MAY NOT NEED THIS SECTION AFTER ALL
# Now to determine if stratified or random sampling is better for the models. Below
# is code to view the boxplots of stratified vs random for all 5 Y variables. When
# using continuous data for Y, createFolds automatically implements stratified sampling
# in order to preserve a homogeneous distribution among the fold of Y. This is computationally
# more expensive and if random does it just as well I will use random. IT DID!

dfs <- list(Z = Z, CBH = CBH, CBD = CBD, CC = CC, CFL = CFL)
stratSummaries <- list()
randomSummaries <- list()

for (name in names(dfs)) {
  df <- dfs[[name]]
  # set.seed(33)
  stratifiedFolds <- createFolds(df[[1]], k = 10, returnTrain = FALSE)
  randomFolds <- sample(rep(1:10, length.out = nrow(df)))
  summarizeFolds <- function(folds, df) {
    sapply(folds, function(idx) {
      c(mean = mean(df[[1]][idx]),
        median = median(df[[1]][idx]),
        sd = sd(df[[1]][idx]))
    })
  }
  stratSummary <- summarizeFolds(stratifiedFolds, df)
  randomSummary <- summarizeFolds(split(seq_along(nrow(df)), randomFolds), df)
  stratSummaries[[name]] <- stratSummary
  randomSummaries[[name]] <- randomSummary
  
  df$stratifiedFold <- NA
  for (i in seq_along(stratifiedFolds)) {
    df$stratifiedFold[stratifiedFolds[[i]]] <- i
  }
  df$randomFold <- randomFolds
  dfs[[name]] <- df
  
  p1 <- ggplot(df, aes(x = factor(stratifiedFold), y = df[[1]])) +
  geom_boxplot() +
  ggtitle(paste0(name, " - Stratified folds")) +
  xlab("Fold") + ylab("Outcome")
  
  p2 <- ggplot(df, aes(x = factor(randomFold), y = df[[1]])) +
  geom_boxplot() +
  ggtitle(paste0(name, " - Random folds")) +
  xlab("Fold") + ylab("Outcome")
  
  print(p1)
  print(p2)
}


trainIndex <- createDataPartition(Z$Z,
                                  p = 0.8,
                                  list = FALSE,
                                  times = 1)
  
train <- Z[trainIndex, ]
test <- Z[-trainIndex, ]

trainControl <- trainControl(method = "cv", number = 5)

model <- train(Z ~.,
               data = train,
               method = "rf",
               metric = "Rsquared",
               trControl = trainControl,
               ntree = 300,
               keep.forest = TRUE,
               importance = TRUE)

model

print(model)
```









