---
title: "Untitled"
output: pdf_document
date: "2026-01-26"
---


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(SPEI)
library(lubridate)
library(lme4)
library(latex2exp)
library(ncdf4)
library(climateR)
library(lubridate)
options(scipen = 999)
templateRaster <- rast("D:/Minnesota/templateRaster.tif")
nationForests.shp <- st_read("D:/Minnesota/National_Forest_Shapefiles/S_USA.FSCommonNames.shp") %>%
  filter(COMMONNAME == "Superior National Forest") %>%
  st_transform(., crs = 26915)
templateRaster <- rast("D:/Minnesota/Data/IC_TM-ID_30m_UTM15N.tif") %>% crop(., nationForests.shp) %>% mask(., nationForests.shp)
northwoods.shp <- st_read("D:/Minnesota/Shapefiles/northwoods.shp") %>%
  st_transform(., crs = 26915)
gc()
```

# Calculate SPEI

```{r}
# In this script I calculate SPEI at a yearly period (SPEI-12) using monthly data SPEI-12 was chosen because I am 
# interested in annual drought indices which are typically associated with mterological drought rather than
# agricultural drought. First off we need to download the climate data from the gridMET dataset online.

gridmetTemp <- getGridMET(AOI = nationForests.shp, varname = c("tmmx", "tmmn"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetPpt <- getGridMET(AOI = nationForests.shp, varname = "pr", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRs <- getGridMET(AOI = nationForests.shp, varname = "srad", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRh <- getGridMET(AOI = nationForests.shp, varname = c("rmin", "rmax"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetWind <- getGridMET(AOI = nationForests.shp, varname = "vs", startDate = "1979-01-01", endDate = "2025-12-31")

# Crop and mask the SNF
shapefile <- st_transform(nationForests.shp, crs = crs(gridmetTemp$daily_maximum_temperature))
temp <- lapply(gridmetTemp, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
ppt <- lapply(gridmetPpt, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
rs <- lapply(gridmetRs, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
rh <- lapply(gridmetRh, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
wind <- lapply(gridmetWind, function(x) {crop(x, shapefile) %>% mask(., shapefile)})

# Create climateDf and alter units as needed for SPEI calculation
climateDf <- cbind(terra::global(temp$daily_maximum_temperature - 273.15, "mean", na.rm = TRUE), # Convert from K to C
                   terra::global(temp$daily_minimum_temperature - 273.15, "mean", na.rm = TRUE), # Convert from K to C
                   terra::global(ppt$precipitation_amount, "mean", na.rm = TRUE),
                   terra::global(rs$daily_mean_shortwave_radiation_at_surface * 0.0864, "mean", na.rm = TRUE), # Convert from W/m2 to MJ/m2/day
                   terra::global(rh$daily_maximum_relative_humidity, "mean", na.rm = TRUE),
                   terra::global(rh$daily_minimum_relative_humidity, "mean", na.rm = TRUE),
                   terra::global(wind$daily_mean_wind_speed, "mean", na.rm = TRUE)) %>%
  `colnames<-`(c("maxTemp", "minTemp", "Ppt", "Rs", "maxRh", "minRh", "WindSpeed")) %>%
  rownames_to_column() %>%
  mutate(Date = as.Date(stringr::str_extract(rowname, "\\d{4}-\\d{2}-\\d{2}")),
         meanTemp = (maxTemp + minTemp) / 2,
         meanRh = (maxRh + minRh) / 2) %>%
  dplyr::select(Date, meanTemp, minTemp, maxTemp, Ppt, Rs, meanRh, WindSpeed)

# Summarise monthly data to be used in SPEI calculation
climateMonthlyDf <- climateDf %>%
  mutate(month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(minTemp = mean(minTemp),
            maxTemp = mean(maxTemp),
            Rs = mean(Rs),
            Rh = mean(meanRh),
            WindSpeed = mean(WindSpeed),
            Ppt = sum(Ppt)) %>%
  ungroup() %>%
  mutate(meanTemp = (minTemp + maxTemp)/2)

# Penman calculation
PET_monthly <- penman(
  Tmin = climateMonthlyDf$minTemp,
  Tmax = climateMonthlyDf$maxTemp,
  Rs = climateMonthlyDf$Rs,
  RH = climateMonthlyDf$Rh,
  U2 = climateMonthlyDf$WindSpeed,
  lat = 48,
  z = 400
)

climateMonthlyDf$PET <- PET_monthly
D_monthly <- climateMonthlyDf$Ppt - climateMonthlyDf$PET
D_ts <- ts(D_monthly, start = c(year(min(climateMonthlyDf$month)), month(min(climateMonthlyDf$month))), frequency = 12)  # monthly
SPEI_12 <- spei(D_ts, scale = 12) # 12-month SPEI
  

SPEI_12

as.data.frame(SPEI_12$fitted)



```



```{r}
gridmetTemp <- getGridMET(AOI = nationForests.shp, varname = c("tmmx", "tmmn"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetPpt <- getGridMET(AOI = nationForests.shp, varname = "pr", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRs <- getGridMET(AOI = nationForests.shp, varname = "srad", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRh <- getGridMET(AOI = nationForests.shp, varname = c("rmin", "rmax"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetWind <- getGridMET(AOI = nationForests.shp, varname = "vs", startDate = "1979-01-01", endDate = "2025-12-31")

shapefile <- st_transform(nationForests.shp, crs = crs(gridmetTemp$daily_maximum_temperature))

temp <- lapply(gridmetTemp, function(x) crop(x, shapefile) |> mask(shapefile))
ppt  <- lapply(gridmetPpt,  function(x) crop(x, shapefile) |> mask(shapefile))
rs   <- lapply(gridmetRs,   function(x) crop(x, shapefile) |> mask(shapefile))
rh   <- lapply(gridmetRh,   function(x) crop(x, shapefile) |> mask(shapefile))
wind <- lapply(gridmetWind, function(x) crop(x, shapefile) |> mask(shapefile))

climateDf <- cbind(
  terra::global(temp$daily_maximum_temperature - 273.15, "mean", na.rm = TRUE),
  terra::global(temp$daily_minimum_temperature - 273.15, "mean", na.rm = TRUE),
  terra::global(ppt$precipitation_amount, "mean", na.rm = TRUE),
  terra::global(rs$daily_mean_shortwave_radiation_at_surface * 0.0864, "mean", na.rm = TRUE),
  terra::global(rh$daily_maximum_relative_humidity, "mean", na.rm = TRUE),
  terra::global(rh$daily_minimum_relative_humidity, "mean", na.rm = TRUE),
  terra::global(wind$daily_mean_wind_speed, "mean", na.rm = TRUE)) %>%
  `colnames<-`(c("maxTemp", "minTemp", "Ppt", "Rs", "maxRh", "minRh", "WindSpeed")) |>
  rownames_to_column("rowname") %>%
  mutate(Date = as.Date(str_extract(rowname, "\\d{4}-\\d{2}-\\d{2}")),
         meanTemp = (maxTemp + minTemp) / 2,
         meanRh   = (maxRh + minRh) / 2) %>%
  select(Date, meanTemp, minTemp, maxTemp, Ppt, Rs, meanRh, WindSpeed)


climateMonthlyDf <- climateDf %>%
  mutate(month = floor_date(Date, "month")) %>%
  group_by(month) %>%
  summarise(
    minTemp   = mean(minTemp, na.rm = TRUE),
    maxTemp   = mean(maxTemp, na.rm = TRUE),
    Rs        = mean(Rs, na.rm = TRUE),
    Rh        = mean(meanRh, na.rm = TRUE),
    WindSpeed = mean(WindSpeed, na.rm = TRUE),
    Ppt       = sum(Ppt, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(meanTemp = (minTemp + maxTemp) / 2)

PET_daily <- penman(
  Tmin = climateMonthlyDf$minTemp,
  Tmax = climateMonthlyDf$maxTemp,
  Rs   = climateMonthlyDf$Rs,
  RH   = climateMonthlyDf$Rh,
  U2   = climateMonthlyDf$WindSpeed,
  lat  = 48,
  z    = 400
)

# Convert mm/day → mm/month
PET_monthly <- PET_daily * days_in_month(climateMonthlyDf$month)

climateMonthlyDf$PET <- PET_monthly

D_monthly <- climateMonthlyDf$Ppt - climateMonthlyDf$PET

D_ts <- ts(
  D_monthly,
  start = c(year(min(climateMonthlyDf$month)),
            month(min(climateMonthlyDf$month))),
  frequency = 12
)

SPEI_12 <- spei(
  D_ts,
  scale = 12,
  na.rm = TRUE
)

speiDf <- data.frame(
  month = climateMonthlyDf$month,
  SPEI_12 = as.numeric(SPEI_12$fitted)
) %>%
  mutate(Status = case_when(
    SPEI_12 >= -2, "DO"
  ))

# Variable yet not significantly changing drought conditions for the SNF/BWCA
speiDf$time_num <- as.numeric(speiDf$month)
summary(lm(SPEI_12 ~ time_num, data = speiDf))

ggplot(speiDf, aes(x = time_num, y = SPEI_12)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_classic() +
  stat_function(fun = function(x){-0.198431684 + 0.000015864*x}, color = "red", size = 1.2)
```

# Northwoods

```{r}
# Download SPEI 12 month data (1 year data)
gridmetSPEI12 <- getGridMET(AOI = northwoods.shp, varname = "spei1y", startDate = "2000-01-01", endDate = "2025-12-31")
shapefile <- st_transform(northwoods.shp, crs = crs(gridmetSPEI12$spei))

# Get raster list of SPEI values and extract dates
speiRaster <- gridmetSPEI12$spei
layerDates <- as.Date(sub("spei1y_", "", names(speiRaster)), format = "%Y-%m-%d")

# Identify last date per year because not all of the SPEI dates are YYYY-12-31. This is the best right now.
years <- format(layerDates, "%Y")
lastDates <- tapply(layerDates, years, max)
lastDates <- as.Date(lastDates, origin = "1970-01-01")
lastLayers <- which(layerDates %in% lastDates)

# Subset raster to one layer per year
speiYearlyRaster <- speiRaster[[lastLayers]]
# plot(speiYearlyRaster)

# Crop and mask to the Northwoods shapefile then plot to have a look
spei1y <- lapply(speiYearlyRaster, function(x) crop(x, shapefile) |> mask(shapefile))
lapply(spei1y, function(x) plot(x))

# Timeline of boxplots to visualise the changes in SPEI over the study period
lapply(spei1y, as.data.frame) %>%
  do.call(cbind, .) %>%
  pivot_longer(cols = everything(), names_to = "layer", values_to = "spei") %>%
  mutate(year = sub(".*(\\d{4}).*", "\\1", layer),
         year = as.factor(year)) %>%
  ggplot(aes(x = year, y = spei)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Year", y = "SPEI (12-month)", title = "Yearly SPEI Distribution") +
  geom_hline(yintercept =  0, color = "blue") +
  geom_hline(yintercept =  -1, color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Superior National Forest

```{r}
# Download SPEI 12 month data (1 year data)
gridmetSPEI12_SNF <- getGridMET(AOI = nationForests.shp, varname = "spei1y", startDate = "1980-01-01", endDate = "2025-12-31")
shapefile <- st_transform(nationForests.shp, crs = crs(gridmetSPEI12_SNF$spei))

# Get raster list of SPEI values and extract dates
speiRaster <- gridmetSPEI12_SNF$spei
layerDates <- as.Date(sub("spei1y_", "", names(speiRaster)), format = "%Y-%m-%d")

# Identify last date per year because not all of the SPEI dates are YYYY-12-31. This is the best right now.
years <- format(layerDates, "%Y")
lastDates <- tapply(layerDates, years, max)
lastDates <- as.Date(lastDates, origin = "1970-01-01")
lastLayers <- which(layerDates %in% lastDates)

# Subset raster to one layer per year
speiYearlyRaster <- speiRaster[[lastLayers]]
# plot(speiYearlyRaster)

# Crop and mask to the Northwoods shapefile then plot to have a look
spei1y <- lapply(speiYearlyRaster, function(x) crop(x, shapefile) |> mask(shapefile))
lapply(spei1y, function(x) plot(x))

# Timeline of boxplots to visualise the changes in SPEI over the study period
lapply(spei1y, as.data.frame) %>%
  do.call(cbind, .) %>%
  pivot_longer(cols = everything(), names_to = "layer", values_to = "spei") %>%
  mutate(year = sub(".*(\\d{4}).*", "\\1", layer),
         year = as.factor(year)) %>%
  ggplot(aes(x = year, y = spei)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Year", y = "SPEI (12-month)", title = "Yearly SPEI Distribution") +
  geom_hline(yintercept =  0, color = "blue") +
  geom_hline(yintercept =  -1, color = "red") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Historical interannual variation
lapply(spei1y, as.data.frame) %>%
  do.call(cbind, .) %>%
  pivot_longer(cols = everything(), names_to = "layer", values_to = "spei") %>%
  mutate(year = sub(".*(\\d{4}).*", "\\1", layer),
         year = as.factor(year)) %>%
  group_by(year) %>%
  summarise(var = var(spei),
            sd = sd(spei),
            mean = mean(spei),.groups = "drop") %>%
  summarise(sd = sd(mean),
            var = var(mean))

gc()


test <- getMACA(AOI = nationForests.shp, model = "BNU-ESM",
        varname = c("tasmax", "tasmin", "pr", "rsds", "rhsmax", "rhsmin"),
        timeRes = "month",
        scenario = "rcp85",
        startDate = "2025-01-01",
        endDate = "2099-12-31")

shapefile <- st_transform(nationForests.shp, crs = crs(test$relative_humidity))



lapply(test$relative_humidity , plot)



"uas", "vas"

?getMACA
```




gridmetTemp <- getGridMET(AOI = nationForests.shp, varname = c("tmmx", "tmmn"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetPpt <- getGridMET(AOI = nationForests.shp, varname = "pr", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRs <- getGridMET(AOI = nationForests.shp, varname = "srad", startDate = "1979-01-01", endDate = "2025-12-31")
gridmetRh <- getGridMET(AOI = nationForests.shp, varname = c("rmin", "rmax"), startDate = "1979-01-01", endDate = "2025-12-31")
gridmetWind <- getGridMET(AOI = nationForests.shp, varname = "vs", startDate = "1979-01-01", endDate = "2025-12-31")

# Crop and mask the SNF
shapefile <- st_transform(nationForests.shp, crs = crs(gridmetTemp$daily_maximum_temperature))
temp <- lapply(gridmetTemp, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
ppt <- lapply(gridmetPpt, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
rs <- lapply(gridmetRs, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
rh <- lapply(gridmetRh, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
wind <- lapply(gridmetWind, function(x) {crop(x, shapefile) %>% mask(., shapefile)})
```




