---
title: "Untitled"
output: pdf_document
date: "2025-12-27"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(readxl)
library(data.table)
templateRaster <- rast("D:/Minnesota/templateRaster.tif")
options(scipen = 999)
gc()
```

# Mosaic MN together

```{r}
MN.shp <- st_read("C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/MN_Shapefile/mn_county_boundaries.shp")
directory <- "D:/Minnesota/TreeMap"
files <- list.files(directory, full.names = TRUE)
fortypcdList <- list()
for (file in files) {
  raster <- rast(file)
  name <- basename(file)
  fortypcdList[[name]] <- raster
}

rasterSPRC <- sprc(fortypcdList)
fortypcdMN <- mosaic(rasterSPRC)


shapefile <- st_transform(MN.shp, crs = crs(fortypcdMN))
fortypcdMN <- crop(fortypcdMN, shapefile) %>% mask(., shapefile)
fortypcdMN <- ifel(fortypcdMN < 0, 0, fortypcdMN)
fortypcdMN <- project(fortypcdMN, templateRaster, method = "near")

plot(fortypcdMN)


writeRaster(fortypcdMN,
            filename = "D:/Minnesota/Data/IC_30m_UTM15N.tif",
            overwrite = TRUE,
            datatype = "INT4S",
            NAflag = 0)


fortypcdDf <- read_csv("D:/Minnesota/FORTYPCDs.csv")[,-1] %>% `colnames<-`(c("FORTYPCD", "Forest_Type")) %>%
  mutate(FORTYPCD = str_trim(FORTYPCD, side = "both"))
fortypcdDf$FORTYPCD <- as.integer(fortypcdDf$FORTYPCD)

# Plot with labels and not just the numbered FORTYPCDs
r <- fortypcdMN
r <- as.int(r)
r <- as.factor(r)
levels(r) <- fortypcdDf
plot(r)




```

# Create MN TreeMap

```{r}
# # Read in the CONUS TreeMap and crop to MN
# r <- rast("D:/Minnesota/TreeMap/Data/TreeMap2022_CONUS.tif")
# shapefile <- st_transform(MN.shp, crs = crs(r))
# r <- crop(r, shapefile) %>% mask(., shapefile)
# r[is.na(r)] <- 0
# # terra::activeCat(r) <- 1
# r <- project(r, templateRaster, method = "near")
# plot(r)
# 
# writeRaster(r,
#             filename = "D:/Minnesota/Data/IC_TM-ID_30m_UTM15N.tif",
#             overwrite = TRUE,
#             datatype = "INT4S",
#             NAflag = 0)
```


```{r}
treeMap <- rast("D:/Minnesota/Data/IC_TM-ID_30m_UTM15N.tif")
terra::activeCat(treeMap) <- 1
treeMap_vals <- unique(values(treeMap))

plotData <- data.table::fread("D:/Minnesota/TreeMap/TreeMap2022_CONUS_Tree_Table.csv") %>%
  filter(TM_ID %in% treeMap_vals)

plotCounts <- as.data.frame(table(values(treeMap))) %>%
  rename(TM_ID = Var1, Freq = Freq)

speciesREF <- read_excel("D:/Minnesota/TreeMap/REF_SPECIES.xlsx")

tlTreesBA <- plotData %>%
  group_by(TM_ID, SPCD) %>%
  summarise(plotBA = sum((DIA / 2)^2, na.rm = TRUE), .groups = "drop") %>%
  mutate(TM_ID = as.factor(TM_ID)) %>%
  left_join(plotCounts, by = "TM_ID") %>%
  mutate(aoiBA = plotBA * Freq) %>%
  group_by(SPCD) %>%
  summarise(sppBATotal = sum(aoiBA) / 10000) %>%
  left_join(speciesREF %>% select(SPCD, SPECIES_SYMBOL), by = "SPCD") %>%
  mutate(sppBA_Pct = sppBATotal / sum(sppBATotal))

mnSpp <- tlTreesBA %>%
  filter(sppBA_Pct > 0.005)
```






```{r}
#----------------------------------------------------------
# MN TreeMap: Corrected Biomass and Cohort Raster Pipeline
#----------------------------------------------------------
gc()

#--------------------------
# Load template raster
#--------------------------
templateRaster <- rast("D:/Minnesota/templateRaster.tif")

#--------------------------
# Load MN shapefile
#--------------------------
MN.shp <- st_read("C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/MN_Shapefile/mn_county_boundaries.shp")

#--------------------------
# Load TreeMap raster for MN
#--------------------------
treeMap <- rast("D:/Minnesota/Data/IC_TM-ID_30m_UTM15N.tif")
terra::activeCat(treeMap) <- 1

# Crop & project to MN
MN.shp_proj <- st_transform(MN.shp, crs = crs(treeMap))
treeMap <- crop(treeMap, MN.shp_proj) %>% mask(., MN.shp_proj)
treeMap <- project(treeMap, templateRaster, method = "near")

# Unique TreeMap IDs in MN
treeMap_vals <- unique(values(treeMap)) %>% na.omit()

#--------------------------
# Load TreeMap tree table
#--------------------------
plotData <- fread("D:/Minnesota/TreeMap/TreeMap2022_CONUS_Tree_Table.csv") %>%
  filter(TM_ID %in% treeMap_vals)

# Get plot frequency for TM_IDs (for weighting)
plotCounts <- table(values(treeMap)) %>% as.data.frame() %>%
  rename(TM_ID = Var1, Freq = Freq)

#--------------------------
# Load species reference table
#--------------------------
speciesREF <- read_excel("D:/Minnesota/TreeMap/REF_SPECIES.xlsx")

#--------------------------
# Select "important" species (>0.5% BA)
#--------------------------
tlTreesBA <- plotData %>%
  group_by(TM_ID, SPCD) %>%
  summarise(plotBA = sum(I((DIA/2)^2), na.rm = TRUE), .groups = "drop") %>%
  left_join(plotCounts %>%
              mutate(TM_ID = as.integer(as.character(TM_ID))), by = "TM_ID") %>%
  mutate(aoiBA = plotBA * Freq) %>%                     # Weight by plot frequency
  group_by(SPCD) %>%
  summarise(sppBATotal = sum(aoiBA)/10000) %>%         # divide by 10,000 to scale
  left_join(speciesREF %>% select(SPCD, SPECIES_SYMBOL), by = "SPCD") %>%
  mutate(sppBA_Pct = sppBATotal / sum(sppBATotal))

mnSpp <- tlTreesBA %>% filter(sppBA_Pct > 0.005)

#--------------------------
# Load TREE / COND / SITETREE tables for MN, WI, MI
#--------------------------
directory <- "D:/Minnesota/TreeMap/States/"

# TREE
treeFiles <- list.files(directory, pattern = "*TREE.csv", full.names = TRUE)
treeList <- lapply(treeFiles, fread)
trees <- bind_rows(treeList)
rm(treeList)
trees <- trees %>% filter(PLT_CN %in% plotData$PLT_CN)

# COND
condFiles <- list.files(directory, pattern = "*COND.csv", full.names = TRUE)
condList <- lapply(condFiles, fread)
cond <- bind_rows(condList)
rm(condList)
cond <- cond %>% filter(PLT_CN %in% plotData$PLT_CN)

# SITETREE
sitetreeFiles <- list.files(directory, pattern = "*SITETREE.csv", full.names = TRUE)
sitetreeList <- lapply(sitetreeFiles, fread)
sitetree <- bind_rows(sitetreeList)
rm(sitetreeList)
sitetree <- sitetree %>% filter(PLT_CN %in% plotData$PLT_CN)

gc()

#--------------------------
# Fit Age Regression per species
#--------------------------
treeRegressions <- sitetree %>%
  filter(!is.na(DIA) & !is.na(AGEDIA) & !is.na(SPCD)) %>%
  filter(SPCD %in% trees$SPCD) %>%
  group_by(SPCD) %>%
  do(model = lm(AGEDIA ~ log(DIA) + 0, data = .)) %>%
  filter(SPCD %in% mnSpp$SPCD)

# Predict Age for each tree
trees <- trees %>%
  inner_join(treeRegressions, by = "SPCD") %>%
  mutate(Age = map2_dbl(model, DIA, ~predict(.x, newdata = tibble(DIA = .y)))) %>%
  inner_join(mnSpp[,c(1,3)], by = "SPCD") %>%
  mutate(Age = ifelse(Age < 1, 1, Age))

#--------------------------
# Cohort Binning
#--------------------------
breaks <- seq(0, 140, 10)   # 10-year bins
trees <- trees %>%
  mutate(bin = cut(Age, breaks = breaks, labels = breaks[-1], right = TRUE),
         bin = as.integer(as.character(bin)))

#--------------------------
# Calculate Cohort Biomass per plot/species/bin
#--------------------------
siteBiomass <- trees %>%
  mutate(biomassArea = DRYBIO_AG * TPA_UNADJ) %>%         # lb/ac per tree
  group_by(PLT_CN, SPCD, bin) %>%
  summarise(biomass = sum(biomassArea, na.rm = TRUE)) %>%
  mutate(biomass = biomass * 0.1121)                     # convert lb/ac -> g/m²

#--------------------------
# Weight by TM_ID frequency
#--------------------------
siteBiomass <- siteBiomass %>%
  left_join(plotData %>% mutate(TM_ID = as.integer(as.character(TM_ID))) %>% dplyr::select(PLT_CN, TM_ID), by = "PLT_CN") %>%
  left_join(plotCounts %>% mutate(TM_ID = as.integer(as.character(TM_ID))), by = "TM_ID")

#--------------------------
# Aggregate total biomass per TM_ID and calculate CWD / Roots
#--------------------------
siteTotalBiomass2 <- siteBiomass %>%
  group_by(TM_ID) %>%
  summarise(totalBiomass_MgHa = sum(biomass, na.rm = TRUE) * 0.01,  # g/m² -> Mg/ha
            CWD_MgHA = totalBiomass_MgHa * 0.19,
            coarseRoot_MgHa = totalBiomass_MgHa * 0.3,
            fineRoot_MgHa = totalBiomass_MgHa * 0.1)

#--------------------------
# Map biomass to raster
#--------------------------
mapCodeMatrix <- siteTotalBiomass2 %>% dplyr::select(TM_ID) %>% mutate(TM_ID = TM_ID, MapCode = TM_ID) %>% as.matrix()
cwdMatrix <- siteTotalBiomass2 %>% dplyr::select(TM_ID, CWD_MgHA) %>% as.matrix()
coarseRootsMatrix <- siteTotalBiomass2 %>% dplyr::select(TM_ID, coarseRoot_MgHa) %>% as.matrix()
fineRootsMatrix <- siteTotalBiomass2 %>% dplyr::select(TM_ID, fineRoot_MgHa) %>% as.matrix()

finalTreeMap <- terra::subst(treeMap, from = mapCodeMatrix[,1], to = mapCodeMatrix[,2])
finalTreeMap_Num <- as.numeric(finalTreeMap)

cwdRast <- terra::subst(finalTreeMap_Num, from = cwdMatrix[,1], to = cwdMatrix[,2])
coarseRootRast <- terra::subst(finalTreeMap_Num, from = coarseRootsMatrix[,1], to = coarseRootsMatrix[,2])
fineRootRast <- terra::subst(finalTreeMap_Num, from = fineRootsMatrix[,1], to = fineRootsMatrix[,2])

#--------------------------
# Plot & check values
#--------------------------
plot(finalTreeMap, main = "MN TreeMap MapCode")
plot(cwdRast, main = "CWD Mg/ha")
plot(coarseRootRast, main = "Coarse Roots Mg/ha")
plot(fineRootRast, main = "Fine Roots Mg/ha")

# Check for realistic ranges
x <- values(cwdRast) %>% as.data.frame() %>% drop_na()
summary(x)
hist(x[[1]])



```





# Now for the real shit

```{r}
treeMap <- rast("D:/Minnesota/Data/IC_TM-ID_30m_UTM15N.tif")
terra::activeCat(treeMap) <- 1

plotCounts <- table(values(treeMap)) %>% as.data.frame() %>% rename("TM_ID" = "Var1")

plotData <- data.table::fread("D:/Minnesota/TreeMap/TreeMap2022_CONUS_Tree_Table.csv")

plotData <- plotData %>% filter(TM_ID %in% values(treeMap))

speciesREF <- readxl::read_excel("D:/Minnesota/TreeMap/REF_SPECIES.xlsx")

tlTreesBA <- plotData %>%
  group_by(TM_ID, SPCD) %>%
  summarise(plotBA = sum(I((DIA/2)^2), na.rm = TRUE), .groups = "drop") %>%
  mutate(TM_ID = as.factor(TM_ID)) %>%
  left_join(plotCounts, by = "TM_ID") %>%
  mutate(aoiBA = plotBA * Freq) %>%
  group_by(SPCD) %>%
  summarise(sppBATotal = sum(aoiBA) / 10000) %>%
  arrange(sppBATotal) %>%
  left_join(dplyr::select(speciesREF, c("SPCD", "SPECIES_SYMBOL", "GENUS", "SPECIES"))) %>%
  mutate(sppBA_Pct = sppBATotal / sum(sppBATotal))

# This is the version that would likely be used going forward because using species with an exceedingly low
# BA will mean we are simulating species that are "less" ecologically important. Also, 25 vs. 98 species is
# quite a big difference in regards to computational power. Also, with these 25 species we still have 97.15%
# of Minnesota's BA. This way we also eliminate random extras that shouldn't be there like Ponderosa pine
mnSpp <- tlTreesBA %>%
  arrange(desc(sppBA_Pct * 100)) %>%
  mutate(cumulativePct = cumsum(sppBA_Pct)) %>%
  filter(sppBA_Pct > 0.005)
landscapeSpp <- mnSpp %>% select(SPECIES_SYMBOL) %>% arrange(SPECIES_SYMBOL)

gc()

# Now to create a for loop that binds the TREE tables of MN, MI, and WI
directory <- "D:/Minnesota/TreeMap/States/"
files <- list.files(path = directory, pattern = "*TREE.csv", full.names = TRUE)
treeList <- lapply(files, data.table::fread)
trees <- do.call(bind_rows, treeList)
rm(treeList)
trees <- trees %>% filter(PLT_CN %in% plotData$PLT_CN)

# Now for COND and SITETREE tables
files <- list.files(path = directory, pattern = "*COND.csv", full.names = TRUE)
condList <- lapply(files, data.table::fread)
cond <- do.call(bind_rows, condList)
rm(condList)
cond <- cond %>% filter(PLT_CN %in% plotData$PLT_CN)

files <- list.files(path = directory, pattern = "*SITETREE.csv", full.names = TRUE)
sitetreeList <- lapply(files, data.table::fread)
sitetree <- do.call(bind_rows, sitetreeList)
rm(sitetreeList)
sitetree <- sitetree %>% filter(PLT_CN %in% plotData$PLT_CN)

gc()

#----AGE CALCULATIONS----#    # TODO, find equation for SPCD == 313 (Acer negundo)
# Fit a linear regression
treeRegressions <- sitetree %>%
  filter(!is.na(DIA) & !is.na(AGEDIA) & !is.na(SPCD)) %>%
  filter(SPCD %in% trees$SPCD) %>%
  group_by(SPCD) %>%
  do(model = lm(AGEDIA ~ log(DIA) + 0, data = .)) %>%
  filter(SPCD %in% mnSpp$SPCD)

sort(unique(treeRegressions$SPCD))
sort(unique(mnSpp$SPCD))

#----BIOMASS----#
trees <- trees %>%
  inner_join(treeRegressions, by = "SPCD") %>%
  mutate(Age = map2_dbl(model, DIA, ~predict(.x, newdata = tibble(DIA = .y)))) %>%
  inner_join(mnSpp[,c(1,3)], by = "SPCD")

ggplot(trees, aes(x = SPECIES_SYMBOL, y = Age, fill = SPECIES_SYMBOL)) +
  geom_boxplot() +
  theme_classic()

gc()

# Calculate site total biomass
breaks <- seq(0, 140, 10)
siteBiomass <- trees %>%
  mutate(biomassArea = DRYBIO_AG * TPA_UNADJ) %>%
  mutate(Age = ifelse(Age < 1, 1, Age)) %>%
  mutate(bin = cut(Age, breaks = breaks, labels = breaks[-1], right = TRUE),
         bin = as.integer(as.character(bin))) %>%
  group_by(PLT_CN, SPCD, bin) %>%
  summarise(biomass = sum(biomassArea, na.rm = TRUE)) %>%
  mutate(biomass = round(biomass, digits = 0),
         biomass = biomass * 0.1121) # convert from lb/ac to g/m2
names(siteBiomass) <- c("PLT_CN", "SPCD", "CohortAge", "CohortBiomass")


rm(trees)

siteTotalBiomass <- siteBiomass %>%
  group_by(PLT_CN) %>%
  summarise(totalBiomass = sum(CohortBiomass, na.rm = TRUE)) %>%
  mutate(totalBiomass_MgHa = totalBiomass * 0.01) %>%
  mutate(CWD_MgHA = totalBiomass_MgHa * 0.19,
         coarseRoot_MgHa = totalBiomass_MgHa * 0.3,
         fineRoot_MgHa = totalBiomass_MgHa * 0.1)

siteTotalBiomass2 <- siteTotalBiomass %>%
  left_join(plotData %>% select(PLT_CN, TM_ID), by = "PLT_CN") %>%
  mutate(MapCode = TM_ID)

siteTotalBiomass_TM <- siteTotalBiomass2 %>%
  group_by(MapCode) %>%
  summarise(
    CWD_MgHa        = mean(CWD_MgHA, na.rm = TRUE),
    coarseRoot_MgHa = mean(coarseRoot_MgHa, na.rm = TRUE),
    fineRoot_MgHa   = mean(fineRoot_MgHa, na.rm = TRUE),
    .groups = "drop"
  )

# MapCodeDf <- siteTotalBiomass2 %>%
#   unnest(MapCode) %>%
#   mutate(ID = 1:length(unique(MapCode))) %>%
#   left_join(siteBiomass, by = "PLT_CN") %>%
#   select(PLT_CN, ID, SPCD, CohortAge, CohortBiomass) %>%
#   `colnames<-`(c("PLT_CN", "MapCode", "SPCD", "CohortAge", "CohortBiomass"))
# MapCodeDf$PLT_CN <- as.numeric(MapCodeDf$PLT_CN)


MapCodeDf <- siteBiomass %>%
  left_join(siteTotalBiomass2 %>% select(PLT_CN, MapCode), by = "PLT_CN") %>%
  select(PLT_CN, MapCode, SPCD, CohortAge, CohortBiomass) %>%
  mutate(TM_ID = MapCode)
MapCodeDf$PLT_CN <- as.numeric(MapCodeDf$PLT_CN)


# Read in plot tables for all 50 states
files <- list.files(path = directory, pattern = "*PLOT.csv", full.names = TRUE)
plotDf <- do.call(rbind, lapply(files, data.table::fread))

mergedMapCodeDf <- plotDf %>%
  mutate(CN = as.numeric(as.character(CN))) %>%
  left_join(MapCodeDf, by = c("CN" = "PLT_CN")) %>%
  filter(!is.na(MapCode))

valuesTreeMap <- values(treeMap) %>% as.data.frame() %>% drop_na() %>% unique() %>% arrange(TM_ID)

# Using MN/WI/MI data we can cover 95.66% of the plots in MN
threeStatesMapCode <- mergedMapCodeDf %>% filter(MapCode %in% valuesTreeMap$TM_ID) %>% select(MapCode) %>% unique() %>% arrange(MapCode)
# (nrow(threeStatesMapCode) / nrow(valuesTreeMap)) * 100


test <- ifel(treeMap %in% threeStatesMapCode$MapCode, 1, 2)
plot(test, col = c("green", "black"))


medianBiomassValues <- mergedMapCodeDf %>%
  select(CN, MapCode, SPCD, CohortAge, CohortBiomass) %>%
  group_by(SPCD, CohortAge) %>%
  summarise(medianBiomass = median(CohortBiomass, na.rm = TRUE))

# mergedMapCodeDf <- mergedMapCodeDf %>%
#   mutate(TM_ID = MapCode) %>%
#   select(CN, TM_ID, MapCode, SPCD, CohortAge, CohortBiomass) %>%
#   arrange(MapCode) %>%
#   mutate(MapCode = cumsum(MapCode != lag(MapCode, default = first(MapCode) -1)))
# 
# mergedMapCodeDf <- mergedMapCodeDf %>%
#   left_join(medianBiomassValues, by = c("SPCD", "CohortAge")) %>%
#   mutate(CohortBiomass = coalesce(CohortBiomass, medianBiomass)) %>%
#   dplyr::select(-medianBiomass) %>%
#   drop_na()

siteTotalBiomass2 <- siteTotalBiomass2 %>%
  arrange(TM_ID) %>%
  mutate(MapCode = cumsum(MapCode != lag(MapCode, default = first(MapCode) -1)))


mapCodeMatrix <- mergedMapCodeDf[,c(2,2,3)] %>% unique() %>% as.matrix()
# cwdMatrix <- siteTotalBiomass2[,c(7,7,4)] %>% unique() %>% as.matrix()
# coarseRootsMatrix <- siteTotalBiomass2[,c(7,7,5)] %>% unique() %>% as.matrix()
# fineRootsMatrix <- siteTotalBiomass2[,c(7,7,6)] %>% unique() %>% as.matrix()



finalTreeMap <- terra::subst(treeMap, from = mapCodeMatrix[,1], to = mapCodeMatrix[,3])

plot(finalTreeMap)


# Currently finalTreeMap is a categorical raster and needs to be numeric to change the values in it
# Here I create a cimple numeric version
finalTreeMap_Num <- as.numeric(finalTreeMap)

gc()

# Build classification matrices: [from , to]
cwd_mat <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "CWD_MgHa")])
cr_mat  <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "coarseRoot_MgHa")])
fr_mat  <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "fineRoot_MgHa")])

# Classify
cwdRast <- terra::classify(finalTreeMap_Num, cwd_mat, others = NA)
coarseRootRast <- terra::classify(finalTreeMap_Num, cr_mat, others = NA)
fineRootRast <- terra::classify(finalTreeMap_Num, fr_mat, others = NA)

# Plot
plot(finalTreeMap)
plot(cwdRast)
plot(coarseRootRast)
plot(fineRootRast)


cwd_mat %>% as.data.frame() %>% arrange(desc(CWD_MgHa))


gc()


writeRaster(cwdRast,
            filename = "D:/Minnesota/Data/CWD_30m_UTM15N.tif",
            datatype = "FLT4S",
            NAflag = 0,
            overwrite = TRUE)

writeRaster(coarseRootRast,
            filename = "D:/Minnesota/Data/CoarseRoots_30m_UTM15N.tif",
            datatype = "FLT4S",
            NAflag = 0,
            overwrite = TRUE)

writeRaster(fineRootRast,
            filename = "D:/Minnesota/Data/FineRoots_30m_UTM15N.tif",
            datatype = "FLT4S",
            NAflag = 0,
            overwrite = TRUE)


plot(rast("D:/Minnesota/Data/CWD_30m_UTM15N.tif"))
```


# cwdRast <- terra::subst(
#   finalTreeMap_Num,
#   from = cwdMatrix[,1],
#   to = cwdMatrix[,3]
# )

cwdRast <- terra::subst(finalTreeMap_Num,
                        from = siteTotalBiomass_TM$MapCode,
                        to   = siteTotalBiomass_TM$CWD_MgHa)

plot(cwdRast)

# coarseRootRast <- terra::subst(
#   finalTreeMap_Num,
#   from = coarseRootsMatrix[,1],
#   to = coarseRootsMatrix[,3]
# )

coarseRootRast <- terra::subst(finalTreeMap_Num,
                               from = siteTotalBiomass_TM$MapCode,
                               to   = siteTotalBiomass_TM$coarseRoot_MgHa)

plot(coarseRootRast)

# fineRootRast <- terra::subst(
#   finalTreeMap_Num,
#   from = fineRootsMatrix[,1],
#   to = fineRootsMatrix[,3]
# )

fineRootRast <- terra::subst(finalTreeMap_Num,
                             from = siteTotalBiomass_TM$MapCode,
                             to   = siteTotalBiomass_TM$fineRoot_MgHa)

plot(fineRootRast)

gc()


##########################################################################################

# Build classification matrices: [from , to]
cwd_mat <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "CWD_MgHa")])
cr_mat  <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "coarseRoot_MgHa")])
fr_mat  <- as.matrix(siteTotalBiomass_TM[, c("MapCode", "fineRoot_MgHa")])

# Classify
cwdRast <- terra::classify(finalTreeMap_Num, cwd_mat, others = NA)
coarseRootRast <- terra::classify(finalTreeMap_Num, cr_mat, others = NA)
fineRootRast <- terra::classify(finalTreeMap_Num, fr_mat, others = NA)

# Plot
plot(cwdRast)
plot(coarseRootRast)
plot(fineRootRast)








```



















