---
title: "Harvest Reduction Table"
output: pdf_document
date: "2024-05-07"
---


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
```



```{r}
# Read in data we will need
mgmtRast <- rast("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/clippedPiedmontOwnership.tif")
mgmtRastOG <- rast("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/clippedPiedmontOwnership.tif")
ecoregions <- rast("C:/Users/lagoodal/Desktop/All Raster Layers/Clipped Piedmont/ecoregions.tif")
ICMap <- rast("C:/Users/lagoodal/Desktop/All Raster Layers/Clipped Piedmont/MapCode_IC.tif")
mapCodeDf <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Final_table.csv")

# Reclassify some ecoregion values
ecoregions <- ifel(ecoregions == 0, NA,
                   ifel(ecoregions == 1, 1, ecoregions))

# Mask out NA ecoregions on management and ICMap raster
mgmtRast <- mask(mgmtRast, ecoregions)
ICMap <- mask(ICMap, ecoregions)

# Cells per management area
mgmtRast %>%
  as.data.frame() %>%
  `colnames<-`("Class") %>%
  group_by(Class) %>%
  summarise(n = n())

# Create filtered management area map which will then be used to figure out what
# Map Codes are in which management area
mgmt1 <- ifel(mgmtRast == 1, 1, NA)
mgmt2 <- ifel(mgmtRast == 2, 2, NA)
mgmt3 <- ifel(mgmtRast == 3, 3, NA)
IC1 <- mask(ICMap, mgmt1)
IC2 <- mask(ICMap, mgmt2)
IC3 <- mask(ICMap, mgmt3)

# Get Map Codes by management area
IC1MC <- values(IC1) %>% as.data.frame() %>% drop_na() %>% unique()
IC2MC <- values(IC2) %>% as.data.frame() %>% drop_na() %>% unique()
IC3MC <- values(IC3) %>% as.data.frame() %>% drop_na() %>% unique()
IC1Df <- mapCodeDf %>% filter(MapCode %in% IC1MC$MapCode_IC)
IC2Df <- mapCodeDf %>% filter(MapCode %in% IC2MC$MapCode_IC)
IC3Df <- mapCodeDf %>% filter(MapCode %in% IC3MC$MapCode_IC)

# Create vectors that contain the species for each FORTYP classification
oakHickory <- c("QUAL","QUCO2","QUMO4","QUPH","QURU","QUST","QUVE","CATO6","CAGL8","LIST","LITU","ACRU")
oakPine <- c("QUAL","QUCO2","QUMO4","QUPH","QURU","QUST","QUVE","PITA","PIEC","PIVI2","PIPA","JUVI")
softwoods <- c("PIEC", "PIPA", "PIVI2", "PITA", "JUVI")


# Now to determine which cells fall into which forest type based upon their species and biomass values
IC1Df <- IC1Df %>%
  group_by(MapCode, SpeciesName) %>%
  summarise(biomass = sum(CohortBiomass)) %>%
  mutate(totalBiomass = sum(biomass),
         propBiomass = biomass / totalBiomass) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  mutate(FORTYP = case_when(
    sum(propBiomass[SpeciesName == "PITA"]) > 0.9 ~ "LOBLOLLY",
    sum(propBiomass[SpeciesName %in% oakHickory]) > 0.6 ~ "OAK-HICKORY",
    sum(propBiomass[SpeciesName %in% oakPine]) > 0.6 ~ "OAK-PINE",
    sum(propBiomass[SpeciesName %in% softwoods]) >= 0.4 ~ "SOFTWOODS",
    TRUE ~ NA_character_
  )) %>%
  ungroup()


IC2Df <- IC2Df %>%
  group_by(MapCode, SpeciesName) %>%
  summarise(biomass = sum(CohortBiomass)) %>%
  mutate(totalBiomass = sum(biomass),
         propBiomass = biomass / totalBiomass) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  mutate(FORTYP = case_when(
    sum(propBiomass[SpeciesName == "PITA"]) > 0.9 ~ "LOBLOLLY",
    sum(propBiomass[SpeciesName %in% oakHickory]) > 0.6 ~ "OAK-HICKORY",
    sum(propBiomass[SpeciesName %in% oakPine]) > 0.6 ~ "OAK-PINE",
    sum(propBiomass[SpeciesName %in% softwoods]) >= 0.4 ~ "SOFTWOODS",
    TRUE ~ NA_character_
  )) %>%
  ungroup()


IC3Df <- IC3Df %>%
  group_by(MapCode, SpeciesName) %>%
  summarise(biomass = sum(CohortBiomass)) %>%
  mutate(totalBiomass = sum(biomass),
         propBiomass = biomass / totalBiomass) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  mutate(FORTYP = case_when(
    sum(propBiomass[SpeciesName == "PITA"]) > 0.9 ~ "LOBLOLLY",
    sum(propBiomass[SpeciesName %in% oakHickory]) > 0.6 ~ "OAK-HICKORY",
    sum(propBiomass[SpeciesName %in% oakPine]) > 0.6 ~ "OAK-PINE",
    sum(propBiomass[SpeciesName %in% softwoods]) >= 0.4 ~ "SOFTWOODS",
    TRUE ~ NA_character_
  )) %>%
  ungroup()

# Proportions of each FORTYP in each management zone
IC1Df %>% group_by(FORTYP) %>% summarise(n = n()) %>% mutate(total = sum(n), prop = n / total)
IC2Df %>% group_by(FORTYP) %>% summarise(n = n()) %>% mutate(total = sum(n), prop = n / total)
IC3Df %>% group_by(FORTYP) %>% summarise(n = n()) %>% mutate(total = sum(n), prop = n / total)


IC1MapCodes <- IC1Df %>% select(MapCode, FORTYP) %>% unique()
IC2MapCodes <- IC2Df %>% select(MapCode, FORTYP) %>% unique()
IC3MapCodes <- IC3Df %>% select(MapCode, FORTYP) %>% unique()


# NEED TO IFEL/RECLASSIFY THE MAPCODE VALUES TO FORTYP VALUES
```



# Calculate how many active and inactive cells are in each management area
# First of all, how many NAs fall outside of the AOI
clippedHUC.shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedHUC.shp")
rastHUC <- rasterize(clippedHUC.shp, mgmtRast)
# Cell counts
totalCells <- 1011 * 1442
outsideNAs <- 493699 # Calculated by counting all cells outside of the landscape
totalMgmt1 <- values(mgmtRastOG) %>% as.data.frame() %>% drop_na() %>% filter(forest_own1 == 1) %>% nrow()
totalMgmt2 <- values(mgmtRastOG) %>% as.data.frame() %>% drop_na() %>% filter(forest_own1 == 2) %>% nrow()
totalMgmt3 <- values(mgmtRastOG) %>% as.data.frame() %>% drop_na() %>% filter(forest_own1 == 3) %>% nrow()

mgmt1Active <- values(mgmt1) %>% as.data.frame() %>% drop_na() %>% nrow()
mgmt2Active <- values(mgmt2) %>% as.data.frame() %>% drop_na() %>% nrow()
mgmt3Active <- values(mgmt3) %>% as.data.frame() %>% drop_na() %>% nrow()

# 22087 are NAs that fell within the clippedHUC.shp and still need to be counted
# or the totals will be off
mgmt1Inactive <- (totalCells - outsideNAs - 22087 - totalMgmt2 - totalMgmt3 - mgmt1Active)
mgmt2Inactive <- (totalCells - outsideNAs - 22087 - totalMgmt1 - totalMgmt3 - mgmt2Active)
mgmt3Inactive <- (totalCells - outsideNAs - 22087 - totalMgmt1 - totalMgmt2 - mgmt3Active)



plot(clippedHUC.shp)
# NumclippedHUC.Shp# Number of time steps per rotation
# FORTYP    Rotation    Timesteps/Rotation
# Loblolly  35          3
# Oak-H     40          4
# Oak-P     40          4
# Soft      40          4


plot(mgmtRast)
plot(clippedHUC.shp, add = TRUE, col = NA)

```




FORTYP    N     total prop
LOBLOLLY	3842	14899	0.25786966	
OAK-HICKORY	5693	14899	0.38210618	
OAK-PINE	3275	14899	0.21981341	
SOFTWOODS	595	14899	0.03993557	
NA	1494	14899	0.10027519






