---
title: "Untitled"
output: pdf_document
date: "2023-10-19"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(tidyterra)
library(terra)
library(sf)
library(rgdal)
library(RColorBrewer)
library(spatstat)
library(gstat)
```


```{r}
set.seed(33)

# Read in template raster, clippedPiedmont.shp and forest ownership raster, crop and reproject
templateRaster <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/treeMap/Clipped Piedmont/ecoregions.tif")
clippedPiedmont.shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedHUC.shp")
forestOwnership <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Management Areas/Data/forest_own1/forest_own1.tif")
clippedPiedmont.shp <- st_transform(clippedPiedmont.shp, crs = crs(forestOwnership))
forestOwnership <- crop(forestOwnership, clippedPiedmont.shp) %>% mask(., clippedPiedmont.shp)
piedmontOwnership <- terra::project(forestOwnership, templateRaster, method = "near")

# Create a lookup to table reclassify the raster and then reclassify it
replacements <- rbind(c(3,2), c(4,1), c(5,3), c(6,3), c(7,3))
piedmontOwnership <- terra::classify(piedmontOwnership, replacements)

# New Ownership values
# 1 = Private Family
# 2 = Private Corporate
# 3 = Public

# Use foical to fill in the gaps
piedmontOwnership <- focal(piedmontOwnership, w=9, fun = modal, na.policy = "only", na.rm = TRUE)

# writeRaster(piedmontOwnership,
#             filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/treeMap/Harvest/managementAreas.tif",
#             datatype = "INT1U",
#             NAflag = 0,
#             overwrite = TRUE)
```



```{r}
# Read in the HUC12 watershed data to serve as initial stand boundaries
Random <- brewer.pal(13, "Set3")
clippedPiedmont.shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedHUC.shp")
HUC12 <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/HUC 8 Watersheds/Shape/WBDHU12.shp") %>%
  st_transform(crs = crs(piedmontOwnership))
huc12Rast <- rasterize(HUC12, piedmontOwnership, field = "ObjectID")
huc12Rast <- crop(huc12Rast, clippedPiedmont.shp) %>% mask(., clippedPiedmont.shp)

# Create a dataframe that merges the HUC12 stands and the Management Areas
huc12Df <- as.data.frame(huc12Rast, xy = TRUE)
ownershipDf <- as.data.frame(piedmontOwnership, xy = TRUE)
huc12Stands <- inner_join(huc12Df, ownershipDf, by = c("x", "y"))
huc12Stands <- huc12Stands %>% mutate(Stand = paste0(forest_own1, ObjectID))

# Create a Spatraster from the dataframe and then reporject to the appropriate dimensions
piedmontStands <- as_spatraster(huc12Stands[,c(1,2,5)], xycols = c(1,2), crs = crs(piedmontOwnership))
piedmontStands <- terra::project(piedmontStands, piedmontOwnership, method = "near")

plot(piedmontStands, col = rep(Random, 500))


# writeRaster(piedmontStands,
#             filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/treeMap/Storage/largePiedmontStands.tif",
#             datatype = "INT4U",
#             overwrite = TRUE,
#             NAflag = NA)
```


```{r}
# Polygonize the larger stands raster
standPolygon <- as.polygons(piedmontStands) %>% st_as_sf(.)

# use st_intersection to cookie cutter the stands polygon that we made from NC rivers and roads in QGIS
unionStands <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/treeMap/Storage/Stands Polygon/qgisPolygon.shp") %>%
  st_intersection(., clippedPiedmont.shp) %>%
  st_intersection(., standPolygon)

# Convert stand numbers to their row ID and then rasterize
unionStands <- unionStands  %>% mutate(Stand = row_number())
smallStandsRast <- rasterize(unionStands, piedmontOwnership, field = "Stand", touchers = TRUE)

# plot(smallStandsRast, col = rep(Random, 500))

# writeRaster(smallStandsRast,
#             filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/treeMap/Harvest/standsRast.tif",
#             datatype = "INT4U",
#             overwrite = TRUE,
#             NAflag = NA)
```



# THIS SECTION IS FOR CLEANING THE STAND RASTER

```{r}
Random <- brewer.pal(13, "Set3")

# # Read in the HUC10 watershed files
piedmontOwnership250m <- rast("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/ownershipRaster250m.tif")
# HUC10 <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/HUC 8 Watersheds/Shape/WBDHU10.shp") %>%
#   st_transform(crs = crs(piedmontOwnership250m))
# huc10Rast <- rasterize(HUC10, piedmontOwnership250m, field = "ObjectID")
# huc10Rast <- mask(huc10Rast, piedmontOwnership250m)
# huc10Df <- as.data.frame(huc10Rast, xy = TRUE)
# ownershipDf <- as.data.frame(piedmontOwnership250m, xy = TRUE)
# huc10Stands <- right_join(huc10Df, ownershipDf, by = c("x", "y"))
# huc10Stands <- huc10Stands %>% mutate(Stand = paste0(forest_own1, ObjectID))
# huc10StandsRast <- rast(huc10Stands[,c(1,2,5)], extent = ext(piedmontOwnership250m), crs = crs(piedmontOwnership250m), type = "xyz")
# plot(huc10StandsRast, col = rep(Random, 500))


HUC12 <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/HUC 8 Watersheds/Shape/WBDHU12.shp") %>%
  st_transform(crs = crs(piedmontOwnership250m))
huc12Rast <- rasterize(HUC12, piedmontOwnership250m, field = "ObjectID")
huc12Rast <- mask(huc12Rast, piedmontOwnership250m)
huc12Df <- as.data.frame(huc12Rast, xy = TRUE)
ownershipDf <- as.data.frame(piedmontOwnership250m, xy = TRUE)
huc12Stands <- right_join(huc12Df, ownershipDf, by = c("x", "y"))
huc12Stands <- huc12Stands %>% mutate(Stand = paste0(forest_own1, ObjectID))
huc12StandsRast <- rast(huc12Stands[,c(1,2,5)], extent = ext(piedmontOwnership250m), crs = crs(piedmontOwnership250m), type = "xyz")
plot(huc12StandsRast, col = rep(Random, 500))

writeRaster(huc12StandsRast,
            filename = "C:/Users/lagoodal/Desktop/All Raster Layers/standsRaster/huc12Stands.tif",
            datatype = "FLT4S",
            overwrite = TRUE)

#----CLIPPED STANDS----#
# Clip and reproject the stands raster to fit the clipped criteria
clippedStandsRast <- huc12StandsRast
clippedHUC.Shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedHUC.shp")
clippedStandsRast <- clippedStandsRast %>% crop(clippedHUC.Shp) %>% mask(clippedHUC.Shp)

# Create a template raster. clippedPiedmont[[10]] is from the Clipped Landscape.Rmd
templateRaster <- rast(crs = crs(clippedPiedmont[[10]]), ext = terra::ext(clippedPiedmont[[10]]), resolution = sqrt(5000))

# Project the stands raster to the higher resolution template raster
clippedStandsRast <- terra::project(clippedStandsRast, templateRaster, method = "near")
# standIDs <- clippedStandsRast %>% as.data.frame() %>% unique() %>% arrange(Stand) %>% cbind(., c(1:156)) %>% `colnames<-`(c("Stand", "standID"))
# testRasterDf <- as.data.frame(clippedStandsRast, xy = TRUE)
# testRasterDf <- testRasterDf %>% left_join(standIDs, by = "Stand")
# clippedStandsRast <- as_spatraster(testRasterDf[,c(1,2,4)])

uniqueValues <- unique(clippedStandsRast)
lookupTable <- data.frame(oldValue = uniqueValues, newValue = 1:nrow(uniqueValues))
reclassMatrix <- as.matrix(lookupTable)
clippedStandsRast <- classify(clippedStandsRast, rcl = reclassMatrix)

newValues <- lookupTable$newValue
```

# I kind of forgot what I did here, but it essentially just makes sure that all stands fall within one management area.
# It works so we're gonna keep on moving

```{r}
# Use ifel statement to change the stands within the map
clippedStandsRast <- ifel(clippedStandsRast == 13, 6, ifel(clippedStandsRast == 14, 4, ifel(clippedStandsRast == 22, 21, ifel(clippedStandsRast == 24, 6, ifel(clippedStandsRast == 25, 27, ifel(clippedStandsRast == 28, 57,ifel(clippedStandsRast == 29, 31,ifel(clippedStandsRast == 30, 9,ifel(clippedStandsRast == 37, 39,ifel(clippedStandsRast == 50, 49,ifel(clippedStandsRast == 54, 57,ifel(clippedStandsRast == 55, 108,ifel(clippedStandsRast %in% c(74,75), 1,ifel(clippedStandsRast == 76, 82,ifel(clippedStandsRast == 77, 83,ifel(clippedStandsRast == 79, 87,ifel(clippedStandsRast == 80, 87,ifel(clippedStandsRast == 91, 67,ifel(clippedStandsRast == 93, 11,ifel(clippedStandsRast == 97, 39,ifel(clippedStandsRast == 98, 38,ifel(clippedStandsRast == 99, 39,ifel(clippedStandsRast == 106, 21,ifel(clippedStandsRast == 119, 118,ifel(clippedStandsRast %in% c(121,122,123,125,126), 127, clippedStandsRast)))))))))))))))))))))))))

# Broke it up because it was such a long ifel statement               
clippedStandsRast <- ifel(clippedStandsRast == 133, 156,ifel(clippedStandsRast == 135, 156,ifel(clippedStandsRast == 137, 15,ifel(clippedStandsRast == 147, 150,ifel(clippedStandsRast == 148, 66,ifel(clippedStandsRast == 153, 127,ifel(clippedStandsRast == 42, 27,ifel(clippedStandsRast == 43, 41,ifel(clippedStandsRast %in% c(71, 72), 53,ifel(clippedStandsRast == 73, 83,ifel(clippedStandsRast == 88, 86,ifel(clippedStandsRast == 89, 87,ifel(clippedStandsRast == 90, 66,ifel(clippedStandsRast == 109, 108,ifel(clippedStandsRast == 114, 110,ifel(clippedStandsRast == 116, 117,ifel(clippedStandsRast == 120, 108,ifel(clippedStandsRast == 124, 131,ifel(clippedStandsRast == 132, 135,ifel(clippedStandsRast == 134, 111,ifel(clippedStandsRast == 139, 152,ifel(clippedStandsRast == 140, 145,ifel(clippedStandsRast == 141, 145,ifel(clippedStandsRast %in% c(142,143), 144,ifel(clippedStandsRast == 154, 156,ifel(clippedStandsRast == 155, 156,clippedStandsRast))))))))))))))))))))))))))

# Reclassify to new unique numbers of 1:99 instead of the non-sequential numbers they were before
uniqueValues <- unique(clippedStandsRast)
lookupTable <- data.frame(oldValue = uniqueValues, newValue = 1:nrow(uniqueValues))
reclassMatrix <- as.matrix(lookupTable)
clippedStandsRast <- classify(clippedStandsRast, rcl = reclassMatrix)

# Let's figure out which stands are in which management areas
# Create the clipped raster for ownership in the Piedmont
ecoregionsClipped <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Clipped Piedmont/ecoregions.tif")
clippedPiedmontOwnership <- piedmontOwnership250m
clippedPiedmontOwnership <- clippedPiedmontOwnership %>%
  crop(clippedHUC.Shp) %>%
  mask(clippedHUC.Shp)
clippedPiedmontOwnership <- terra::project(clippedPiedmontOwnership, templateRaster, method = "near")
clippedPiedmontOwnership <- mask(clippedPiedmontOwnership, ecoregionsClipped)

# I have to find out if any stands straddle management areas and then reassign them to be their own unique stand
# Some are small, but for now this will work
stand_values <- values(clippedStandsRast)
management_values <- values(clippedPiedmontOwnership)
standMgmtDf <- data.frame(Stand = stand_values, Management = management_values, Cell = seq_along(stand_values))

# Table for the Stands that are in multiple management zones
cells_in_multiple_zones <- standMgmtDf %>%
  group_by(Stand) %>%
  summarise(ManagementZones = n_distinct(forest_own1)) %>%
  filter(ManagementZones > 1)
combined_data <- standMgmtDf %>%
  mutate(NewStand = as.integer(factor(paste0(Stand, forest_own1, sep = "_"))))
combined_data$NewStand <- ifelse(combined_data$NewStand == 115, NA, combined_data$NewStand)
values(clippedStandsRast) <- combined_data$NewStand

# writeRaster(clippedStandsRast,
#             "C:/Users/lagoodal/Desktop/TESTING FOR OAK GROWTH/Harvest/clippedStandsRastTEST.tif",
#             overwrite = TRUE,
#             datatype = "INT1U")

plot(clippedStandsRast)

```



```{r}
# I tried several ways to do this but to no avail. I had to export clippedStandsRast into QGIS and also roadsNC (seen below)
# In there I converted clippedStandsRast to a shapefile of polygons. I did the same for roadsNC. Then I performed a un ion on them.
# Now I will bring them back in and attempt to re-rasterise them

# roadsNC <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Data/County Roads/State_Maintained_Roads.shp") %>%
#   st_zm(., drop = TRUE) %>%
#   st_transform(crs = crs(clippedStandsRast)) %>%
#   st_crop(., clippedStandsRast)
# roadsNC <- roadsNC[,c(5,12,13)]
# 
# st_write(roadsNC,
#          dsn = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Data/County Roads/Clipped/roadsNC.shp")

# Bring the union of roadsNC and clippedStandsRast back in
unionStands <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Data/County Roads/Clipped/Nearly Finished/standsPolygon.shp") %>%
  st_intersection(., clippedHUC.shp)
# Convert stand numbers to their row ID and then rasterize
unionStands <- unionStands  %>% mutate(Stand = row_number())
smallStandsRast <- rasterize(unionStands, clippedStandsRast, field = "Stand", touchers = TRUE)

# change stand values so they start sequentially from 1
uniqueValues <- unique(smallStandsRast)
lookupTable <- data.frame(oldValue = uniqueValues, newValue = 1:nrow(uniqueValues))
reclassMatrix <- as.matrix(lookupTable)
smallStandsRast <- classify(smallStandsRast, rcl = reclassMatrix)

# plot(smallStandsRast, col = rep(Random, 500))
# plot(clippedPiedmontOwnership)

# During the rasterization process some cells on the edges weren't assigned a Stand value
# and for now I couldn't figure out a way of doing a clean nearest neighbour interpolation.
# For ow I will just make those edge MAs into NAs and fix later

# Create a table to find the Management Area cell positions that are causing a problem.
valuesSmallStandsRast <- values(smallStandsRast)
valuesClippedPiedmontOwnership <- values(clippedPiedmontOwnership)
cellPositions <- expand.grid(col = 1:ncol(smallStandsRast),row = 1:nrow(smallStandsRast))
cellPositions <- cbind(cellPositions, valuesSmallStandsRast, valuesClippedPiedmontOwnership) %>%
  `colnames<-`(c("col", "row", "Stand", "ManagementArea")) %>%
  mutate(Cell = 1:nrow(.))

# Create a seperate table where I will change the problem cells
alteredMAs <- cellPositions %>%
  filter(ManagementArea > 0 & is.na(Stand)) %>%
  mutate(ManagementArea = ifelse(ManagementArea > 0, NA, ManagementArea))

# Change the cell values to NA at the correct positions
values(clippedPiedmontOwnership)[alteredMAs$Cell] <- NA


writeRaster(clippedPiedmontOwnership,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/fakeOwnership.tif",
            datatype = "INT1U",
            overwrite = TRUE)



writeRaster(smallStandsRast,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/smallStandsRast.tif",
            datatype = "INT4S",
            overwrite = TRUE,
            NAflag  = 0)


x <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/smallStandsRast.tif")
plot(x)
datatype(x)
```



# change stand values so they start sequentially from 1
uniqueValues <- unique(smallStandsRast)
lookupTable <- data.frame(oldValue = uniqueValues, newValue = 1:nrow(uniqueValues))
reclassMatrix <- as.matrix(lookupTable)
smallStandsRast <- classify(smallStandsRast, rcl = reclassMatrix)




# # Let's find out if with this new stands map, any of the stands/cells fall into
# # different management zones
# valuesSmallStandsRast <- values(smallStandsRast)
# valuesClippedPiedmontOwnership <- values(clippedPiedmontOwnership)
# cellPositions <- expand.grid(col = 1:ncol(smallStandsRast),row = 1:nrow(smallStandsRast))
# cellPositions <- cbind(cellPositions, valuesSmallStandsRast, valuesClippedPiedmontOwnership) %>%
#   `colnames<-`(c("col", "row", "Stand", "ManagementArea"))
# 
# # Filter down to get a table that has just the stands that are in different management zones
# cellPositions %>%
#   drop_na() %>%
#   group_by(Stand) %>%
#   summarise(uniqueMA = n_distinct(ManagementArea)) %>%
#   filter(uniqueMA > 1)
# 
# 
# cellPositions %>%
#   filter(Stand == 255)

```



```{r}
r <- rast(ncol=10, nrow=10)
values(r) <- round(runif(ncell(r)) * 2) + 1
r[c(1,7,12,63)] <- NA
plot(r)

f <- focal(r, 3, "modal", na.policy="only")
plot(f, col=c('red', 'green', 'blue'))
plot(r, col=c('red', 'green', 'blue'))





plot(smallStandsRast, col = rep(Random, 500))
plot(fake)
plot(clippedPiedmontOwnership)



x <- cover(smallStandsRast, fake)
plot(smallStandsRast, col = rep(Random, 500))
plot(x, col = rep(Random, 500))
plot(fake)

z <- ifel(x == 1, x, NA)
plot(z)

##########################
test <- smallStandsRast
test <- focal(x, 3, "modal", na.policy = "only")
plot(test, col = rep(Random, 500))
plot(fake)





fakeRast <- x
cell_indices <- cells$Cell
coords <- xyFromCell(fakeRast, cell_indices)

r_interp <- rast(fakeRast)
values(r_interp) <- NA
values(r_interp)[cell_indices] <- values(fakeRast)[cell_indices]

r_interp <- resample(r_interp, fakeRast, method = "near")

plot(r_interp)
```
















```{r}
# Testing to see if w need to pre-mask the stand/management areas with the ecoregions tif
# I thought that this would be done automatically, but it keeps thinking NAs are straddling mgmt zones
# ecoregionsClipped <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Clipped Piedmont/ecoregions.tif")
# ecoregionsClipped <- ifel(ecoregionsClipped == 0, NA, ecoregionsClipped)
# clippedStandsRast <- mask(clippedStandsRast, ecoregionsClipped)
writeRaster(clippedStandsRast,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/clippedStandsRast.tif",
            datatype = "INT1U",
            overwrite = TRUE)

#----MANAGEMENT AREAS----#
clippedPiedmontOwnership <- piedmontOwnership250m
clippedPiedmontOwnership <- clippedPiedmontOwnership %>%
  crop(clippedHUC.Shp) %>%
  mask(clippedHUC.Shp)
clippedPiedmontOwnership <- terra::project(clippedPiedmontOwnership, templateRaster, method = "near")
clippedPiedmontOwnership <- mask(clippedPiedmontOwnership, ecoregionsClipped)

# clippedPiedmontOwnership[is.na(clippedPiedmontOwnership)] <- 0

writeRaster(clippedPiedmontOwnership,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/clippedPiedmontOwnership.tif",
            datatype = "INT1U",
            overwrite = TRUE,
            NAflag = NA)

# Some stands are falling across two management areas which is not allowed in LANDIS
# To get around this I will have to manually find the management area cells and change them
test <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/clippedStandsRast.tif")
testMgmt <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/clippedPiedmontOwnership.tif")
extracted_values <- ifel(test == 34, testMgmt, NA)
# plot(extracted_values)

# Get row/col values that match our criteria
cell_indices <- which(values(extracted_values) %in% c(2,3))
positions <- rowColFromCell(extracted_values, cell_indices)
# Couldn't figure out a for loop to do this bit
clippedPiedmontOwnership[353,433] <- 1
clippedPiedmontOwnership[353,434] <- 1
clippedPiedmontOwnership[353,435] <- 1
clippedPiedmontOwnership[353,436] <- 1
clippedPiedmontOwnership[353,437] <- 1
clippedPiedmontOwnership[353,438] <- 1
clippedPiedmontOwnership[353,439] <- 1
clippedPiedmontOwnership[353,444] <- 1
clippedPiedmontOwnership[353,445] <- 1
clippedPiedmontOwnership[353,446] <- 1
clippedPiedmontOwnership[353,451] <- 1
clippedPiedmontOwnership[353,452] <- 1
clippedPiedmontOwnership[353,453] <- 1
clippedPiedmontOwnership[353,454] <- 1
clippedPiedmontOwnership[353,455] <- 1
clippedPiedmontOwnership[353,456] <- 1
clippedPiedmontOwnership[353,457] <- 1
clippedPiedmontOwnership[353,461] <- 1
clippedPiedmontOwnership[353,462] <- 1
clippedPiedmontOwnership[353,463] <- 1
clippedPiedmontOwnership[353,464] <- 1
clippedPiedmontOwnership[353,468] <- 1
clippedPiedmontOwnership[353,469] <- 1
clippedPiedmontOwnership[353,470] <- 1
clippedPiedmontOwnership[353,471] <- 1
clippedPiedmontOwnership[353,479] <- 1
clippedPiedmontOwnership[353,480] <- 1
clippedPiedmontOwnership[353,481] <- 1
clippedPiedmontOwnership[353,482] <- 1
# Repeat for other stands in a similar situation
extracted_values <- ifel(test == 136, testMgmt, NA)
cell_indices <- which(values(extracted_values) %in% c(1,2))
positions <- rowColFromCell(extracted_values, cell_indices)
clippedPiedmontOwnership[353,476] <- 3
clippedPiedmontOwnership[353,477] <- 3
clippedPiedmontOwnership[353,478] <- 3
clippedPiedmontOwnership[353,490] <- 3
clippedPiedmontOwnership[353,491] <- 3
clippedPiedmontOwnership[353,492] <- 3
clippedPiedmontOwnership[353,497] <- 3
clippedPiedmontOwnership[353,498] <- 3
clippedPiedmontOwnership[353,499] <- 3
clippedPiedmontOwnership[353,500] <- 3
clippedPiedmontOwnership[353,501] <- 3
clippedPiedmontOwnership[353,502] <- 3
clippedPiedmontOwnership[353,503] <- 3
clippedPiedmontOwnership[353,507] <- 3
clippedPiedmontOwnership[353,508] <- 3
clippedPiedmontOwnership[353,509] <- 3
clippedPiedmontOwnership[353,510] <- 3
clippedPiedmontOwnership[353,511] <- 3
clippedPiedmontOwnership[353,512] <- 3
clippedPiedmontOwnership[353,513] <- 3
clippedPiedmontOwnership[353,514] <- 3
clippedPiedmontOwnership[353,515] <- 3
clippedPiedmontOwnership[353,516] <- 3
clippedPiedmontOwnership[353,517] <- 3

extracted_values <- ifel(test == 138, testMgmt, NA)
cell_indices <- which(values(extracted_values) %in% c(2))
positions <- rowColFromCell(extracted_values, cell_indices)
clippedPiedmontOwnership[353,582] <- 3
clippedPiedmontOwnership[353,583] <- 3
clippedPiedmontOwnership[353,584] <- 3
clippedPiedmontOwnership[353,589] <- 3
clippedPiedmontOwnership[353,590] <- 3
clippedPiedmontOwnership[353,591] <- 3

writeRaster(clippedPiedmontOwnership,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Clipped Test/test1/Harvest/clippedPiedmontOwnership.tif",
            datatype = "INT1U",
            overwrite = TRUE,
            NAflag = NA)


```
















