---
title: "Untitled"
output: pdf_document
date: "2024-08-09"
---


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(rFIA)
options(scipen = 999)
```



```{r}
piedmontBoundary <- st_read("C:/Users/lagoodal/Desktop/nc_eco_l3/Piedmont UTM 17N.shp")
NC_FIA <- readFIA("C:/Users/lagoodal/Desktop/FIA_NC_2021/All")
# REF_SPECIES <- readxl::read_excel("C:/Users/lagoodal/Desktop/Dissertation Stuff/USFS Coefficients/REF_SPECIES.xlsx")

# Create FORTYP column
NC_FIA$COND$FORTYP <- ifelse(NC_FIA$COND$FORTYPCD %in% 100:199, "Softwoods",
       ifelse(NC_FIA$COND$FORTYPCD %in% 400:499, "Oak-Pine",
              ifelse(NC_FIA$COND$FORTYPCD %in% 500:599, "Oak-Hickory",
                     ifelse(NC_FIA$COND$FORTYPCD %in% 600:699, "Oak-Gum-Cypress",
                            ifelse(NC_FIA$COND$FORINDCD %in% 700:799, "Elm-Ash-Cottonwood",
                                   ifelse(NC_FIA$COND$FORTYPCD %in% 800:899, "Maple-Beech-Birch",
                                          ifelse(NC_FIA$COND$FORTYPCD %in% 900:950, "Aspen-Birch", "Other")))))))

# Read in a table that matches SPCDs to common names
fiaSPCDs <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/FIADB Species List.csv")
fiaSPCDs <- fiaSPCDs %>% drop_na()
fiaSPCDs$COMMON_NAME <- str_to_title(fiaSPCDs$COMMON_NAME)

# Filter for stands that have a natural origin i.e. not a plantation
# NC_FIA$COND <- NC_FIA$COND %>%
#   filter(STDORGCD == 0)

# Ifelse statement to attach Taxonomic Family to the TREE table
NC_FIA$TREE <- NC_FIA$TREE %>%
  inner_join(fiaSPCDs, by = "SPCD")
# Add SCIENTFIC FAMILY
NC_FIA$TREE$SCIENTIFIC_FAMILY <- ifelse(grepl("Liquidambar", NC_FIA$TREE$`Scientific Name`), "Altingiaceae",ifelse(grepl("Asiminia", NC_FIA$TREE$`Scientific Name`), "Annonaceae",ifelse(grepl("Ilex", NC_FIA$TREE$`Scientific Name`), "Aquifoliaceae",ifelse(grepl("Betula", NC_FIA$TREE$`Scientific Name`), "Betulaceae",ifelse(grepl("Carpinus", NC_FIA$TREE$`Scientific Name`), "Betulaceae",ifelse(grepl("Ostrya", NC_FIA$TREE$`Scientific Name`), "Betulaceae",ifelse(grepl("Catalpa", NC_FIA$TREE$`Scientific Name`), "Bignoniaceae",ifelse(grepl("Celtis", NC_FIA$TREE$`Scientific Name`), "Cannabaceae",ifelse(grepl("Juniperus", NC_FIA$TREE$`Scientific Name`), "Cupressaceae",ifelse(grepl("Taxodium", NC_FIA$TREE$`Scientific Name`), "Cupressaceae",ifelse(grepl("Diospyros", NC_FIA$TREE$`Scientific Name`), "Ebenaceae",ifelse(grepl("Oxydendrum", NC_FIA$TREE$`Scientific Name`), "Ericaceae",ifelse(grepl("Albizia", NC_FIA$TREE$`Scientific Name`), "Fabaceae",ifelse(grepl("Cercis", NC_FIA$TREE$`Scientific Name`), "Fabaceae",ifelse(grepl("Gleditsia", NC_FIA$TREE$`Scientific Name`), "Fabaceae",ifelse(grepl("Robinia", NC_FIA$TREE$`Scientific Name`), "Fabaceae",ifelse(grepl("Castanea", NC_FIA$TREE$`Scientific Name`), "Fagaceae",ifelse(grepl("Fagus", NC_FIA$TREE$`Scientific Name`), "Fagaceae",ifelse(grepl("Quercus", NC_FIA$TREE$`Scientific Name`), "Fagaceae",ifelse(grepl("Carya", NC_FIA$TREE$`Scientific Name`), "Juglandaceae",ifelse(grepl("Juglans", NC_FIA$TREE$`Scientific Name`), "Juglandaceae",ifelse(grepl("Persea", NC_FIA$TREE$`Scientific Name`), "Lauraceae",ifelse(grepl("Sassafras", NC_FIA$TREE$`Scientific Name`), "Lauraceae",ifelse(grepl("Liriodendron", NC_FIA$TREE$`Scientific Name`), "Magnoliaceae",ifelse(grepl("Magnolia", NC_FIA$TREE$`Scientific Name`), "Magnoliaceae",ifelse(grepl("Tilia", NC_FIA$TREE$`Scientific Name`), "Malvaceae",ifelse(grepl("Morus", NC_FIA$TREE$`Scientific Name`), "Moraceae",ifelse(grepl("Nyssa", NC_FIA$TREE$`Scientific Name`), "Nyssaceae",ifelse(grepl("Fraxinus", NC_FIA$TREE$`Scientific Name`), "Oleaceae",ifelse(grepl("Paulownia", NC_FIA$TREE$`Scientific Name`), "Paulowniaceae",
ifelse(grepl("Pinus", NC_FIA$TREE$`Scientific Name`), "Pinaceae",
ifelse(grepl("Tsuga", NC_FIA$TREE$`Scientific Name`), "Pinaceae",
ifelse(grepl("Platanus", NC_FIA$TREE$`Scientific Name`), "Platanaceae",
ifelse(grepl("Amelanchier", NC_FIA$TREE$`Scientific Name`), "Rosaceae",ifelse(grepl("Crataegus", NC_FIA$TREE$`Scientific Name`), "Rosaceae",ifelse(grepl("Malus", NC_FIA$TREE$`Scientific Name`), "Rosaceae",ifelse(grepl("Prunus", NC_FIA$TREE$`Scientific Name`), "Rosaceae",ifelse(grepl("Pyrus", NC_FIA$TREE$`Scientific Name`), "Rosaceae",ifelse(grepl("Populus", NC_FIA$TREE$`Scientific Name`), "Salicaceae",ifelse(grepl("Salix",NC_FIA$TREE$`Scientific Name`), "Salicaceae",ifelse(grepl("Acer", NC_FIA$TREE$`Scientific Name`), "Sapindaceae",ifelse(grepl("Aesculus", NC_FIA$TREE$`Scientific Name`), "Sapindaceae",ifelse(grepl("Ailanthus", NC_FIA$TREE$`Scientific Name`), "Simaroubaceae",ifelse(grepl("Halesia", NC_FIA$TREE$`Scientific Name`), "Styracaceae",ifelse(grepl("Ulmus", NC_FIA$TREE$`Scientific Name`), "Ulmaceae", "Other")))))))))))))))))))))))))))))))))))))))))))))


# Get area estimates for each species
areaSppDf <- area(db = NC_FIA,
                  polys = piedmontBoundary[1],
                  grpBy = SPCD,
                  landType = "forest",
                  method = "SMA",
                  totals = TRUE)

areaFORTYPDf <- area(db = NC_FIA,
                     polys = piedmontBoundary[1],
                     grpBy = FORTYP,
                     landType = "forest",
                     method = "SMA",
                     totals = TRUE)

# Species
treeVolBioDf <- growMort(db = NC_FIA,
         landType = "forest",
         treeType = "all",
         totals = TRUE,
         bySpecies = FALSE,
         polys = piedmontBoundary[1],
         stateVar = "BIO_AG",
         grpBy = SPCD)


# Estimates for converting from lbs/ac to Mg/ha
treeVolBioDf %>%
  filter(YEAR == 2022) %>%
  select(YEAR, SPCD, REMV_BIO_AG_ACRE, REMV_TOTAL) %>%
  inner_join(areaSppDf, by = c("YEAR", "SPCD")) %>%
  inner_join(fiaSPCDs, by = "SPCD") %>%
  select(YEAR, SPCD, COMMON_NAME, REMV_BIO_AG_ACRE, REMV_TOTAL, AREA_TOTAL) %>%
  mutate(LBS_ACRE = REMV_TOTAL / AREA_TOTAL,
         MG_HEC = LBS_ACRE * 0.00112085,
         TEST_HEC = REMV_BIO_AG_ACRE * 0.00112085)




treeVolBioDf %>%
  select(YEAR, SPCD, REMV_BIO_AG_ACRE, REMV_TOTAL) %>%
  inner_join(areaSppDf, by = c("YEAR", "SPCD")) %>%
  inner_join(fiaSPCDs, by = "SPCD") %>%
  select(YEAR, SPCD, COMMON_NAME, REMV_BIO_AG_ACRE, REMV_TOTAL, AREA_TOTAL) %>%
  group_by(COMMON_NAME) %>%
  summarise(LBS_AC = mean(REMV_BIO_AG_ACRE)) %>%
  mutate(MG_HEC = LBS_AC * 0.00112085)


```


# Estimates for converting from tons/acre to Mg/ha
treeVolBioDf %>%
  filter(YEAR == 2022) %>%
  select(YEAR, SPCD, REMV_BIO_AG_ACRE, REMV_TOTAL) %>%
  inner_join(areaSppDf, by = c("YEAR", "SPCD")) %>%
  inner_join(fiaSPCDs, by = "SPCD") %>%
  select(YEAR, SPCD, COMMON_NAME, REMV_BIO_AG_ACRE, REMV_TOTAL, AREA_TOTAL) %>%
  mutate(TONS_ACRE = REMV_TOTAL / AREA_TOTAL,
         MG_HEC = TONS_ACRE * 2.2417,
         TEST_HEC = REMV_BIO_AG_ACRE * 2.2417)


# FORTYP
treeVolBioFORTYPDf <- growMort(db = NC_FIA,
         landType = "forest",
         treeType = "all",
         totals = TRUE,
         bySpecies = FALSE,
         grpBy = FORTYP,
         polys = piedmontBoundary[1],
         stateVar = "BIO_AG")


# Estimates for converting from lbs/ac to Mg/ha
treeVolBioFORTYPDf %>%
  filter(YEAR == 2022) %>%
  select(YEAR, FORTYP, REMV_BIO_AG_ACRE, REMV_TOTAL) %>%
  inner_join(areaFORTYPDf, by = c("YEAR", "FORTYP")) %>%
  select(YEAR, FORTYP, REMV_BIO_AG_ACRE, REMV_TOTAL, AREA_TOTAL) %>%
  mutate(LBS_ACRE = REMV_TOTAL / AREA_TOTAL,
         MG_HEC = LBS_ACRE * 0.00112085,
         TEST_HEC = REMV_BIO_AG_ACRE * 0.00112085)

# Estimates for converting from tons/ac to Mg/hec
treeVolBioFORTYPDf %>%
  filter(YEAR == 2022) %>%
  select(YEAR, FORTYP, REMV_BIO_AG_ACRE, REMV_TOTAL) %>%
  inner_join(areaFORTYPDf, by = c("YEAR", "FORTYP")) %>%
  select(YEAR, FORTYP, REMV_BIO_AG_ACRE, REMV_TOTAL, AREA_TOTAL) %>%
  mutate(TONS_ACRE = REMV_TOTAL / AREA_TOTAL,
         MG_HEC = TONS_ACRE * 2.2417,
         TEST_HEC = REMV_BIO_AG_ACRE * 2.2417)

```
















