---
title: "Untitled"
output: pdf_document
date: "2024-12-18"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(corrplot)
# library(vegan)
library(data.table)
options(scipen = 999)
templateRaster <- rast("D:/Landis Outputs/Raster Template/templateRaster.tif")
softwoods <- c("JUVI","PIEC2","PIPA2","PIST","PITA","PIVI2","TAAS","TADI2")
oaks <- c("QUAL","QUCO2","QUFA","QULA3","QUNI","QUPH","QUPR2","QURU","QUST","QUVE")
hardwoods <- c("ACRU","CAAL27","CAGL8","FAGR","FRAM2","FRPE","LIST2","LITU","NYBI","NYSY","OXAR","PRSE2")
```


# RESISTANCE
## RCP45
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP45/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resistance")

# Proportional composition
propBiomass_BNU_ESM_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP45_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP45_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "BNU-ESM_RCP45") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP45")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP45_Resistance <- propBiomass_BNU_ESM_RCP45_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP45_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

successionLog_BNU_ESM_RCP45_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP45", RCP = "RCP45", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP45_ResistanceDf <- bind_rows(results)


#----STRUCTURAL DIVERSITY----#
# ATTENTION
# This section require lots of RAM and has to cycle through a lot of rows in the dataframe.
# Because of that all Structural Diversity sections will need to be exported to the HPC
# # for this piece of the analysis
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP45/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resistance")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP45_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP45_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MIROC-ESM-CHEM_RCP45") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP45_Resistance <- propBiomass_MIROC_ESM_CHEM_RCP45_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP45_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

successionLog_MIROC_ESM_CHEM_RCP45_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP45", RCP = "RCP45", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP45_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
combinedData <- list()
index <- 1

for (run in runs) {
  runDir <- file.path(mainDir, run)
  for (year in seq(0, 80, by = 10)) {
    filename <- paste0("community-input-file-", year, ".csv")
    filePath <- file.path(runDir, filename)
    data <- fread(filePath)
    data <- data %>% mutate(across(where(is.double), as.integer))
    data$Run <- run
    data$Time <- year
    combinedData[[index]] <- data
    index <- index + 1
  }
}

combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
  df <- combinedData[[i]]
  return(df)
}))

fwrite(combinedData,
       file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP45/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resistance")

# Proportional composition
propBiomass_MRI_CGCM3_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP45_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP45_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MRI-CGCM3_RCP45") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MRI_CGCM3_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP45")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP45_Resistance <- propBiomass_MRI_CGCM3_RCP45_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP45_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

successionLog_MRI_CGCM3_RCP45_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP45", RCP = "RCP45", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP45_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP45/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resistance")

# Proportional composition
propBiomass_CCSM4_RCP45_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP45_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP45_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "CCSM4_RCP45") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
CCSM4_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP45")

#----BIODIVERSITY----#
diversity_CCSM4_RCP45_Resistance <- propBiomass_CCSM4_RCP45_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP45_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

successionLog_CCSM4_RCP45_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP45", RCP = "RCP45", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_CCSM4_RCP45_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

## RCP85
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP85/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resistance")

# Proportional composition
propBiomass_BNU_ESM_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP85_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP85_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "BNU-ESM_RCP85") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP85")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP85_Resistance <- propBiomass_BNU_ESM_RCP85_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP85_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

successionLog_BNU_ESM_RCP85_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP85", RCP = "RCP85", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP85_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP85/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resistance")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP85_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP85_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MIROC-ESM-CHEM_RCP85") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP85_Resistance <- propBiomass_MIROC_ESM_CHEM_RCP85_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP85_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

successionLog_MIROC_ESM_CHEM_RCP85_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP85", RCP = "RCP85", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP85_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP85/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resistance")

# Proportional composition
propBiomass_MRI_CGCM3_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP85_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP85_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MRI-CGCM3_RCP85") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MRI_CGCM3_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP85")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP85_Resistance <- propBiomass_MRI_CGCM3_RCP85_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP85_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

successionLog_MRI_CGCM3_RCP85_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP85", RCP = "RCP85", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP85_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resistance/RCP85/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resistance")

# Proportional composition
propBiomass_CCSM4_RCP85_Resistance <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resistance",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP85_Resistance_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resistance")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP85_Resistance <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "CCSM4_RCP85") %>%
  mutate(Prescription = "Resistance")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
CCSM4_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP85")

#----BIODIVERSITY----#
diversity_CCSM4_RCP85_Resistance <- propBiomass_CCSM4_RCP85_Resistance[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP85_Resistance <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

successionLog_CCSM4_RCP85_Resistance_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resistance")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP85", RCP = "RCP85", Prescription = "Resistance")
  results[[i]] <- df
}
AWB_CCSM4_RCP85_ResistanceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

# RESILIENCE
## RCP45
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP45/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resilience")

# Proportional composition
propBiomass_BNU_ESM_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP45_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP45_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "BNU-ESM_RCP45") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP45")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP45_Resilience <- propBiomass_BNU_ESM_RCP45_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP45_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

successionLog_BNU_ESM_RCP45_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP45", RCP = "RCP45", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP45_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP45/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resilience")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP45_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP45_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MIROC-ESM-CHEM_RCP45") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP45_Resilience <- propBiomass_MIROC_ESM_CHEM_RCP45_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP45_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

successionLog_MIROC_ESM_CHEM_RCP45_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP45", RCP = "RCP45", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP45_ResilienceDf <- bind_rows(results)

# #----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP45/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resilience")

# Proportional composition
propBiomass_MRI_CGCM3_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP45_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP45_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MRI-CGCM3_RCP45") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP45")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP45_Resilience <- propBiomass_MRI_CGCM3_RCP45_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP45_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

successionLog_MRI_CGCM3_RCP45_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP45", RCP = "RCP45", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP45_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP45/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resilience")

# Proportional composition
propBiomass_CCSM4_RCP45_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP45_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP45_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "CCSM4_RCP45") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP45")

#----BIODIVERSITY----#
diversity_CCSM4_RCP45_Resilience <- propBiomass_CCSM4_RCP45_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP45_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

successionLog_CCSM4_RCP45_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP45", RCP = "RCP45", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_CCSM4_RCP45_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

## RCP85
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP85/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resilience")

# Proportional composition
propBiomass_BNU_ESM_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP85_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP85_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "BNU-ESM_RCP85") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP85")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP85_Resilience <- propBiomass_BNU_ESM_RCP85_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP85_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

successionLog_BNU_ESM_RCP85_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP85", RCP = "RCP85", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP85_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP85/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resilience")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP85_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP85_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MIROC-ESM-CHEM_RCP85") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP85_Resilience <- propBiomass_MIROC_ESM_CHEM_RCP85_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP85_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

successionLog_MIROC_ESM_CHEM_RCP85_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP85", RCP = "RCP85", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP85_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP85/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resilience")

# Proportional composition
propBiomass_MRI_CGCM3_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP85_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP85_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MRI-CGCM3_RCP85") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP85")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP85_Resilience <- propBiomass_MRI_CGCM3_RCP85_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP85_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

successionLog_MRI_CGCM3_RCP85_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP85", RCP = "RCP85", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP85_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Resilience/RCP85/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resilience")

# Proportional composition
propBiomass_CCSM4_RCP85_Resilience <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resilience",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP85_Resilience_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Resilience")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP85_Resilience <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "CCSM4_RCP85") %>%
  mutate(Prescription = "Resilience")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP85")

#----BIODIVERSITY----#
diversity_CCSM4_RCP85_Resilience <- propBiomass_CCSM4_RCP85_Resilience[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP85_Resilience <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

successionLog_CCSM4_RCP85_Resilience_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Resilience")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP85", RCP = "RCP85", Prescription = "Resilience")
  results[[i]] <- df
}
AWB_CCSM4_RCP85_ResilienceDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

# TRANSITION
## RCP45
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP45/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Transition")

# Proportional composition
propBiomass_BNU_ESM_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP45_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "BNU-ESM_RCP45",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP45_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "BNU-ESM_RCP45") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP45")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP45_Transition <- propBiomass_BNU_ESM_RCP45_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP45_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

successionLog_BNU_ESM_RCP45_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP45", RCP = "RCP45", Prescription = "Transition")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP45_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP45/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Transition")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP45_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MIROC-ESM-CHEM_RCP45",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP45_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MIROC-ESM-CHEM_RCP45") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP45_Transition <- propBiomass_MIROC_ESM_CHEM_RCP45_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP45_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

successionLog_MIROC_ESM_CHEM_RCP45_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP45", RCP = "RCP45", Prescription = "Transition")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP45_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP45/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Transition")

# Proportional composition
propBiomass_MRI_CGCM3_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP45_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "MRI-CGCM3_RCP45",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP45_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "MRI-CGCM3_RCP45") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MRI_CGCM3_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP45")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP45_Transition <- propBiomass_MRI_CGCM3_RCP45_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP45_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

successionLog_MRI_CGCM3_RCP45_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP45", RCP = "RCP45", Prescription = "Transition")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP45_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP45/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Transition")

# Proportional composition
propBiomass_CCSM4_RCP45_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP45_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP45",
         Model = "CCSM4_RCP45",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP45_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP45", Model = "CCSM4_RCP45") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
CCSM4_RCP45 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP45")

#----BIODIVERSITY----#
diversity_CCSM4_RCP45_Transition <- propBiomass_CCSM4_RCP45_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP45_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

successionLog_CCSM4_RCP45_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP45",
         RCP = "RCP45",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP45", RCP = "RCP45", Prescription = "Transition")
  results[[i]] <- df
}
AWB_CCSM4_RCP45_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

## RCP85
### HSHV (BNU-ESM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP85/HSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_BNU_ESM_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Transition")

# Proportional composition
propBiomass_BNU_ESM_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_BNU_ESM_RCP85_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "BNU-ESM_RCP85",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_BNU_ESM_RCP85_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "BNU-ESM_RCP85") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
BNU_ESM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "BNU-ESM_RCP85")

#----BIODIVERSITY----#
diversity_BNU_ESM_RCP85_Transition <- propBiomass_BNU_ESM_RCP85_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_BNU_ESM_RCP85_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

successionLog_BNU_ESM_RCP85_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "BNU-ESM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "BNU-ESM_RCP85", RCP = "RCP85", Prescription = "Transition")
  results[[i]] <- df
}
AWB_BNU_ESM_RCP85_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### HSLV (MIROC-ESM-CHEM)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP85/HSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MIROC_ESM_CHEM_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Transition")

# Proportional composition
propBiomass_MIROC_ESM_CHEM_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MIROC_ESM_CHEM_RCP85_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MIROC-ESM-CHEM_RCP85",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MIROC_ESM_CHEM_RCP85_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MIROC-ESM-CHEM_RCP85") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MIROC_ESM_CHEM_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85")

#----BIODIVERSITY----#
diversity_MIROC_ESM_CHEM_RCP85_Transition <- propBiomass_MIROC_ESM_CHEM_RCP85_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MIROC_ESM_CHEM_RCP85_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

successionLog_MIROC_ESM_CHEM_RCP85_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MIROC-ESM-CHEM_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MIROC-ESM-CHEM_RCP85", RCP = "RCP85", Prescription = "Transition")
  results[[i]] <- df
}
AWB_MIROC_ESM_CHEM_RCP85_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSHV (MRI-CGCM3)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP85/LSHV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_MRI_CGCM3_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Transition")

# Proportional composition
propBiomass_MRI_CGCM3_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_MRI_CGCM3_RCP85_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "MRI-CGCM3_RCP85",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_MRI_CGCM3_RCP85_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "MRI-CGCM3_RCP85") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
MRI_CGCM3_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "MRI-CGCM3_RCP85")

#----BIODIVERSITY----#
diversity_MRI_CGCM3_RCP85_Transition <- propBiomass_MRI_CGCM3_RCP85_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_MRI_CGCM3_RCP85_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

successionLog_MRI_CGCM3_RCP85_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "MRI-CGCM3_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "MRI-CGCM3_RCP85", RCP = "RCP85", Prescription = "Transition")
  results[[i]] <- df
}
AWB_MRI_CGCM3_RCP85_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")
```

### LSLV (CCSM4)

```{r, message = FALSE, warning = FALSE}
#----Spp Biomass----#
mainDir <- "D:/Landis Outputs/Transition/RCP85/LSLV"
runs <- paste0("run", 1:5)
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "spp-biomass-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
finalTable <- do.call(rbind, combinedData) %>%
  select(-`...34`)

# Composition through time
sppBiomass_CCSM4_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""),
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Transition")

# Proportional composition
propBiomass_CCSM4_RCP85_Transition <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Species) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n()))) %>%
  mutate(RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Transition",
         FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                                  ifelse(Species %in% oaks, "Oaks", "Hardwoods")),
         TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

propBiomass_CCSM4_RCP85_Transition_AllRuns <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, Run) %>% # Group by time and run
  mutate(Percent_Biomass = Biomass_MG / sum(Biomass_MG, na.rm = TRUE) * 100,
         RCP = "RCP85",
         Model = "CCSM4_RCP85",
         Prescription = "Transition")

#----Harvesting Rates----#
## Normal
combinedData <- list()
for (run in runs){
  harvestDir <- file.path(mainDir, run, "Harvest")
  filePath <- file.path(harvestDir, "biomass-harvest-summary-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
harvest_CCSM4_RCP85_Transition <- do.call(rbind, combinedData) %>%
  mutate(Prescription_Type = Prescription, RCP = "RCP85", Model = "CCSM4_RCP85") %>%
  mutate(Prescription = "Transition")

#----Climate----#
# For loop to read in future climate data. Then organised into appropriate metrics
climateData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "Climate-future-input-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  climateData[[run]] <- data
}
climateData <- do.call(rbind, climateData) %>%
  select(-`...28`)
CCSM4_RCP85 <- climateData[,c(1,2,5,6,7,28)] %>%
  mutate(mean_airtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year) %>%
  summarise(meanppt = mean(ppt),
            sumppt = sum(ppt),
            airtemp = mean(mean_airtemp)) %>%
  mutate(Model = "CCSM4_RCP85")

#----BIODIVERSITY----#
diversity_CCSM4_RCP85_Transition <- propBiomass_CCSM4_RCP85_Transition[,c(1:3,9)] %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE)) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (run in runs){
  runDir <- file.path(mainDir, run)
  filePath <- file.path(runDir, "NECN-succession-log.csv")
  data <- read_csv(filePath)
  data$Run <- run
  combinedData[[run]] <- data
}
successionLog_CCSM4_RCP85_Transition <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

successionLog_CCSM4_RCP85_Transition_All <- rbind(combinedData[[1]], combinedData[[2]], combinedData[[3]], combinedData[[4]], combinedData[[5]]) %>%
  select(-`...62`) %>%
  group_by(Time, Run) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n())))) %>%
  mutate(Model = "CCSM4_RCP85",
         RCP = "RCP85",
         Prescription = "Transition")

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (run in 1:5) {
  runDir <- file.path(mainDir, paste0("run", run))
  for (year in seq(10, 80, by = 10)) {
    filename <- paste0("Annual-water-budget-", year, ".img")
    filePath <- file.path(runDir, filename)
    rasterData <- rast(filePath)
    crs(rasterData) <- "epsg:26917"
    rasterData <- flip(rasterData)
    newFileName <- sub("\\.img$", paste0("_run", run, ".tif"), filename)
    combinedRasters[[newFileName]] <- rasterData
  }
}

results <- list()
for (i in 1:8) {
  indices <- seq(i, 33 + i, by = 8)
  df <- c(combinedRasters[[indices[1]]], combinedRasters[[indices[2]]], combinedRasters[[indices[3]]], 
          combinedRasters[[indices[4]]], combinedRasters[[indices[5]]]) %>%
    as.data.frame() %>%
    `colnames<-`(c("run1", "run2", "run3", "run4", "run5")) %>%
    pivot_longer(cols = "run1":"run5", values_to = "AWB", names_to = "Run") %>%
    filter(AWB > 0) %>%
    group_by(Run) %>%
    summarise(AWB = mean(AWB)) %>%
    mutate(Time = i * 10, Model = "CCSM4_RCP85", RCP = "RCP85", Prescription = "Transition")
  results[[i]] <- df
}
AWB_CCSM4_RCP85_TransitionDf <- bind_rows(results)

#----STRUCTURAL DIVERSITY----#
# combinedData <- list()
# index <- 1
# 
# for (run in runs) {
#   runDir <- file.path(mainDir, run)
#   for (year in seq(0, 80, by = 10)) {
#     filename <- paste0("community-input-file-", year, ".csv")
#     filePath <- file.path(runDir, filename)
#     data <- fread(filePath)
#     data <- data %>% mutate(across(where(is.double), as.integer))
#     data$Run <- run
#     data$Time <- year
#     combinedData[[index]] <- data
#     index <- index + 1
#   }
# }
# 
# combinedData <- do.call(rbind, lapply(seq_along(combinedData), function(i) {
#   df <- combinedData[[i]]
#   return(df)
# }))
# 
# fwrite(combinedData,
#        file = "C:/Users/lagoodal/Documents/TEST HPC OUTPUTS/combinedData.csv")

```

# Final Data



## Maps
## Total Biomass


## Annual Water Budget

```{r}
mainDir <- "D:/Landis Outputs"
scenarios <- c("Resistance", "Resilience", "Transition")
rcps <- c("RCP45", "RCP85")
climates <- c("HSHV", "HSLV", "LSHV", "LSLV")
runs <- paste0("run",1:5)
timesteps <- seq(10,80,10)

raster_list <- list()
for (scenario in scenarios) {
  for (rcp in rcps) {
    for (climate in climates){
      for (run in runs) {
        for (timestep in timesteps) {
          img_file <- file.path(mainDir, scenario, rcp, climate, run, paste0("Annual-water-budget-", timestep, ".img"))
          raster <- rast(img_file)
          crs(raster) <- "epsg:26917"
          raster <- flip(raster)
          ext(raster) <- ext(templateRaster)
          # raster <- project(raster, res = 70.71068, templateRaster, method = "bilinear")
          # raster_list[[length(raster_list) + 1]] <- raster
          raster_list[[img_file]] <- raster
        }
      }
    }
  }
}



# Resistance
AWB_Resistance_RCP45_HSHV <- c(raster_list[[1]],raster_list[[2]],raster_list[[3]],raster_list[[4]],raster_list[[5]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP45_HSLV <- c(raster_list[[6]],raster_list[[7]],raster_list[[8]],raster_list[[9]],raster_list[[10]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP45_LSHV <- c(raster_list[[11]],raster_list[[12]],raster_list[[13]],raster_list[[14]],raster_list[[15]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP45_LSLV <- c(raster_list[[16]],raster_list[[17]],raster_list[[18]],raster_list[[19]],raster_list[[20]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP85_HSHV <- c(raster_list[[21]],raster_list[[22]],raster_list[[23]],raster_list[[24]],raster_list[[25]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP85_HSLV <- c(raster_list[[26]],raster_list[[27]],raster_list[[28]],raster_list[[29]],raster_list[[30]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP85_LSHV <- c(raster_list[[31]],raster_list[[32]],raster_list[[33]],raster_list[[34]],raster_list[[35]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resistance_RCP85_LSLV <- c(raster_list[[36]],raster_list[[37]],raster_list[[38]],raster_list[[39]],raster_list[[40]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
resistance_RCP45_AWB_Stack <- c(AWB_Resistance_RCP45_HSHV,AWB_Resistance_RCP45_HSLV,AWB_Resistance_RCP45_LSHV,AWB_Resistance_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Resistance")
resistance_RCP85_AWB_Stack <- c(AWB_Resistance_RCP85_HSHV,AWB_Resistance_RCP85_HSLV,AWB_Resistance_RCP85_LSHV,AWB_Resistance_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Resistance")
# Resilience
AWB_Resilience_RCP45_HSHV <- c(raster_list[[41]],raster_list[[42]],raster_list[[43]],raster_list[[44]],raster_list[[45]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP45_HSLV <- c(raster_list[[46]],raster_list[[47]],raster_list[[48]],raster_list[[49]],raster_list[[50]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP45_LSHV <- c(raster_list[[51]],raster_list[[52]],raster_list[[53]],raster_list[[54]],raster_list[[55]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP45_LSLV <- c(raster_list[[56]],raster_list[[57]],raster_list[[58]],raster_list[[59]],raster_list[[60]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP85_HSHV <- c(raster_list[[61]],raster_list[[62]],raster_list[[63]],raster_list[[64]],raster_list[[65]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP85_HSLV <- c(raster_list[[66]],raster_list[[67]],raster_list[[68]],raster_list[[69]],raster_list[[70]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP85_LSHV <- c(raster_list[[71]],raster_list[[72]],raster_list[[73]],raster_list[[74]],raster_list[[75]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Resilience_RCP85_LSLV <- c(raster_list[[76]],raster_list[[77]],raster_list[[78]],raster_list[[79]],raster_list[[80]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
resilience_RCP45_AWB_Stack <- c(AWB_Resilience_RCP45_HSHV,AWB_Resilience_RCP45_HSLV,AWB_Resilience_RCP45_LSHV,AWB_Resilience_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Resilience")
resilience_RCP85_AWB_Stack <- c(AWB_Resilience_RCP85_HSHV,AWB_Resilience_RCP85_HSLV,AWB_Resilience_RCP85_LSHV,AWB_Resilience_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Resilience")
# Transition
AWB_Transition_RCP45_HSHV <- c(raster_list[[81]],raster_list[[82]],raster_list[[83]],raster_list[[84]],raster_list[[85]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP45_HSLV <- c(raster_list[[86]],raster_list[[87]],raster_list[[88]],raster_list[[89]],raster_list[[90]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP45_LSHV <- c(raster_list[[91]],raster_list[[92]],raster_list[[93]],raster_list[[94]],raster_list[[95]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP45_LSLV <- c(raster_list[[96]],raster_list[[97]],raster_list[[98]],raster_list[[99]],raster_list[[100]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP85_HSHV <- c(raster_list[[101]],raster_list[[102]],raster_list[[103]],raster_list[[104]],raster_list[[105]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP85_HSLV <- c(raster_list[[106]],raster_list[[107]],raster_list[[108]],raster_list[[109]],raster_list[[110]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP85_LSHV <- c(raster_list[[111]],raster_list[[112]],raster_list[[113]],raster_list[[114]],raster_list[[115]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
AWB_Transition_RCP85_LSLV <- c(raster_list[[116]],raster_list[[117]],raster_list[[118]],raster_list[[119]],raster_list[[110]]) %>% app(., "mean") %>% app(., function(x) ifelse(x == 0, NA, x))
transition_RCP45_AWB_Stack <- c(AWB_Transition_RCP45_HSHV,AWB_Transition_RCP45_HSLV,AWB_Transition_RCP45_LSHV,AWB_Transition_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Transition")
transition_RCP85_AWB_Stack <- c(AWB_Transition_RCP85_HSHV,AWB_Transition_RCP85_HSLV,AWB_Transition_RCP85_LSHV,AWB_Transition_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Transition")

final_Resistance_AWB <- rbind(resistance_RCP45_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
resistance_RCP85_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))

final_Resilience_AWB <- rbind(resilience_RCP45_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
resilience_RCP85_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))

final_Transition_AWB <- rbind(transition_RCP45_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
transition_RCP85_AWB_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))

final_AWB <- rbind(final_Resilience_AWB, final_Resistance_AWB, final_Transition_AWB)



ggplot(final_Resistance_AWB) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_gradient(low = "#a8dadc", high = "#1d3557", name = "AWB") +
  theme_classic() +
  facet_wrap(RCP ~ Model, ncol = 4)

ggplot(final_Resilience_AWB) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_gradient(low = "#a8dadc", high = "#1d3557", name = "AWB") +
  theme_classic() +
  facet_wrap(RCP ~ Model, ncol = 4)

ggplot(final_Transition_AWB) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_gradient(low = "#a8dadc", high = "#1d3557", name = "AWB") +
  theme_classic() +
  facet_wrap(RCP ~ Model, ncol = 4)



ggplot(final_AWB, aes(x = Model, y = value, fill = Model)) +
  geom_violin(width = 1) +
  geom_boxplot(width = 0.05) +
  theme_classic() +
  facet_grid(RCP~Prescription)



```


### Total Carbon

```{r}
mainDir <- "D:/Landis Outputs"
scenarios <- c("Resistance", "Resilience", "Transition") # Fill in with Resilience
rcps <- c("RCP45", "RCP85")
climates <- c("HSHV", "HSLV", "LSHV", "LSLV")
runs <- paste0("run",1:5)

raster_list <- list()
for (scenario in scenarios) {
  for (rcp in rcps) {
    for (climate in climates){
      for (run in runs) {
        for (timestep in timesteps) {
          img_file <- file.path(mainDir, scenario, rcp, climate, run, paste0("TotalC-", timestep, ".img"))
          raster <- rast(img_file)
          crs(raster) <- "epsg:26917"
          raster <- flip(raster)
          ext(raster) <- ext(templateRaster)
          # raster <- project(raster, res = 70.71068, templateRaster, method = "bilinear")
          raster_list[[length(raster_list) + 1]] <- raster
        }
      }
    }
  }
}

# Resistance
TotalC_Resistance_RCP45_HSHV <- c(raster_list[[1]],raster_list[[2]],raster_list[[3]],raster_list[[4]],raster_list[[5]]) %>% app(., "mean")
TotalC_Resistance_RCP45_HSLV <- c(raster_list[[6]],raster_list[[7]],raster_list[[8]],raster_list[[9]],raster_list[[10]]) %>% app(., "mean")
TotalC_Resistance_RCP45_LSHV <- c(raster_list[[11]],raster_list[[12]],raster_list[[13]],raster_list[[14]],raster_list[[15]]) %>% app(., "mean")
TotalC_Resistance_RCP45_LSLV <- c(raster_list[[16]],raster_list[[17]],raster_list[[18]],raster_list[[19]],raster_list[[20]]) %>% app(., "mean")
TotalC_Resistance_RCP85_HSHV <- c(raster_list[[21]],raster_list[[22]],raster_list[[23]],raster_list[[24]],raster_list[[25]]) %>% app(., "mean")
TotalC_Resistance_RCP85_HSLV <- c(raster_list[[26]],raster_list[[27]],raster_list[[28]],raster_list[[29]],raster_list[[30]]) %>% app(., "mean")
TotalC_Resistance_RCP85_LSHV <- c(raster_list[[31]],raster_list[[32]],raster_list[[33]],raster_list[[34]],raster_list[[35]]) %>% app(., "mean")
TotalC_Resistance_RCP85_LSLV <- c(raster_list[[36]],raster_list[[37]],raster_list[[38]],raster_list[[39]],raster_list[[40]]) %>% app(., "mean")
resistance_RCP45_C_Stack <- c(TotalC_Resistance_RCP45_HSHV,TotalC_Resistance_RCP45_HSLV,TotalC_Resistance_RCP45_LSHV,TotalC_Resistance_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Resistance")
resistance_RCP85_C_Stack <- c(TotalC_Resistance_RCP85_HSHV,TotalC_Resistance_RCP85_HSLV,TotalC_Resistance_RCP85_LSHV,TotalC_Resistance_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Resistance")
# Resilience
TotalC_Resilience_RCP45_HSHV <- c(raster_list[[41]],raster_list[[42]],raster_list[[43]],raster_list[[44]],raster_list[[45]]) %>% app(., "mean")
TotalC_Resilience_RCP45_HSLV <- c(raster_list[[46]],raster_list[[47]],raster_list[[48]],raster_list[[49]],raster_list[[50]]) %>% app(., "mean")
TotalC_Resilience_RCP45_LSHV <- c(raster_list[[51]],raster_list[[52]],raster_list[[53]],raster_list[[54]],raster_list[[55]]) %>% app(., "mean")
TotalC_Resilience_RCP45_LSLV <- c(raster_list[[56]],raster_list[[57]],raster_list[[58]],raster_list[[59]],raster_list[[60]]) %>% app(., "mean")
TotalC_Resilience_RCP85_HSHV <- c(raster_list[[61]],raster_list[[62]],raster_list[[63]],raster_list[[64]],raster_list[[65]]) %>% app(., "mean")
TotalC_Resilience_RCP85_HSLV <- c(raster_list[[66]],raster_list[[67]],raster_list[[68]],raster_list[[69]],raster_list[[70]]) %>% app(., "mean")
TotalC_Resilience_RCP85_LSHV <- c(raster_list[[71]],raster_list[[72]],raster_list[[73]],raster_list[[74]],raster_list[[75]]) %>% app(., "mean")
TotalC_Resilience_RCP85_LSLV <- c(raster_list[[76]],raster_list[[77]],raster_list[[78]],raster_list[[79]],raster_list[[80]]) %>% app(., "mean")
resilience_RCP45_C_Stack <- c(TotalC_Resilience_RCP45_HSHV,TotalC_Resilience_RCP45_HSLV,TotalC_Resilience_RCP45_LSHV,TotalC_Resilience_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Resilience")
resilience_RCP85_C_Stack <- c(TotalC_Resilience_RCP85_HSHV,TotalC_Resilience_RCP85_HSLV,TotalC_Resilience_RCP85_LSHV,TotalC_Resilience_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Resilience")
# Transition
TotalC_Transition_RCP45_HSHV <- c(raster_list[[81]],raster_list[[82]],raster_list[[83]],raster_list[[84]],raster_list[[85]]) %>% app(., "mean")
TotalC_Transition_RCP45_HSLV <- c(raster_list[[86]],raster_list[[87]],raster_list[[88]],raster_list[[89]],raster_list[[90]]) %>% app(., "mean")
TotalC_Transition_RCP45_LSHV <- c(raster_list[[91]],raster_list[[92]],raster_list[[93]],raster_list[[94]],raster_list[[95]]) %>% app(., "mean")
TotalC_Transition_RCP45_LSLV <- c(raster_list[[96]],raster_list[[97]],raster_list[[98]],raster_list[[99]],raster_list[[100]]) %>% app(., "mean")
TotalC_Transition_RCP85_HSHV <- c(raster_list[[101]],raster_list[[102]],raster_list[[103]],raster_list[[104]],raster_list[[105]]) %>% app(., "mean")
TotalC_Transition_RCP85_HSLV <- c(raster_list[[106]],raster_list[[107]],raster_list[[108]],raster_list[[109]],raster_list[[110]]) %>% app(., "mean")
TotalC_Transition_RCP85_LSHV <- c(raster_list[[111]],raster_list[[112]],raster_list[[113]],raster_list[[114]],raster_list[[115]]) %>% app(., "mean")
TotalC_Transition_RCP85_LSLV <- c(raster_list[[116]],raster_list[[117]],raster_list[[118]],raster_list[[119]],raster_list[[110]]) %>% app(., "mean")
transition_RCP45_C_Stack <- c(TotalC_Transition_RCP45_HSHV,TotalC_Transition_RCP45_HSLV,TotalC_Transition_RCP45_LSHV,TotalC_Transition_RCP45_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP45", Prescription = "Transition")
transition_RCP85_C_Stack <- c(TotalC_Transition_RCP85_HSHV,TotalC_Transition_RCP85_HSLV,TotalC_Transition_RCP85_LSHV,TotalC_Transition_RCP85_LSLV) %>%
  as.data.frame(xy = TRUE) %>%
  `colnames<-`(c("x","y","BNU-ESM","MIROC-ESM-CHEM","MRI-CGCM3","CCSM4")) %>%
  mutate(RCP = "RCP85", Prescription = "Transition")


final_Resistance_C <- rbind(resistance_RCP45_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
  resistance_RCP85_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))

final_Resilience_C <- rbind(resilience_RCP45_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
resilience_RCP85_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))

final_Transition_C <- rbind(transition_RCP45_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"),
transition_RCP85_C_Stack %>%
  pivot_longer(cols = c("BNU-ESM":"CCSM4"), values_to = "value", names_to = "Model"))


ggplot(final_Resistance_C) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_viridis_c() +
  theme_classic() +
  facet_grid(RCP ~ Model)

ggplot(final_Resilience_C) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_viridis_c() +
  theme_classic() +
  facet_grid(RCP ~ Model)

ggplot(final_Transition_C) +
  geom_raster(aes(x = x, y = y, fill = value)) +
  scale_fill_viridis_c() +
  theme_classic() +
  facet_grid(RCP ~ Model)


rbind(final_Resistance_C, final_Resilience_C, final_Transition_C) %>%
  filter(value > 0) %>%
  aov(value ~ RCP * Prescription * Model, data = .) %>%
  summary(.)

```




```{r}
library(tidyverse)
library(terra)
library(data.table)

args <- commandArgs(trailingOnly = TRUE)
job_index <- as.numeric(args[1])

# Set up objects so that we can then run the for loop
mainDir <- "/share/tcsi/lagoodal/R/MAPS"
scenarios <- c("Resistance", "Resilience", "Transition")
rcps <- c("RCP45", "RCP85")
climates <- c("HSHV", "HSLV", "LSHV", "LSLV")
runs <- paste0("run", 1:5)
timesteps <- seq(10, 80, 10)

# Determine scenario/rcp/climate combo
combo_df <- expand.grid(Scenario = scenarios, RCP = rcps, Climate = climates)
this_combo <- combo_df[job_index, ]
scenario <- as.character(this_combo$Scenario)
rcp <- as.character(this_combo$RCP)
climate <- as.character(this_combo$Climate)

cat("Processing combo:", scenario, rcp, climate, "\n")

# For loop to calculate the weighte biomass of fruit and nut bearing trees
strList <- list()

for (run in runs) {
  for (year in timesteps) {
    runDir <- file.path(mainDir, scenario, rcp, climate, paste0("run", run))
    filePath <- file.path(runDir, paste0("community-input-file-", year, ".csv"))
    
    if (file.exists(filePath)) {
      strData <- data.table::fread(filePath)
      
      df <- strData %>%
        filter((SpeciesName == "CAAL27" & CohortAge >= 25) |
                 (SpeciesName == "CAGL8" & CohortAge >= 30) |
                 (SpeciesName == "QUAL" & CohortAge >= 30) |
                 (SpeciesName == "QUCO2" & CohortAge >= 30) |
                 (SpeciesName == "QUFA" & CohortAge >= 25) |
                 (SpeciesName == "QULA3" & CohortAge >= 35) |
                 (SpeciesName == "QUNI" & CohortAge >= 35) |
                 (SpeciesName == "QUPR2" & CohortAge >= 25) |
                 (SpeciesName == "QUPH" & CohortAge >= 35) |
                 (SpeciesName == "QURU" & CohortAge >= 25) |
                 (SpeciesName == "QUST" & CohortAge >= 35) |
                 (SpeciesName == "QUVE" & CohortAge >= 25)) %>%
  group_by(SpeciesName, CohortAge, Run, Time) %>%
  summarise(CohortBiomass = sum(CohortBiomass), .groups = "drop") %>%
  mutate(Weight = CohortAge / max(CohortAge, na.rm = TRUE)) %>%
  mutate(WeightedBiomass = CohortBiomass * Weight) %>%
  ungroup() %>%
  group_by(Time, Run) %>%
  summarise(Score = sum(WeightedBiomass), .groups = "drop")
      
      df$Scenario <- scenario
      df$RCP <- rcp
      df$Climate <- climate
      
      strList[[length(strList) + 1]] <- df
    }
  }
}

strDf <- bind_rows(strList)

# Make a for loop to assign the fruit/nut tree ecosystem service tree to the indiviudal
# cells within the raster. Check to make sure they all assigned properly
strRasters <- list()

for (run in runs) {
  for (timestep in timesteps) {
    rasterPath <- file.path(mainDir, scenario, rcp, climate, paste0("run", run), paste0("output-community-", timestep, ".img"))
    rasterRun <- rast(rasterPath) %>% flip()
    dfRun <- strDf %>%
      filter(Run == run, Time == timestep) %>%
      mutate(MapCode = as.numeric(MapCode))
    rasterFruit <- subst(rasterRun, from = dfRun$MapCode, to = dfRun$Score)
    
    # medianValue <- median(values(rasterRaster), na.rm = TRUE)
    # rasterH <- ifel(rasterH > 3, medianValue, rasterH)
    
    name <- paste(scenario, rcp, climate, paste0("run", run), timestep, sep = "_")
    strRasters[[name]] <- rasterH
  }
}

# Calculate the mean score for each cell across all runs for each raster
meanRasters <- list()
raster_names <- names(strRasters)
group_keys <- gsub("_run[0-9]+", "", raster_names) # Create groupings based on prescription, rcp, climate and timestep
unique_keys <- unique(group_keys)

for (key in unique_keys) {
  matched_rasters <- strRasters[which(group_keys == key)] # Grab the 5 runs for each model scenario
  raster_stack <- rast(matched_rasters)
  mean_raster <- app(raster_stack, mean, na.rm = TRUE)
  meanRasters[[key]] <- mean_raster
}

# Write the raster out
writeRaster(meanRasters[[key]], file = '/share/tcsi/lagoodal/R/Outputs/Structural_Diversity_Maps/',
            NAflag = 0, overwrite = TRUE, datatype = "FLT4S")





```



















