---
title: "Untitled"
output: pdf_document
date: "2025-10-09"
---

```{r, warning = FALSE, message = FALSE}
library(tidyverse)
library(terra)
library(sf)
library(educate)
library(AICcmodavg)
library(glmmTMB)
library(DHARMa)
library(performance)
options(scipen = 999)
templateRaster <- rast("D:/Landis Outputs/Raster Template/templateRaster.tif")
Piedmont.shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedPiedmont.shp")
```

# Exploratory Analysis Plots
## 

```{r}
directory <- "D:/Hurricane_LANDIS"
climates <- c("HINT", "NORM")
scenarios <- c("HSLV", "LSLV")
prescriptions <- c("Resilience", "Resistance", "Transition")
runs <- paste0("run", 1:3)

dfList <- list()

for (climate in climates) {
  for (scenario in scenarios) {
    for (prescription in prescriptions) {
      for (run in runs) {
        filePath <- file.path(directory, climate, scenario, prescription, run)
        csvPath <- file.path(filePath, "hurricane-events-log.csv")
        
        if (!file.exists(csvPath)) {
          message("Skipping (file not found): ", csvPath)
          next
        }
        
        # only runs if the file exists
        df <- read_csv(csvPath)
        df$RCP <- climate
        df$Model <- scenario
        df$Prescription <- prescription
        df$Run <- run
        df <- df[-12]
        
        name <- paste(climate, scenario, prescription, run, sep = "_")
        dfList[[name]] <- df
        message("Read file: ", csvPath)
        gc()
      }
    }
  }
}

hurricaneDf <- do.call(bind_rows, dfList)

# The mortality values in this table are in Tg (1 Tg is 1 million metric tons (Mg))
hurricaneDf <- hurricaneDf %>% mutate(Scenario = paste(Model, RCP, sep = "_"))

# # Zero Inflated Model
# m_zi_tweedie <- glmmTMB(
#   BiomassMortality ~ LandfallMaxWindSpeed,
#   ziformula = ~1,  # or ~ LandfallMaxWindSpeed if you suspect zeros vary with wind
#   family = tweedie(link = "log"),
#   data = hurricaneDf
# )
# summary(m_zi_tweedie)
# 
# res <- simulateResiduals(m_zi_tweedie)
# plot(res)
# testDispersion(res)
# testZeroInflation(res)
# 
# newdat <- data.frame(LandfallMaxWindSpeed = seq(min(hurricaneDf$LandfallMaxWindSpeed),
#                                                 max(hurricaneDf$LandfallMaxWindSpeed), length = 100))
# 
# # predicted mean biomass mortality including zero-inflation
# newdat$pred <- predict(m_zi_tweedie, newdata = newdat, type = "response")
# 
# ggplot(hurricaneDf, aes(LandfallMaxWindSpeed, BiomassMortality)) +
#   geom_point(alpha = 1) +
#   geom_line(data = newdat, aes(y = pred), color = "firebrick1", size = 1.2, linetype = "solid") +
#   labs(x = "Max Wind Speed (km/h)", y = "Biomass Mortality (Tg)") +
#   theme_classic()

# ggsave(width = 10, height = 6, dpi = 300,
#        filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Hurricane_Mortality.png")

hurricaneDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Prescription, Model, RCP) %>%
  summarise(Total_Mortality = sum(BiomassMortality), .groups = "drop") %>%
  group_by(Prescription, Model, RCP) %>%
  summarise(Total_Mortality = mean(Total_Mortality), .groups = "drop") %>%
  ggplot(., aes(x = Prescription, y = Total_Mortality, fill = Prescription)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_fill_manual(values = c("#66c2a5","#fc8d62","#542788")) +
  scale_y_continuous(name = "Total Biomass Mortality (Pg)", breaks = seq(0,3e3,1e3), labels = seq(0,3,1))

# Cumulative biomass mortality bar plot with SE errorbars
hurricaneDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Prescription, Model, RCP, Run) %>%
  summarise(Total_Mortality = sum(BiomassMortality), .groups = "drop") %>%
  group_by(Prescription, Model, RCP) %>%
  summarise( n_runs = n(), Sum_Total = sum(Total_Mortality), SD_runs  = sd(Total_Mortality), SE_sum   = SD_runs * sqrt(n_runs), .groups = "drop") %>%
  ggplot(., aes(x = Prescription, y = Sum_Total, fill = Prescription)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Sum_Total - SE_sum, ymax = Sum_Total + SE_sum), width = 0.2, linewidth = 0.6) +
  facet_grid(RCP ~ Model) +
  theme_classic() +
  scale_fill_manual(values = c("#66c2a5","#fc8d62","#542788")) +
  scale_y_continuous(name = "Total Biomass Mortality (Pg)",breaks = seq(0, 3e3, 1e3), labels = seq(0, 3, 1))

ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Mortality_BarPlot.png")

hurricaneDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Prescription, Model, RCP, Time) %>%
  summarise(Total_Mortality = sum(BiomassMortality), .groups = "drop") %>%
  group_by(Prescription, RCP, Model) %>%
  arrange(Prescription, RCP, Model, Time) %>%
  mutate(CumulativeMortality = cumsum(Total_Mortality), Scenario = paste(Prescription, Model, RCP, sep = "_")) %>%
  ggplot(., aes(x = Time, y = CumulativeMortality, col = Scenario)) +
  geom_line(size = 1) +
  theme_classic() +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Cumulative Mortality (Pg)", breaks = seq(0,3e3,1e3), labels = seq(0,3,1))
  
hurricaneDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Model, RCP, Time) %>%
  summarise(Total_Mortality = mean(BiomassMortality), .groups = "drop") %>%
  group_by(RCP, Model) %>%
  arrange(RCP, Model, Time) %>%
  mutate(CumulativeMortality = cumsum(Total_Mortality), Scenario = paste(Model, RCP, sep = "_")) %>%
  ggplot(., aes(x = Time, y = CumulativeMortality, col = Scenario)) +
  geom_line(size = 1, alpha = 1) +
  # geom_smooth() +
  theme_classic() +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Cumulative Mortality (Pg)", breaks = seq(0,3e3,1e3), labels = seq(0,3,1))

# Hurricane summary dataframe
dfList <- list()
for (climate in climates) {
  for (scenario in scenarios) {
    for (prescription in prescriptions) {
      for (run in runs) {
        filePath <- file.path(directory, climate, scenario, prescription, run)
        csvPath <- file.path(filePath, "hurricane-summary-log.csv")
        
        if (!file.exists(csvPath)) {
          message("Skipping (file not found): ", csvPath)
          next
        }
        
        # only runs if the file exists
        df <- read_csv(csvPath)
        df$RCP <- climate
        df$Model <- scenario
        df$Prescription <- prescription
        df$Run <- run
        df <- df[-3]
        
        name <- paste(climate, scenario, prescription, run, sep = "_")
        dfList[[name]] <- df
        message("Read file: ", csvPath)
      }
    }
  }
}

hurricaneSummaryDf <- do.call(rbind, dfList)

# Timeseries of hurricane events
hurricaneSummaryDf %>%
  group_by(Year, RCP, Model, Prescription) %>%
  summarise(NumberEvents = mean(NumberEvents), .groups = "drop") %>%
  ggplot(., aes(x = Year, y = NumberEvents, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model)

# Bar plot of total hurricane events by RCP, GCM, and Prescription
hurricaneSummaryDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(RCP, Model, Prescription, Year) %>%
  summarise(NumberEvents = mean(NumberEvents), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(NumberEvents = sum(NumberEvents), .groups = "drop") %>%
  ggplot(., aes(x = Model, y = NumberEvents, fill = Prescription)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(name = "Total Hurricane Events") +
  theme_classic() +
  facet_grid(~ RCP) +
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

ggsave(width = 10, height = 6, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Count_Hurricane_Events.png")

hurricaneSummaryDf %>%
  group_by(RCP, Model, Prescription, Year) %>%
  summarise(NumberEvents = mean(NumberEvents), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(NumberEvents = sum(NumberEvents), .groups = "drop")

modelColours <- c(
  "HINT_HSLV" = "#762A83",
  "HINT_LSLV" = "#B756C8",
  "NORM_HSLV" = "#407C3C",
  "NORM_LSLV" = "#6DB668"
)

hurricaneSummaryDf %>%
  group_by(Year, RCP, Model) %>%
  summarise(NumberEvents = mean(NumberEvents), .groups = "drop") %>%
  group_by(RCP, Model) %>%
  arrange(RCP, Model, Year) %>%
  mutate(CumulativeEvents = cumsum(NumberEvents), Scenario = paste(RCP, Model, sep = "_")) %>%
  ggplot(aes(x = Year, y = CumulativeEvents, colour = Scenario)) +
  geom_line(size = 1) +
  scale_colour_manual(values = modelColours) +
  theme_classic() +
  scale_x_continuous(name = "Year", breaks = seq(0, 80, 20), labels = seq(2020, 2100, 20)) +
  scale_y_continuous(name = "Cumulative Storm Events", breaks = seq(0, 30, 5), labels = seq(0, 30, 5))

ggsave(width = 10, height = 6, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Hurricane_Events.png")

hurricaneSummaryDf %>%
  group_by(Year, RCP, Model) %>%
  summarise(NumberEvents = mean(NumberEvents), .groups = "drop") %>%
  group_by(RCP, Model) %>%
  arrange(RCP, Model, Year) %>%
  mutate(CumulativeEvents = cumsum(NumberEvents), Scenario = paste(RCP, Model, sep = "_")) 


# ggsave(width = 10, height = 6, dpi = 300,
#        filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Hurricane_Timeseries.png")


hurricane_events <- hurricaneDf %>%
  # keep only events that actually affected the study area, if desired
  filter(ImpactsStudyArea) %>%                      
  group_by(RCP, Model, Prescription, Run, Time, HurricaneNumber) %>%
  summarise(MaxWS = max(LandfallMaxWindSpeed, na.rm = TRUE), .groups = "drop") %>%
  mutate(
    Hurricane_Category = case_when(
      MaxWS >= 119 & MaxWS <= 153 ~ "1",
      MaxWS >= 154 & MaxWS <= 177 ~ "2",
      MaxWS >= 178 & MaxWS <= 208 ~ "3",
      MaxWS >= 209 & MaxWS <= 251 ~ "4",
      MaxWS > 251                   ~ "5",
      TRUE                          ~ "TS"
    )
  )

# 2) If you only want hurricanes (exclude TS), filter here
hurricane_events_hurr <- hurricane_events

# A) TOTAL events per scenario (sum across runs)
counts_total <- hurricane_events %>%
  count(RCP, Model, Prescription, Hurricane_Category, name = "NumberEvents")

# B) MEAN events per run per scenario (average across runs)
counts_mean_per_run <- hurricane_events_hurr %>%
  count(Run, RCP, Model, Prescription, Hurricane_Category) %>%
  group_by(RCP, Model, Prescription, Hurricane_Category) %>%
  summarise(NumberEvents = mean(n), .groups = "drop")

counts_mean_per_run %>%  # or counts_total
  ggplot(aes(x = Model, y = NumberEvents, fill = Hurricane_Category)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_grid(~ RCP) +
  ylab("Number of Storm Events") +
  theme_classic()
  
ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Hurricane_Categories.png")





plot(Piedmont.shp[2], col = NA, border = "red", lwd = 5)

ggplot() +
  geom_sf(data = Piedmont.shp[2], fill = NA, col = "red", size = 2) +
  theme_classic() +
  theme(
    plot.background  = element_rect(fill = "transparent", color = NA),
    panel.background = element_rect(fill = "transparent", color = NA)
  )

ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Piedmont_Outline.png")
```



# Hurricane Rasters

```{r}
# Mortality rasters for loop to read in and wrangle raster data
rasterList <- list()
for (climate in climates) {
  for (scenario in scenarios) {
    for (prescription in prescriptions) {
      for (run in runs) {
        hurricaneDir <- file.path(directory, climate, scenario, prescription, run, "hurricane")
        if (!dir.exists(hurricaneDir)) {
          message("Skipping (directory not found: ", hurricaneDir)
          next
        }
        mortalityRasters <- list.files(hurricaneDir, pattern = "mortality.*\\.tif$", full.names = TRUE, ignore.case = TRUE)
        if(length(mortalityRasters) == 0) {
          message("No mortality rasters found in: ", hurricaneDir)
          next
        }
        for (rasterPath in mortalityRasters) {
          message("Reading raster: ", rasterPath)
          r <- rast(rasterPath)
          name <- paste(climate, scenario, prescription, run, names(r), sep = "_")
          names(r) <- name
          crs(r) <- crs(templateRaster)
          ext(r) <- ext(templateRaster)
          r <- r %>% flip()
          r[r == 0] <- NA
          rasterList[[name]] <- r
        }
      }
    }
  }
}

# Convert into a dataframe for plotting with ggplot
dfList <- lapply(rasterList, function(r) {
  df <- as.data.frame(r, xy = TRUE)
  names(df)[3] <- "mortality"
  nameParts <- str_split(names(r), "_")[[1]]
  RCP <- nameParts[1]
  Model <- nameParts[2]
  Prescription <- nameParts[3]
  Run <- nameParts[4]
  fileName <- nameParts[5]
  matches <- str_match(fileName, "mortality-(\\d+)-(\\d+)")
  Year <- matches[,2]
  Hurricane <- matches[,3]
  df %>% mutate(RCP=RCP, Model=Model, Prescription=Prescription, Run=Run,
                Year=as.integer(Year), Hurricane=as.integer(Hurricane))
})

# Combine all data frames into one big table
allMortalityDF <- do.call(bind_rows, dfList)

# Number of storm events per cell
allMortalityDF$Hurricane <- as.numeric(as.character(allMortalityDF$Hurricane))

gc()

x <- allMortalityDF %>%
  mutate(HurricaneEvent = ifelse(Hurricane > 0, 1, 0)) %>%
  group_by(x, y, RCP, Model, Prescription, Year) %>% 
  summarise(yearly_event = max(HurricaneEvent), .groups = "drop") %>% 
  group_by(x, y, RCP, Model, Prescription) %>%
  summarise(total_hurricanes = sum(yearly_event), .groups = "drop")


x %>%
  group_by(x, y, Model, Prescription) %>%
  summarise(hurricanes = mean(total_hurricanes, na.rm = TRUE), .groups = "drop") %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = hurricanes)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_minimal() +
  facet_grid(Prescription ~ Model)

```
df <- allMortalityDF %>%
  group_by(x, y, RCP, Model, Prescription) %>%
  summarise(avg_Hurricane = mean(Hurricane, na.rm = TRUE), .groups = "drop") %>%
  group_by(x, y, RCP, Model) %>%
  summarise(total_Hurricane = sum(avg_Hurricane), .groups = "drop")


vmin <- min(df$total_Hurricane, na.rm = TRUE)
vmax <- max(df$total_Hurricane, na.rm = TRUE)
ggplot(df) +
  geom_raster(aes(x = x, y = y, fill = total_Hurricane)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  coord_sf() +
  theme_minimal() +
  facet_grid(RCP ~ Model) +
  scale_fill_gradientn(
    colours = c("red", "red", "yellow", "dodgerblue"),
    # explicitly rescale to 0–1 across data range
    values = scales::rescale(c(vmin, 3, 4, vmax), from = c(vmin, vmax)),
    limits = c(vmin, vmax),
    oob = scales::squish,
    name = "Average Storm Events"
  )

ggplot(df) +
  geom_raster(aes(x = x, y = y, fill = total_Hurricane)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  coord_sf() +
  theme_minimal() +
  facet_grid(RCP ~ Model) +
  scale_fill_gradientn(
    colours = c("red", "yellow", "dodgerblue"),  # clean 3-color gradient
    values = scales::rescale(c(vmin, (vmin + vmax)/2, vmax), from = c(vmin, vmax)),  # make yellow the midpoint
    limits = c(vmin, vmax),
    oob = scales::squish,
    name = "Average Storm Events"
  )

df %>%
  mutate(
    Hurricane_Bin = case_when(
      total_Hurricane < 1 ~ 1,
      total_Hurricane >= 6 ~ 6,
      TRUE ~ floor(total_Hurricane)
    ) %>%
      as.character() %>%  # ✅ ensure levels are "1", "2", ..., "6"
      factor(levels = as.character(1:6))
  ) %>%
ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = Hurricane_Bin)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  coord_sf() +
  theme_minimal() +
  facet_grid(RCP ~ Model) +
  scale_fill_manual(
    values = c(
      "1" = "#d73027",
      "2" = "#f46d43",
      "3" = "#fdae61",
      "4" = "#abd9e9",
      "5" = "#74add1",
      "6" = "#4575b4"
    ),
    name = "Hurricane Category"
  )


ggsave(width = 25, height = 10, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Hurricane_Events_Map.png")


# # Mortality Map, values are Mg (metric tons), but some are really high because they
# # have been hit multiple times
df2 <- allMortalityDF %>%
  group_by(x, y, RCP, Model) %>%
  summarise(Mortality = mean(mortality, na.rm = TRUE))
# 
# 
# # Cap values for coloring (optional, used in the scale)
df2$Mortality_capped <- pmin(df2$Mortality, 1001)  # 1001 to allow red for >1000

# Plot of average mortality over the simulation period. All values > 1000 are coloured red
ggplot(df2) +
  geom_raster(aes(x = x, y = y, fill = Mortality_capped)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  coord_sf() +
  theme_minimal() +
  facet_grid(RCP ~ Model) +
  scale_fill_gradientn(
    colors = c("green", "blue", "red"),          # gradient green → blue → red
    values = scales::rescale(c(0, 1000, 1001)), # 0–1000 = gradient, >1000 = red
    limits = c(0, 1001),
    na.value = "grey80",
    guide = guide_colorbar(barheight = 10)
  ) +
  labs(fill = "Mortality")

ggsave(width = 25, height = 10, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Average_Mortality_Map.png")


hurricaneDf %>%
  group_by(RCP, Model, Prescription, Time, HurricaneNumber) %>%
  summarise(BiomassMortality = mean(BiomassMortality), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(BiomassMortality = sum(BiomassMortality)) %>%
  ggplot(., aes(x = Prescription, y = BiomassMortality, fill = Prescription)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  facet_grid(RCP ~ Model)

ggsave(width = 10, height = 6, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Total_Hurricane_Mortality.png")

hurricaneDf %>%
  group_by(RCP, Model, Prescription, Time, HurricaneNumber) %>%
  summarise(BiomassMortality = mean(BiomassMortality), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(BiomassMortality = sum(BiomassMortality)) %>%
  arrange(BiomassMortality, .by_group = TRUE)
```




```{r}
stormDf <- data.table::fread("D:/Hurricane_LANDIS/hurricaneEvents.csv")

stormDf %>%
  group_by(x, y, Model, Prescription) %>%
  summarise(hurricanes = mean(total_hurricanes), .groups = "drop") %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = hurricanes)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_minimal() +
  facet_grid(Prescription ~ Model)




x %>%
  group_by(x, y, Model, Prescription) %>%
  summarise(hurricanes = mean(total_hurricanes, na.rm = TRUE), .groups = "drop") %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = hurricanes)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_minimal() +
  facet_grid(Prescription ~ Model)

cumulativeStormDf <- data.table::fread("D:/Hurricane_LANDIS/hurricaneCumulative.csv")

cumulativeStormDf %>%
  mutate(Scenario = paste(Prescription, RCP, Model, sep = "_")) %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = total_hurricanes)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_minimal() +
  facet_wrap(~ Scenario)

```

















