---
title: "Untitled"
output: pdf_document
date: "2025-10-13"
---

```{r, messages = FALSE, warning = FALSE}
library(tidyverse)
library(data.table)
library(terra)
library(sf)
library(gt)
library(rFIA)

templateRaster <- rast("D:/Landis Outputs/Raster Template/templateRaster.tif")
softwoods <- c("JUVI","PIEC2","PIPA2","PIST","PITA","PIVI2","TAAS","TADI2")
oaks <- c("QUAL","QUCO2","QUFA","QULA3","QUNI","QUPH","QUPR2","QURU","QUST","QUVE")
hardwoods <- c("ACRU","CAAL27","CAGL8","FAGR","FRAM2","FRPE","LIST2","LITU","NYBI","NYSY","OXAR","PRSE2")
options(scipen = 999)
Piedmont.shp <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/standsraster/Clipped Shapefile/clippedPiedmont.shp")
```

# All

```{r, message = FALSE, warning = FALSE}
mainDir <- "D:/Hurricane_LANDIS"
rcps <- c("NORM", "HINT")
prescriptions <- c("Resistance", "Resilience", "Transition")
climates <- c("HSLV", "LSLV")
runs <- paste0("run", 1:3)
combinedData <- list()

for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        runDir <- file.path(mainDir, rcp, climate, prescription, run)
        filePath <- file.path(runDir, "spp-biomass-log.csv")
        if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
          }
        data <- read_csv(filePath)
        data$RCP <- rcp
        data$Model <- climate
        data$Prescription <- prescription
        data$Run <- run
        name <- paste(prescription, rcp, climate, run, sep = "_")
        combinedData[[name]] <- data
      }
    }
  }
}
finalTable <- do.call(rbind, combinedData) %>% select(-`...34`)

# Composition through time
sppAllDf <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  group_by(Time, RCP, Model, Prescription, Species, Run) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897, 24948), length.out = n()))) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", ""))

# Proportional Biomass
propSppAllDf <- finalTable %>%
  filter(NumActiveSites != 0) %>%
  select(-EcoName, -NumActiveSites) %>%
  pivot_longer(cols = c("AboveGroundBiomass_ACRU":"AboveGroundBiomass_TADI2"), names_to = "Species", values_to = "Biomass_MG") %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  group_by(Time, RCP, Model, Prescription, Species, Run) %>%
  summarise(Biomass_MG = weighted.mean(x = Biomass_MG, w = rep(c(528897,24948), length.out = n())), .groups = "drop") %>%
  mutate(FunctionalGroup = ifelse(Species %in% softwoods, "Softwoods",
                             ifelse(Species %in% oaks, "Oaks", "Hardwoods"))) %>%
  group_by(Time, RCP, Model, Prescription, Run) %>%  # regroup before totals
  mutate(TotalBiomass = sum(Biomass_MG),
         Biomass_Percent = (Biomass_MG / TotalBiomass) * 100)

# Harvesting Rates
combinedData <- list()
for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        harvestDir <- file.path(mainDir, rcp, climate, prescription, run)
        filePath <- file.path(harvestDir, "Harvest/biomass-harvest-summary-log.csv")
        if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
        }
        data <- fread(filePath)
        data<- data %>% rename("Prescription_Type" = "Prescription")
        data$RCP <- rcp
        data$Model <- climate
        data$Prescription <- prescription
        data$Run <- run
        name <- paste(prescription, rcp, climate, run, sep = "_")
        combinedData[[name]] <- data
      }
    }
  }
}

harvestTable <- do.call(rbind, combinedData) %>% select(-`V68`)

harvestAllDf <- harvestTable[,c(1,38:71)] %>%
  pivot_longer(cols = c("BiomassHarvestedMg_ACRU":"BiomassHarvestedMg_TADI2"), names_to = "Species", values_to = "Harvested_Biomass") %>%
  group_by(Time, Run, Prescription, RCP, Model, Species)  %>%
  summarise(Total_Harvest = sum(Harvested_Biomass)) %>%
  mutate(Species = str_replace(Species, "^[^_]+_", ""))

# Climate
climateData <- list()
for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        climateDir <- file.path(mainDir, rcp, climate, prescription, run)
        filePath <- file.path(climateDir, "Climate-future-input-log.csv")
        if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
        }
        data <- fread(filePath) %>% select(-28)
        data$RCP <- rcp
        data$Model <- climate
        data$Prescription <- prescription
        data$Run <- run
        name <- paste(prescription, rcp, climate, run, sep = "_")
        climateData[[name]] <- data
      }
    }
  }
}
climateDf <- do.call(rbind, climateData)
climateDf <- climateDf[,c(1,2,5,6,7,28,29,30,31)] %>%
  mutate(meanAirtemp = (min_airtemp + max_airtemp) / 2) %>%
  group_by(Year, RCP, Model, Prescription) %>%
  summarise(sumppt = sum(ppt),
            sdPpt = sd(ppt),
            airtemp = mean(meanAirtemp),
            sdTemp = sd(meanAirtemp))


#----BIODIVERSITY----#
propDiversityAllDf <- propSppAllDf %>%
  mutate(Pi = Biomass_Percent / 100,
         lnPi = log(Pi),
         PixlnPi = Pi * lnPi) %>%
  group_by(Time, RCP, Model, Prescription, Run) %>%
  summarise(H = -sum(PixlnPi, na.rm = TRUE))

#----SUCCESSION LOG VARIABLES----#
combinedData <- list()
for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        runDir <- file.path(mainDir, rcp, climate, prescription, run)
        filePath <- file.path(runDir, "NECN-succession-log.csv")
        if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
        }
        data <- fread(filePath) %>% select(-V62)
        data$RCP <- rcp
        data$Model <- climate
        data$Prescription <- prescription
        data$Run <- run
        name <- paste(prescription, rcp, climate, run, sep = "_")
        combinedData[[name]] <- data
      }
    }
  }
}

successionAllDf <- do.call(rbind, combinedData) %>% mutate(ANPP = AG_NPPC * 2)
successionAllDf <- successionAllDf %>%
  group_by(Time, RCP, Model, Run, Prescription) %>%
  summarise(across(where(is.numeric), ~ weighted.mean(x = ., w = rep(c(528897, 24948), length.out = n()))))

```



```{r}
#----TOTAL CARBON----#
combinedRasters <- list()
for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        runDir <- file.path(mainDir, rcp, climate, prescription, run)
        for (year in seq(10, 80, 10)){
          fileName <- paste0("NECN/TotalC-", year, ".img")
          filePath <- file.path(runDir, fileName)
          if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
          }
          raster <- rast(filePath) %>% flip()
          name <- paste(prescription, rcp, climate, run, year, sep = "_")
          crs(raster) <- crs(templateRaster)
          ext(raster) <- ext(templateRaster)
          # raster <- project(raster, templateRaster)
          combinedRasters[[name]] <- raster
        }
      }
    }
  }
}

# Need to split into groupings for processing
groupID <- ceiling(seq_along(combinedRasters) / 8)
groupedBy8 <- split(names(combinedRasters), groupID)

# For loop to get the landscape average of AWB for each scenario and scenario run
totalCList <- list()
for (group in groupedBy8) {
  for (i in group) {
    rasters <- rast(combinedRasters[names(combinedRasters) %in% i])
    rasters[rasters == 0] <- NA
    df <- as.data.frame(rasters, xy = FALSE)
    names(df) <- gsub(".*_(\\d+)$", "\\1", names(df))
    df <- df %>%
      pivot_longer(cols = everything(), names_to = "layer", values_to = "value") %>%
      group_by(layer) %>%
      summarise(TotalC = mean(value, na.rm = TRUE)) %>%
      mutate(filename = tools::file_path_sans_ext(basename(i))) %>%
      separate(
        filename,
        into = c("Prescription", "RCP", "Model", "Run", "Timestep"),
        sep = "_",
        fill = "right"
      )
    df <- df[,-1]
    totalCList[[basename(i)]] <- df
  }
}


totalCDf <- do.call(rbind, totalCList)
totalCDf$Timestep <- as.integer(totalCDf$Timestep)

#----ANNUAL WATER BUDGET----#
combinedRasters <- list()
for (rcp in rcps) {
  for (prescription in prescriptions) {
    for (climate in climates) {
      for (run in runs) {
        runDir <- file.path(mainDir, rcp, climate, prescription, run)
        for (year in seq(10, 80, 10)){
          fileName <- paste0("NECN/Annual-water-budget-", year, ".img")
          filePath <- file.path(runDir, fileName)
          if (!file.exists(filePath)) {
          message("Skipping (file not found: ", filePath)
          next
          }
          raster <- rast(filePath) %>% flip()
          name <- paste(prescription, rcp, climate, run, year, sep = "_")
          crs(raster) <- crs(templateRaster)
          ext(raster) <- ext(templateRaster)
          # raster <- project(raster, templateRaster)
          combinedRasters[[name]] <- raster
        }
      }
    }
  }
}


# Need to split into groupings for processing
groupID <- ceiling(seq_along(combinedRasters) / 8)
groupedBy8 <- split(names(combinedRasters), groupID)

# For loop to get the landscape average of AWB for each scenario and scenario run
awbList <- list()
for (group in groupedBy8) {
  for (i in group) {
    rasters <- rast(combinedRasters[names(combinedRasters) %in% i])
    rasters[rasters == 0] <- NA
    df <- as.data.frame(rasters, xy = FALSE)
    names(df) <- gsub(".*_(\\d+)$", "\\1", names(df))
    df <- df %>%
      pivot_longer(cols = everything(), names_to = "layer", values_to = "value") %>%
      group_by(layer) %>%
      summarise(AWB = mean(value, na.rm = TRUE)) %>%
      mutate(filename = tools::file_path_sans_ext(basename(i))) %>%
      separate(
        filename,
        into = c("Prescription", "RCP", "Model", "Run", "Timestep"),
        sep = "_",
        fill = "right"
      )
    df <- df[,-1]
    awbList[[basename(i)]] <- df
  }
}


AWBDf <- do.call(rbind, awbList)
AWBDf$Timestep <- as.integer(AWBDf$Timestep)

AWBDf %>%
  group_by(Prescription, RCP, Model, Timestep) %>%
  summarise(AWB = mean(AWB)) %>%
  ggplot(., aes(x = Timestep, y = AWB, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(Model ~ RCP) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20))

# TODO find out if the very close results are genuine or not. Techncally the results differ,
# but the difference is minute

# Cultural Trees
culturalAllDf <- read_csv("D:/Hurricane_LANDIS/Culture_Trees.csv") %>%
  mutate(RCP = case_when(
    RCP == "Climate-Change" ~ "HINT",
    TRUE ~ "NORM"
  ))

# Fruit Trees
fruitAllDf <- read_csv("D:/Hurricane_LANDIS/Fruit_Trees.csv") %>%
  mutate(RCP = case_when(
    RCP == "Climate-Change" ~ "HINT",
    TRUE ~ "NORM"
  ))

# Structural Diversity
structureAllDf <- read_csv("D:/Hurricane_LANDIS/Structural_Diversity.csv") %>%
  mutate(RCP = case_when(
    RCP == "Climate-Change" ~ "HINT",
    TRUE ~ "NORM"
  ))

gc()

```

# Plots
## Ecosystem Services


```{r}
# AGB
successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(AGB = mean(AGB * 0.01), .groups = "drop") %>%
  filter(Time > 0) %>%
  ggplot(., aes(x = Time, y = AGB, col = Prescription)) +
  geom_line(size = 1) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Aboveground Biomass (Mg/ha)") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788")) +
  theme_classic() +
  facet_grid(RCP ~ Model)

successionAllDf %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(AGB = mean(AGB * 0.01)) %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = AGB, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)

successionAllDf %>%
  filter(Time > 0) %>%
  group_by(Time, Model, RCP, Prescription) %>%
  summarise(AGB = mean(AGB * 0.01), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(AGB),
            sd = sd(AGB)) %>%
  arrange(desc(sd))

statsAGB <- successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(AGB_MgHa = mean(AGB * 0.01), .groups = "drop") %>%
  lm(AGB_MgHa ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "AGB") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_AGB.png")

# ANPP
successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  filter(Time > 0) %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(ANPP = mean(ANPP * 0.01)) %>%
  ggplot(., aes(x = Time, y = ANPP, col = Prescription)) +
  geom_line(size = 1) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "ANPP (Mg/ha)") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788")) +
  theme_classic() +
  facet_grid(RCP ~ Model)

successionAllDf %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(ANPP = mean(ANPP * 0.01)) %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = ANPP, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
successionAllDf %>%
  filter(Time > 0) %>%
  group_by(Time, Model, RCP, Prescription) %>%
  summarise(ANPP = mean(AGB * 0.01), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(ANPP),
            sd = sd(ANPP)) %>%
  arrange(desc(sd))

statsANPP <- successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(ANPP_MgHa = mean(ANPP * 0.01), .groups = "drop") %>%
  lm(ANPP_MgHa ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "ANPP") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_ANPP.png")

# AWB
AWBDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Prescription, RCP, Model, Timestep) %>%
  summarise(AWB = mean(AWB), .groups = "drop") %>%
  ggplot(., aes(x = Timestep, y = AWB, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "AWB (cm)", breaks = seq(0,100,20), labels = seq(0,100,20)) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

AWBDf %>%
  group_by(Timestep, RCP, Model, Prescription) %>%
  summarise(AWB = mean(AWB)) %>%
  filter(Timestep > 0) %>%
  pivot_wider(names_from = Timestep, values_from = AWB, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
AWBDf %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Model, RCP, Prescription) %>%
  summarise(AWB = mean(AWB), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(AWB),
            sd = sd(AWB)) %>%
  arrange(desc(sd))

statsAWB <- AWBDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Prescription, Model, RCP) %>%
  summarise(AWB_cm = mean(AWB), .groups = "drop") %>%
  lm(AWB_cm ~ Timestep * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "AWB") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 300,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_AWB.png")

# Culture Trees
culturalAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = sum(Score)) %>%
  ggplot(., aes(x = Timestep, y = Total, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Culturally Important Trees (Mg/ha)") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

culturalAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = sum(Score), .groups = "drop") %>%
  filter(Timestep > 0) %>%
  pivot_wider(names_from = Timestep, values_from = Total, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)

culturalAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = sum(Score), .groups = "drop") %>%
  filter(Timestep > 0) %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(Total),
            sd = sd(Total)) %>%
  arrange(desc(sd))

statsCultural <- culturalAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Cultural_MgHA = sum(Score)) %>%
  lm(Cultural_MgHA ~ Timestep * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "Culture") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_Culture.png")

# Fruit Trees
fruitAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = sum(Score)) %>%
  ggplot(., aes(x = Timestep, y = Total, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Fruit Bearing Trees (Mg/ha)") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

fruitAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = mean(Score)) %>%
  filter(Timestep > 0) %>%
  pivot_wider(names_from = Timestep, values_from = Total, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
fruitAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Total = mean(Score)) %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(Total),
            sd = sd(Total)) %>%
  arrange(desc(sd))

statsFruit <- fruitAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep) %>%
  summarise(Score = mean(Score * 0.01), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(Fruit_MgHA = sum(Score)) %>%
  lm(Fruit_MgHA ~ Timestep * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "Fruit-Nut") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_Fruit.png")

# H
propDiversityAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(H = mean(H), .groups = "drop") %>%
  filter(Time > 0) %>%
  ggplot(., aes(x = Time, y = H, col = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

propDiversityAllDf %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(H = mean(H)) %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = H, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
propDiversityAllDf %>%
  filter(Time > 0) %>%
  group_by(Time, Model, RCP, Prescription) %>%
  summarise(H = mean(H), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(H),
            sd = sd(H)) %>%
  arrange(desc(sd))

statsH <- propDiversityAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(H = mean(H), .groups = "drop") %>%
  lm(H ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "H") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_H.png")

# NEEC
successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(NEEC = mean(NEEC * 0.01)) %>%
  filter(Time > 0) %>%
  ggplot(., aes(x = Time, y = NEEC, col = Prescription)) +
  geom_line(size = 1) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "NEEC (Mg/ha)") +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

successionAllDf %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(NEEC = mean(NEEC * 0.01)) %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = NEEC, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
successionAllDf %>%
  filter(Time > 0) %>%
  group_by(Time, Model, RCP, Prescription) %>%
  summarise(NEEC = mean(NEEC * 0.01), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(NEEC),
            sd = sd(NEEC)) %>%
  arrange(desc(sd))

statsNEEC <- successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(NEEC_MgHa = mean(NEEC * 0.01), .groups = "drop") %>%
  lm(NEEC_MgHa ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "NEEC") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_NEEC.png")

# SOMTC
successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(SOMTC = mean(SOMTC * 0.01)) %>%
  filter(Time > 0) %>%
  ggplot(., aes(x = Time, y = SOMTC, col = Prescription)) +
  geom_line(size = 1) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "SOMTC (Mg/ha)") +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

successionAllDf %>%
  group_by(Time, RCP, Model, Prescription) %>%
  summarise(SOMTC = mean(SOMTC * 0.01)) %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = SOMTC, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
successionAllDf %>%
  filter(Time > 0) %>%
  group_by(Time, Model, RCP, Prescription) %>%
  summarise(SOMTC = mean(SOMTC * 0.01), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(SOMTC),
            sd = sd(SOMTC)) %>%
  arrange(desc(sd))

statsSOMTC <- successionAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(SOMTC_MgHa = mean(SOMTC * 0.01), .groups = "drop") %>%
  lm(SOMTC_MgHa ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "SOMTC") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_SOMTC.png")

# Structural Diversity
structureAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(RCP, Prescription, Model, Timestep) %>%
  summarise(H = mean(H)) %>%
  filter(Timestep > 0) %>%
  ggplot(., aes(x = Timestep, y = H, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "AWB", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "H") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

structureAllDf %>%
  group_by(Timestep, RCP, Model, Prescription) %>%
  summarise(H = mean(H)) %>%
  filter(Timestep > 0) %>%
  pivot_wider(names_from = Timestep, values_from = H, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
structureAllDf %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Model, RCP, Prescription) %>%
  summarise(H = mean(H), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(H),
            sd = sd(H)) %>%
  arrange(desc(sd))

statsStructure <- structureAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Prescription, Model, RCP) %>%
  summarise(H = mean(H), .groups = "drop") %>%
  lm(H ~ Timestep * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "Strucure_H") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_Strucutre_H.png")

# Total C
totalCDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(Prescription, RCP, Model, Timestep) %>%
  summarise(TotalC = mean(TotalC * 0.01)) %>%
  filter(Timestep > 0) %>%
  ggplot(., aes(x = Timestep, y = TotalC, colour = Prescription)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Total Carbon (Mg/ha)") +
  scale_color_manual(values = c("#66c2a5", "#fc8d62", "#542788"))

totalCDf %>%
  group_by(Timestep, RCP, Model, Prescription) %>%
  summarise(TotalC = mean(TotalC * 0.01)) %>%
  filter(Timestep > 0) %>%
  pivot_wider(names_from = Timestep, values_from = TotalC, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10, 2),
         T80 = round(T80, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)
  
totalCDf %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Model, RCP, Prescription) %>%
  summarise(TotalC = mean(TotalC * 0.01), .groups = "drop") %>%
  group_by(RCP, Model, Prescription,) %>%
  summarise(mean = mean(TotalC),
            sd = sd(TotalC)) %>%
  arrange(desc(sd))

statsTotalC <- totalCDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Timestep > 0) %>%
  group_by(Timestep, Prescription, Model, RCP) %>%
  summarise(TotalC_MgHa = mean(TotalC * 0.01), .groups = "drop") %>%
  lm(TotalC_MgHa ~ Timestep * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "TotalC") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_TotalC.png")

# Total Harvest
harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  # convert Mg → Tg (1 Tg = 1 000 000 Mg)
  mutate(Total_Harvest_Tg = Total_Harvest_Mg / 1e6) %>%
  ggplot(aes(x = Time, y = Total_Harvest_Tg, colour = Prescription)) +
  geom_line(size = 1) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Biomass Harvested (Tg per 10 years)", breaks = seq(0,10,2.5), labels = seq(0,10,2.5)) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_color_manual(values = c("#66c2a5","#fc8d62","#542788"))

harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  filter(Time > 0) %>%
  pivot_wider(names_from = Time, values_from = Total_Harvest_Mg, names_prefix = "T") %>%
  select(RCP, Model, Prescription, T10, T80) %>%
  mutate(T10 = round(T10 / 1e6, 2),
         T80 = round(T80 / 1e6, 2),
         Diff = round(T80 - T10, 2)) %>%
  arrange(Diff)

harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(mean_Tg = mean(Total_Harvest_Mg / 1e6, na.rm = TRUE), sd_Tg   = sd(Total_Harvest_Mg / 1e6, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(sd_Tg))

statsHarvest <- harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("LSLV", "HSLV")),
         RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  filter(Time > 0) %>%
  group_by(Time, Prescription, Model, RCP) %>%
  summarise(Total_Harvest_MgHa = mean(Total_Harvest * 0.01), .groups = "drop") %>%
  lm(Total_Harvest_MgHa ~ Time * Prescription * Model * RCP, data = .) %>%
  broom::tidy(.) %>%
  filter(p.value < 0.05) %>%
  mutate(Response = "TotalHarvest") %>%
  select(Response, term, estimate, std.error, statistic, p.value)

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Timeseries_TotalHarvest.png")


# outDir <- "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 2/Images/Final"
# cols <- rainbow(10)  # or use colorspace::qualitative_hcl(10) for nicer tones
# 
# for (i in 1:10) {
#   file_path <- file.path(outDir, paste0("PiedmontP_Plot_", i, ".png"))
#   png(filename = file_path, width = 1200, height = 800, res = 150, bg = "transparent")
#   plot(Piedmont.shp[1], col = cols[i], main = "")
#   dev.off()
# }


bind_rows(statsAGB, statsANPP, statsAWB, statsCultural, statsFruit, statsH, statsHarvest, statsNEEC, statsSOMTC, statsStructure, statsTotalC) %>%
  arrange(Response, p.value) %>%
  mutate(estimate = round(estimate, 3), std.error = round(std.error, 3), statistic = round(statistic, 2), p.value = scales::pvalue(p.value)) %>%
  gt() %>%
  tab_header(title = "Significant Model Terms Across Variables") %>%
  cols_label(
    Response = "Response Variable",
    term = "Model Term",
    estimate = "Estimate",
    std.error = "Std. Error",
    statistic = "t-value",
    p.value = "p-value"
  )

```

# Calculate harvesting rates

```{r}
counties <- c("Caswell", "Person", "Durham", "Alamance", "Orange")
acres <- c(193293, 141838, 90225, 139175, 129356)
perc_tim <- c(71, 56, 49, 51, 51)  # not used for this calculation
stumpage_value <- c(2648658, 2983370, 174205, 2574213, 1213064)
delivered_value <- c(8866736, 9934773, 846754, 7107018, 3511070)

df <- data.frame(county = counties,
                 acres = acres,
                 perc_tim = perc_tim,
                 stumpage_value = stumpage_value,
                 delivered_value = delivered_value)

stumpage_per_Mg <- 30 
df$biomass_Mg <- df$stumpage_value / stumpage_per_Mg
df$biomass_Tg <- (df$biomass_Mg / 1e6)

total_biomass_Mg <- sum(df$biomass_Mg, na.rm = TRUE)
total_biomass_Tg <- total_biomass_Mg / 1e6
avg_biomass_Mg <- mean(df$biomass_Mg, na.rm = TRUE)
avg_biomass_Tg <- avg_biomass_Mg / 1e6

tenYrTotal <- total_biomass_Tg * 10

df$biomass_per_acre_Mg <- df$biomass_Mg / df$acres
cat("\nTotal harvested biomass: ", total_biomass_Mg, "Mg (", total_biomass_Tg, "Tg)\n")
cat("Average per county: ", avg_biomass_Mg, "Mg (", avg_biomass_Tg, "Tg)\n")


harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  mutate(Total_Harvest_Tg = Total_Harvest_Mg / 1e6) %>%
  ggplot(aes(x = Time, y = Total_Harvest_Tg, colour = Prescription)) +
  geom_line(size = 1) +
  geom_hline(yintercept = tenYrTotal, linetype = "dashed", col = "firebrick", size = 1.2) +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Biomass Harvested (Tg per 10 years)", breaks = seq(0,10,2.5), labels = seq(0,10,2.5)) +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_color_manual(values = c("#66c2a5","#fc8d62","#542788"))

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Total_Harvest_HLINE.png")

harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  mutate(Total_Harvest_Tg = Total_Harvest_Mg / 1e6) %>%
  mutate(ActualHarvest = tenYrTotal,
         Ratio = Total_Harvest_Tg / ActualHarvest,
         Label = ifelse(Ratio >= 1, "ABOVE", "BELOW")) %>%
  ggplot(., aes(x = Time, y = Ratio, fill = Prescription)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_fill_manual(values = c("#66c2a5","#fc8d62","#542788"))



harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest), .groups = "drop") %>%
  group_by(Time, Prescription, RCP, Model) %>%
  summarise(Total_Harvest_Mg = mean(Total_Harvest_Mg), .groups = "drop") %>%
  mutate(Total_Harvest_Tg = Total_Harvest_Mg / 1e6,
         ActualHarvest = tenYrTotal,
         Ratio = Total_Harvest_Tg / ActualHarvest,
         Diverge_Ratio = Ratio - 1,      # deviation from 1
         Label = ifelse(Ratio >= 1, "ABOVE", "BELOW")) %>%
  ggplot(aes(x = Time, y = Diverge_Ratio, fill = Prescription)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme_classic() +
  facet_grid(RCP ~ Model) +
  scale_fill_manual(values = c("#66c2a5","#fc8d62","#542788")) +
  scale_y_continuous(labels = function(x) round(x + 1, 2), name = "Ratio")
```




```{r}
culturalDf <- culturalAllDf %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep, Run) %>%
  summarise(Score = mean(Score), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep, Run) %>%
  summarise(Total = mean(Score))

fruitDf <- fruitAllDf %>%
  group_by(SpeciesName, RCP, Prescription, Model, Timestep, Run) %>%
  summarise(Score = mean(Score), .groups = "drop") %>%
  group_by(RCP, Prescription, Model, Timestep, Run) %>%
  summarise(Total = mean(Score))

structureDf <- structureAllDf %>%
  group_by(RCP, Prescription, Model, Timestep, Run) %>%
  summarise(H = mean(H))

harvestDf <- harvestAllDf %>%
  group_by(Time, Prescription, RCP, Model, Run) %>%
  summarise(Total_Harvest = sum(Total_Harvest))

# successionAllDf %>% filter(Run == "run2")
# culturalDf %>% filter(Run == "run2")
# fruitDf %>% filter(Run == "run2")
# structureDf %>% filter(Run == "run2")
# harvestDf %>% filter(Run == "run2")
# AWBDf %>% filter(Run == "run2")
# totalCDf %>% filter(Run == "run2")
# propDiversityAllDf %>% filter(Run == "run2")


tradeoffDf <- successionAllDf %>%
  select(Time, RCP, Model, Prescription, Run, AGB, ANPP, NEEC, SOMTC) %>%
  inner_join(culturalDf, by = c("Time" = "Timestep", "RCP", "Model", "Prescription", "Run")) %>%
  rename("Cultural" = "Total") %>%
  inner_join(fruitDf, by = c("Time" = "Timestep", "RCP", "Model", "Prescription", "Run")) %>%
  rename("Fruit" = "Total") %>%
  inner_join(structureDf, by = c("Time" = "Timestep", "RCP", "Model", "Prescription", "Run")) %>%
  rename("Structure_H" = "H") %>%
  inner_join(propDiversityAllDf, by = c("Time", "RCP", "Model", "Prescription", "Run")) %>%
  inner_join(harvestDf, by = c("Time", "Prescription", "RCP", "Model", "Run")) %>%
  inner_join(AWBDf, by = c("Time" = "Timestep", "Prescription", "RCP", "Model", "Run")) %>%
  inner_join(totalCDf, by = c("Time" = "Timestep", "RCP", "Prescription", "Model", "Run")) %>%
  mutate(Benefit_AGB = (AGB - min(.$AGB)) / (max(.$AGB) - min(.$AGB)),
         Benefit_ANPP = (ANPP - min(.$ANPP)) / (max(.$ANPP) - min(.$ANPP)),
         Benefit_AWB = (AWB - min(.$AWB)) / (max(.$AWB) - min(.$AWB)),
         Benefit_CultureTrees = (Cultural - min(.$Cultural)) / (max(.$Cultural) - min(.$Cultural)),
         Benefit_FruitTrees = (Fruit - min(.$Fruit)) / (max(.$Fruit) - min(.$Fruit)),
         Benefit_H = (H - min(.$H)) / (max(.$H) - min(.$H)),
         Benefit_NEEC = 1 - (NEEC - min(.$NEEC)) / (max(.$NEEC) - min(.$NEEC)),
         Benefit_SOMTC = (SOMTC - min(.$SOMTC)) / (max(.$SOMTC) - min(.$SOMTC)),
         Benefit_StructureH = (Structure_H - min(.$Structure_H)) / (max(.$Structure_H) - min(.$Structure_H)),
         Benefit_TotalC = (TotalC - min(.$TotalC)) / (max(.$TotalC) - min(.$TotalC)),
         Benefit_TotalHarvest = (Total_Harvest - min(.$Total_Harvest)) / (max(.$Total_Harvest) - min(.$Total_Harvest)),
         
         Tradeoff_AWB_NEEC = abs(Benefit_AWB - Benefit_NEEC) * (1 / sqrt(2)),
         Tradeoff_NEEC_AWB = Tradeoff_AWB_NEEC,
         Tradeoff_AWB_SOMTC = abs(Benefit_AWB - Benefit_SOMTC) * (1 / sqrt(2)),
         Tradeoff_SOMTC_AWB = Tradeoff_AWB_SOMTC,
         Tradeoff_AWB_ANPP = abs(Benefit_AWB - Benefit_ANPP) * (1 / sqrt(2)),
         Tradeoff_ANPP_AWB = Tradeoff_AWB_ANPP,
         Tradeoff_AWB_Structure = abs(Benefit_AWB - Benefit_StructureH) * (1 / sqrt(2)),
         Tradeoff_Structure_AWB = Tradeoff_AWB_Structure,
         Tradeoff_AWB_H = abs(Benefit_AWB - Benefit_H) * (1 / sqrt(2)),
         Tradeoff_H_AWB = Tradeoff_AWB_H,
         Tradeoff_AWB_AGB = abs(Benefit_AWB - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_AWB = Tradeoff_AWB_AGB,
         Tradeoff_AWB_FruitTrees = abs(Benefit_AWB - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_AWB = Tradeoff_AWB_FruitTrees,
         Tradeoff_AWB_CultureTrees = abs(Benefit_AWB - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_AWB = Tradeoff_AWB_CultureTrees,
         Tradeoff_AWB_TotalC = abs(Benefit_AWB - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_AWB = Tradeoff_AWB_TotalC,
         Tradeoff_AWB_TotalHarvest = abs(Benefit_AWB - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_AWB = Tradeoff_AWB_TotalHarvest,
         
         Tradeoff_NEEC_SOMTC = abs(Benefit_NEEC - Benefit_SOMTC) * (1 / sqrt(2)),
         Tradeoff_SOMTC_NEEC = Tradeoff_NEEC_SOMTC,
         Tradeoff_NEEC_ANPP = abs(Benefit_NEEC - Benefit_ANPP) * (1 / sqrt(2)),
         Tradeoff_ANPP_NEEC = Tradeoff_NEEC_ANPP,
         Tradeoff_NEEC_Structure = abs(Benefit_NEEC - Benefit_StructureH) * (1 / sqrt(2)),
         Tradeoff_Structure_NEEC = Tradeoff_NEEC_Structure,
         Tradeoff_NEEC_H = abs(Benefit_NEEC - Benefit_H) * (1 / sqrt(2)),
         Tradeoff_H_NEEC = Tradeoff_NEEC_H,
         Tradeoff_NEEC_AGB = abs(Benefit_NEEC - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_NEEC = Tradeoff_NEEC_AGB,
         Tradeoff_NEEC_FruitTrees = abs(Benefit_NEEC - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_NEEC = Tradeoff_NEEC_FruitTrees,
         Tradeoff_NEEC_CultureTrees = abs(Benefit_NEEC - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_NEEC = Tradeoff_NEEC_CultureTrees,
         Tradeoff_NEEC_TotalC = abs(Benefit_NEEC - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_NEEC = Tradeoff_NEEC_TotalC,
         Tradeoff_NEEC_TotalHarvest = abs(Benefit_NEEC - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_NEEC = Tradeoff_NEEC_TotalHarvest,
         
         Tradeoff_SOMTC_ANPP = abs(Benefit_SOMTC - Benefit_ANPP) * (1 / sqrt(2)),
         Tradeoff_ANPP_SOMTC = Tradeoff_SOMTC_ANPP,
         Tradeoff_SOMTC_Structure = abs(Benefit_SOMTC - Benefit_StructureH) * (1 / sqrt(2)),
         Tradeoff_Structure_SOMTC = Tradeoff_SOMTC_Structure,
         Tradeoff_SOMTC_H = abs(Benefit_SOMTC - Benefit_H) * (1 / sqrt(2)),
         Tradeoff_H_SOMTC = Tradeoff_SOMTC_H,
         Tradeoff_SOMTC_AGB = abs(Benefit_SOMTC - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_SOMTC = Tradeoff_SOMTC_AGB,
         Tradeoff_SOMTC_FruitTrees = abs(Benefit_SOMTC - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_SOMTC = Tradeoff_SOMTC_FruitTrees,
         Tradeoff_SOMTC_CultureTrees = abs(Benefit_SOMTC - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_SOMTC = Tradeoff_SOMTC_CultureTrees,
         Tradeoff_SOMTC_TotalC = abs(Benefit_SOMTC - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_SOMTC = Tradeoff_SOMTC_TotalC,
         Tradeoff_SOMTC_TotalHarvest = abs(Benefit_SOMTC - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_SOMTC = Tradeoff_SOMTC_TotalHarvest,
         
         Tradeoff_ANPP_Structure = abs(Benefit_ANPP - Benefit_StructureH) * (1 / sqrt(2)),
         Tradeoff_Structure_ANPP = Tradeoff_ANPP_Structure,
         Tradeoff_ANPP_H = abs(Benefit_ANPP - Benefit_H) * (1 / sqrt(2)),
         Tradeoff_H_ANPP = Tradeoff_ANPP_H,
         Tradeoff_ANPP_AGB = abs(Benefit_ANPP - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_ANPP = Tradeoff_ANPP_AGB,
         Tradeoff_ANPP_FruitTrees = abs(Benefit_ANPP - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_ANPP = Tradeoff_ANPP_FruitTrees,
         Tradeoff_ANPP_CultureTrees = abs(Benefit_ANPP - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_ANPP = Tradeoff_ANPP_CultureTrees,
         Tradeoff_ANPP_TotalC = abs(Benefit_ANPP - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_ANPP = Tradeoff_ANPP_TotalC,
         Tradeoff_ANPP_TotalHarvest = abs(Benefit_ANPP - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_ANPP = Tradeoff_ANPP_TotalHarvest,
         
         Tradeoff_Structure_H = abs(Benefit_StructureH - Benefit_H) * (1 / sqrt(2)),
         Tradeoff_H_Structure = Tradeoff_Structure_H,
         Tradeoff_Structure_AGB = abs(Benefit_StructureH - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_Structure = Tradeoff_Structure_AGB,
         Tradeoff_Structure_FruitTrees = abs(Benefit_StructureH - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_Structure = Tradeoff_Structure_FruitTrees,
         Tradeoff_Structure_CultureTrees = abs(Benefit_StructureH - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_Structure = Tradeoff_Structure_CultureTrees,
         Tradeoff_Structure_TotalC = abs(Benefit_StructureH - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_Structure = Tradeoff_Structure_TotalC,
         Tradeoff_Structure_TotalHarvest = abs(Benefit_StructureH - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_Structure = Tradeoff_Structure_TotalHarvest,
         
         Tradeoff_H_AGB = abs(Benefit_H - Benefit_AGB) * (1 / sqrt(2)),
         Tradeoff_AGB_H = Tradeoff_H_AGB,
         Tradeoff_H_FruitTrees = abs(Benefit_H - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_H = Tradeoff_H_FruitTrees,
         Tradeoff_H_CultureTrees = abs(Benefit_H - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_H = Tradeoff_H_CultureTrees,
         Tradeoff_H_TotalC = abs(Benefit_H - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_H = Tradeoff_H_TotalC,
         Tradeoff_H_TotalHarvest = abs(Benefit_H - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_H = Tradeoff_H_TotalHarvest,
         
         Tradeoff_AGB_FruitTrees = abs(Benefit_AGB - Benefit_FruitTrees) * (1 / sqrt(2)),
         Tradeoff_FruitTrees_AGB = Tradeoff_AGB_FruitTrees,
         Tradeoff_AGB_CultureTrees = abs(Benefit_AGB - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_AGB = Tradeoff_AGB_CultureTrees,
         Tradeoff_AGB_TotalC = abs(Benefit_AGB - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_AGB = Tradeoff_AGB_TotalC,
         Tradeoff_AGB_TotalHarvest = abs(Benefit_AGB - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_AGB = Tradeoff_AGB_TotalHarvest,
         
         Tradeoff_FruitTrees_CultureTrees = abs(Benefit_FruitTrees - Benefit_CultureTrees) * (1 / sqrt(2)),
         Tradeoff_CultureTrees_FruitTrees = Tradeoff_FruitTrees_CultureTrees,
         Tradeoff_FruitTrees_TotalC = abs(Benefit_FruitTrees - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_FruitTrees = Tradeoff_FruitTrees_TotalC,
         Tradeoff_FruitTrees_TotalHarvest = abs(Benefit_FruitTrees - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_FruitTrees = Tradeoff_FruitTrees_TotalHarvest,
         
         Tradeoff_CultureTrees_TotalC = abs(Benefit_CultureTrees - Benefit_TotalC) * (1 / sqrt(2)),
         Tradeoff_TotalC_CultureTrees = Tradeoff_CultureTrees_TotalC,
         Tradeoff_CultureTrees_TotalHarvest = abs(Benefit_CultureTrees - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_CultureTrees = Tradeoff_CultureTrees_TotalHarvest,
         
         Tradeoff_TotalC_TotalHarvest = abs(Benefit_TotalC - Benefit_TotalHarvest) * (1 / sqrt(2)),
         Tradeoff_TotalHarvest_TotalC = Tradeoff_TotalC_TotalHarvest) %>%
  select(Time, Run, RCP, Model, Prescription,
Tradeoff_NEEC_AWB,
Tradeoff_AWB_NEEC,
Tradeoff_AWB_SOMTC,
Tradeoff_SOMTC_AWB,
Tradeoff_AWB_ANPP,
Tradeoff_ANPP_AWB,
Tradeoff_AWB_Structure,
Tradeoff_Structure_AWB,
Tradeoff_AWB_H,
Tradeoff_H_AWB,
Tradeoff_AWB_AGB,
Tradeoff_AGB_AWB,
Tradeoff_AWB_FruitTrees,
Tradeoff_FruitTrees_AWB,
Tradeoff_AWB_CultureTrees,
Tradeoff_CultureTrees_AWB,
Tradeoff_AWB_TotalC, 
Tradeoff_TotalC_AWB,
Tradeoff_AWB_TotalHarvest,
Tradeoff_TotalHarvest_AWB,
Tradeoff_NEEC_SOMTC,
Tradeoff_SOMTC_NEEC,
Tradeoff_NEEC_ANPP,
Tradeoff_ANPP_NEEC,
Tradeoff_NEEC_Structure,
Tradeoff_Structure_NEEC,
Tradeoff_NEEC_H,
Tradeoff_H_NEEC,
Tradeoff_NEEC_AGB,
Tradeoff_AGB_NEEC,
Tradeoff_NEEC_FruitTrees,
Tradeoff_FruitTrees_NEEC,
Tradeoff_NEEC_CultureTrees,
Tradeoff_CultureTrees_NEEC,
Tradeoff_NEEC_TotalC, 
Tradeoff_TotalC_NEEC,
Tradeoff_NEEC_TotalHarvest,
Tradeoff_TotalHarvest_NEEC,
Tradeoff_SOMTC_ANPP,
Tradeoff_ANPP_SOMTC,
Tradeoff_SOMTC_Structure,
Tradeoff_Structure_SOMTC,
Tradeoff_SOMTC_H,
Tradeoff_H_SOMTC,
Tradeoff_SOMTC_AGB,
Tradeoff_AGB_SOMTC,
Tradeoff_SOMTC_FruitTrees,
Tradeoff_FruitTrees_SOMTC,
Tradeoff_SOMTC_CultureTrees,
Tradeoff_CultureTrees_SOMTC,
Tradeoff_SOMTC_TotalC,
Tradeoff_TotalC_SOMTC,
Tradeoff_SOMTC_TotalHarvest,
Tradeoff_TotalHarvest_SOMTC,
Tradeoff_ANPP_Structure,
Tradeoff_Structure_ANPP,
Tradeoff_ANPP_H,
Tradeoff_H_ANPP,
Tradeoff_ANPP_AGB,
Tradeoff_AGB_ANPP,
Tradeoff_ANPP_FruitTrees,
Tradeoff_FruitTrees_ANPP,
Tradeoff_ANPP_CultureTrees,
Tradeoff_CultureTrees_ANPP,
Tradeoff_ANPP_TotalC,
Tradeoff_TotalC_ANPP,
Tradeoff_ANPP_TotalHarvest,
Tradeoff_TotalHarvest_ANPP,
Tradeoff_Structure_H,
Tradeoff_H_Structure,
Tradeoff_Structure_AGB,
Tradeoff_AGB_Structure,
Tradeoff_Structure_FruitTrees,
Tradeoff_FruitTrees_Structure,
Tradeoff_Structure_CultureTrees,
Tradeoff_CultureTrees_Structure,
Tradeoff_Structure_TotalC,
Tradeoff_TotalC_Structure,
Tradeoff_Structure_TotalHarvest,
Tradeoff_TotalHarvest_Structure,
Tradeoff_H_AGB,
Tradeoff_AGB_H,
Tradeoff_H_FruitTrees, 
Tradeoff_FruitTrees_H,
Tradeoff_H_CultureTrees, 
Tradeoff_CultureTrees_H,
Tradeoff_H_TotalC,
Tradeoff_TotalC_H,
Tradeoff_H_TotalHarvest, 
Tradeoff_TotalHarvest_H,
Tradeoff_AGB_FruitTrees,
Tradeoff_FruitTrees_AGB,
Tradeoff_AGB_CultureTrees,
Tradeoff_CultureTrees_AGB,
Tradeoff_AGB_TotalC, 
Tradeoff_TotalC_AGB,
Tradeoff_AGB_TotalHarvest,
Tradeoff_TotalHarvest_AGB,
Tradeoff_FruitTrees_CultureTrees,
Tradeoff_CultureTrees_FruitTrees,
Tradeoff_FruitTrees_TotalC,
Tradeoff_TotalC_FruitTrees,
Tradeoff_FruitTrees_TotalHarvest,
Tradeoff_TotalHarvest_FruitTrees,
Tradeoff_CultureTrees_TotalC,
Tradeoff_TotalC_CultureTrees,
Tradeoff_CultureTrees_TotalHarvest,
Tradeoff_TotalHarvest_CultureTrees,
Tradeoff_TotalC_TotalHarvest,
Tradeoff_TotalHarvest_TotalC)
```




```{r}
tradeoffDfLong <- tradeoffDf %>%
  pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
  separate(Tradeoff_Type, into = c("Prefix", "Var1", "Var2"), sep = "_") %>%
  group_by(Time, RCP, Model, Prescription, Var1, Var2) %>%
  summarise(Value = mean(Value), .groups = "drop")
```



```{r}
df <- tradeoffDf %>%
  pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
  separate(Tradeoff_Type, into = c("prefix", "Var1", "Var2"), sep = "_") %>%
  group_by(Time, Run, RCP, Model, Prescription, Var1, Var2) %>%
  summarise(Value = mean(Value)) %>%
  mutate(x = factor(Var1, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
         y = factor(Var2, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
         Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("HSLV", "LSLV"))) %>%
  group_by(Run, RCP, Model, Prescription) %>%
  summarise(total = sum(Value) / 2, .groups = "drop") %>%
  mutate(Scenario = paste(RCP, Model, Prescription, sep = "_"))


# Run the model to check significance and get post-hoc letters
model <- aov(total ~ Scenario, data = df)
tukey <- agricolae::HSD.test(model, "Scenario")
tukey_letters <- tukey$groups %>%
  rownames_to_column("Scenario") %>%
  select(Scenario, groups)

# Mean cumulative tradeoff score
df %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition")), Scenario = paste(RCP, Model, Prescription, sep = "_")) %>%
  group_by(Scenario, Prescription, Model, RCP, Run) %>%
  summarise(Total = sum(total), .groups = "drop") %>%
  group_by(Scenario, Prescription, Model, RCP) %>%
  summarise(
    n = n(),
    Total_Tradeoff = mean(Total, na.rm = TRUE),
    SD_runs = sd(Total, na.rm = TRUE),
    SE_sum = SD_runs / sqrt(n),
    .groups = "drop") %>%
  left_join(tukey_letters, by = "Scenario") %>%
  ggplot(., aes(x = Prescription, y = Total_Tradeoff, fill = Prescription)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Total_Tradeoff - SE_sum, ymax = Total_Tradeoff + SE_sum), width = 0.2, linewidth = 0.6) +
  geom_text(aes(y = Total_Tradeoff + SE_sum - 0.2 * max(Total_Tradeoff), label = groups), fontface = "bold", color = "black") +
  geom_text(aes(y = Total_Tradeoff + SE_sum + 0.22 * max(Total_Tradeoff), label = round(Total_Tradeoff, 1)), color = "black") +
  facet_grid(RCP ~ Model) +
  theme_classic() +
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#542788")) +
  scale_y_continuous(name = "Cumulative Tradeoff Score", expand = expansion(mult = c(0, 0.1)))

ggsave(width = 10, height = 6, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_All.png")

df %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition")), Scenario = paste(RCP, Model, Prescription, sep = "_")) %>%
  group_by(Prescription, Model, RCP, Run) %>%
  summarise(Total = sum(total), .groups = "drop") %>%
  group_by(Model) %>%
  summarise(
    n = n(),
    Total_Tradeoff = mean(Total, na.rm = TRUE),
    SD_runs = sd(Total, na.rm = TRUE),
    SE_sum = SD_runs / sqrt(n),
    .groups = "drop") %>%
  ggplot(., aes(x = Model, y = Total_Tradeoff, fill = Model)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Total_Tradeoff - SE_sum, ymax = Total_Tradeoff + SE_sum), width = 0.2, linewidth = 0.6) +
  theme_classic() +
  scale_y_continuous(name = "Cumulative Tradeoff Score", expand = expansion(mult = c(0, 0.1)))

df %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition")), Scenario = paste(RCP, Model, Prescription, sep = "_")) %>%
  group_by(Prescription, Model, RCP, Run) %>%
  summarise(Total = sum(total), .groups = "drop") %>%
  group_by(RCP) %>%
  summarise(
    n = n(),
    Total_Tradeoff = mean(Total, na.rm = TRUE),
    SD_runs = sd(Total, na.rm = TRUE),
    SE_sum = SD_runs / sqrt(n),
    .groups = "drop") %>%
  ggplot(., aes(x = RCP, y = Total_Tradeoff, fill = RCP)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = Total_Tradeoff - SE_sum, ymax = Total_Tradeoff + SE_sum), width = 0.2, linewidth = 0.6) +
  theme_classic() +
  scale_y_continuous(name = "Cumulative Tradeoff Score", expand = expansion(mult = c(0, 0.1)))

tradeoffDf %>%
  pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
  separate(Tradeoff_Type, into = c("prefix", "Var1", "Var2"), sep = "_") %>%
  group_by(Time, Run, RCP, Model, Prescription, Var1, Var2) %>%
  summarise(Value = mean(Value)) %>%
  mutate(x = factor(Var1, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
         y = factor(Var2, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
         Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("HSLV", "LSLV"))) %>%
  group_by(Prescription, RCP, Model) %>%
  arrange(Prescription, RCP, Model, Time) %>%
  mutate(Cumulative_Tradeoff = cumsum(Value), Scenario = paste(Prescription, Model, RCP, sep = "_")) %>%
  ggplot(., aes(x = Time, y = Cumulative_Tradeoff, col = Scenario)) +
  geom_line(size = 1) +
  theme_classic()

# Cumulative tradeoff score timeseries by Scenario
tradeoffDf %>%
  pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
  separate(Tradeoff_Type, into = c("prefix", "Var1", "Var2"), sep = "_") %>%
  group_by(Time, Run, RCP, Model, Prescription, Var1, Var2) %>%
  summarise(Value = mean(Value), .groups = "drop") %>%
  group_by(Time, Run, RCP, Model, Prescription) %>%
  summarise(Total_Tradeoff = sum(Value) / 2, .groups = "drop") %>%
  arrange(RCP, Model, Prescription, Run, Time) %>%
  group_by(Run, RCP, Model, Prescription) %>%
  mutate(Cumulative_Tradeoff = cumsum(Total_Tradeoff),
         Scenario = paste(Prescription, Model, RCP, sep = "_")) %>%
  ungroup() %>%
  group_by(Time, Scenario) %>%
  summarise(Mean_Cumulative = mean(Cumulative_Tradeoff, na.rm = TRUE), SD = sd(Cumulative_Tradeoff, na.rm = TRUE), SE = SD / sqrt(n()), .groups = "drop") %>%
  # mutate(Scenario = paste(RCP, Model, Prescription, sep = "_")) %>%
  ggplot(., aes(x = Time, y = Mean_Cumulative, color = Scenario)) +
  geom_line(linewidth = 1) +
  # geom_ribbon(aes(ymin = Mean_Cumulative - SE, ymax = Mean_Cumulative + SE, fill = Prescription), alpha = 0.2, color = NA) +
  # facet_grid(RCP ~ Model) +
  theme_classic()

# Plot of Cumulative Tradeoff Rank as a Timeseries
ranked_df <- tradeoffDf %>%
  pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
  separate(Tradeoff_Type, into = c("prefix", "Var1", "Var2"), sep = "_") %>%
  group_by(Time, Run, RCP, Model, Prescription, Var1, Var2) %>%
  summarise(Value = mean(Value), .groups = "drop") %>%
  group_by(Time, Run, RCP, Model, Prescription) %>%
  summarise(Total_Tradeoff = sum(Value) / 2, .groups = "drop") %>%
  arrange(RCP, Model, Prescription, Run, Time) %>%
  group_by(Run, RCP, Model, Prescription) %>%
  mutate(Cumulative_Tradeoff = cumsum(Total_Tradeoff),
         Scenario = paste(Prescription, Model, RCP, sep = "_")) %>%
  ungroup() %>%
  group_by(Time, Scenario) %>%
  summarise(Mean_Cumulative = mean(Cumulative_Tradeoff, na.rm = TRUE), SD = sd(Cumulative_Tradeoff, na.rm = TRUE), SE = SD / sqrt(n()), .groups = "drop") %>%
  group_by(Time) %>%
  mutate(Rank = min_rank(desc(Mean_Cumulative))) %>%
  ungroup()
final_order <- ranked_df %>%
  filter(Time == max(Time)) %>%
  arrange(Rank) %>%
  select(Scenario, Rank)
ranked_df <- ranked_df %>%
  mutate(Scenario = factor(Scenario, levels = final_order$Scenario))

ggplot(ranked_df, aes(x = Time, y = Rank, color = Scenario, group = Scenario)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  scale_y_reverse(breaks = final_order$Rank, labels = final_order$Scenario ) +
  theme_classic() +
  labs(y = "Scenario (ranked by cumulative tradeoff)", color = "Scenario") +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  theme(legend.position = "none", panel.grid.minor = element_blank(), panel.grid.major.y = element_line(linetype = "dotted", color = "gray80"))

# Timeseries plotting the change in cumulative ES tradeoffs
start_ids <- ranked_df %>%
  filter(Time == min(Time)) %>%
  arrange(Rank) %>%
  mutate(Scenario_ID = row_number()) %>%
  select(Scenario, Scenario_ID)

# 2️⃣ Join IDs back to ranked data
ranked_df <- ranked_df %>% left_join(start_ids, by = "Scenario")

# 🧩 Add legend lookup table
legend_labels <- ranked_df %>%
  filter(Time == max(Time)) %>%
  distinct(Scenario, Scenario_ID) %>%
  arrange(Scenario_ID) %>%
  mutate(Legend_Label = paste0(Scenario_ID, " = ", Scenario)) %>%
  select(Scenario, Legend_Label)

# 3️⃣ Define start and end label positions
start_labels <- ranked_df %>% group_by(Scenario) %>% slice_min(Time, with_ties = FALSE)

end_labels <- ranked_df %>% group_by(Scenario) %>% slice_max(Time, with_ties = FALSE)

ggplot(ranked_df %>% left_join(legend_labels, by = "Scenario"), aes(x = Time, y = Rank, color = Legend_Label, group = Scenario)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  geom_text(data = end_labels, aes(label = Scenario_ID), hjust = -1, vjust = 0.4, color = "black", size = 4) +
  scale_y_reverse(breaks = final_order$Rank, labels = final_order$Rank) +
  scale_color_discrete(name = "Scenario (by number)", labels = legend_labels$Legend_Label) +
  scale_x_continuous(name = "Year", breaks = seq(0, 80, 20), labels = seq(2020, 2100, 20), expand = expansion(mult = c(0.05, 0.1))) +
  theme_classic() +
  labs(y = "Cumulative Tradeoff Rankings") +
  theme(legend.position = "bottom", panel.grid.minor = element_blank(),
        panel.grid.major.y = element_line(linetype = "dotted", color = "gray80"), legend.text = element_text(size = 9))


ggsave(width = 10, height = 6, dpi = 300,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Ranked_Timeseries.png")

# Cumulative Biomass Mortality Timeseries by Scenario
hurricaneDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance","Resilience","Transition"))) %>%
  group_by(Prescription, Model, RCP, Time) %>%
  summarise(Total_Mortality = sum(BiomassMortality), .groups = "drop") %>%
  group_by(Prescription, RCP, Model) %>%
  arrange(Prescription, RCP, Model, Time) %>%
  mutate(CumulativeMortality = cumsum(Total_Mortality), Scenario = paste(Prescription, Model, RCP, sep = "_")) %>%
  ggplot(., aes(x = Time, y = CumulativeMortality, col = Scenario)) +
  geom_line(size = 1) +
  theme_classic() +
  scale_x_continuous(name = "Year", breaks = seq(0,80,20), labels = seq(2020,2100,20)) +
  scale_y_continuous(name = "Cumulative Mortality (Pg)", breaks = seq(0,3e3,1e3), labels = seq(0,3,1)) +
  facet_grid(~ RCP)

# # Merge letters with summary data
# plot_data <- df %>%
#   left_join(tukey_letters, by = "Model_RCP") %>%
#   mutate(ModelBase = Model)  # for coloring
# plot_data <- plot_data %>%
#   group_by(Model, RCP, Prescription, Model_RCP, groups) %>%
#   summarise(total = mean(total))
# 
# ggplot(plot_data, aes(x = Model, y = total, fill = Model)) +
#   geom_bar(stat = "identity") +
#   geom_text(aes(label = groups), vjust = 1.5, color = "black", fontface = "bold") +
#   geom_text(aes(label = round(total, 1)), vjust = -1, color = "black") +
#   facet_grid(RCP ~ Prescription) +
#   scale_fill_manual(values = modelColours,
#                     labels = c("BNU-ESM"="HSHV", "MIROC-ESM-CHEM"="HSLV", "MRI-CGCM3"="LSHV", "CCSM4"="LSLV", "Historical"="Historical")) +
#   theme_classic() +
#   labs(fill = "Future Scenario", x = "Model", y = "Cumulative Tradeoff Score") +
#   geom_text(aes(label = round(total, 1)), vjust = -1, color = "black") +
#   ylim(0,100)

# HEATMAP AVERAGED ACROSS PRESCRIPTION TYPE
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(Model, RCP, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop") %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(RCP ~ Model) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))


ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_Model_RCP.png")

# HEATMAP AVERAGED ACROSS RCP
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(Model, Prescription, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop")  %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition")),
         Model = factor(Model, levels = c("HSLV", "LSLV"))) %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(Model ~ Prescription) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_Prescription_Model.png")

# HEATMAP AVERAGED ACROSS GCM
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(RCP, Prescription, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(RCP ~ Prescription) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_RCP_Prescription.png")

# HEATMAP BY PRESCRIPTION
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(~ Prescription) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_Prescription.png")

# HEATMAP BY MODEL
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(Model, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop") %>%
  mutate(Model = factor(Model, levels = c("LSLV", "HSLV"))) %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(~ Model) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_Model.png")

# HEATMAP BY RCP
tradeoffDfLong %>%
  group_by(Model, RCP, Prescription, Var1, Var2) %>%
  summarise(Value = sum(Value), .groups = "drop") %>%
  group_by(RCP, Var1, Var2) %>%
  summarise(total = mean(Value), .groups = "drop") %>%
  mutate(RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  ggplot(., aes(x = Var1, y = Var2, fill = total)) +
  geom_tile() +
  geom_text(aes(label = round(total, 2)), color = "white", size = 4, na.rm = TRUE) +
  scale_fill_gradient(low = "#ade8f4", high = "#03045e", name = "Tradeoff Value") +
  facet_grid(~ RCP) +
  theme_classic() +
  scale_y_discrete(limits = rev(levels(tradeoffDfLong$Var2)))

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Heatmap_RCP.png")

# Cumulative totals by ES averaged across Prescription
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(RCP, Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(RCP ~ Model)

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Model_RCP.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(RCP, Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(total)

# Cumulative totals by ES averaged across RCP
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(Model ~ Prescription)

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Model_Prescription.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(total)

# Cumulative totals by ES averaged across Model
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, RCP, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(RCP ~ Prescription)

ggsave(width = 25, height = 10, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Prescription_RCP.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, RCP, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(total)

# CUMULATIVE TRADEOFFS BY PRESCRIPTION
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  ylab("Tradeoff Score") +
  facet_grid(~ Prescription) +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 15),
    axis.title.y = element_text(size = 20),
    axis.title.x = element_blank(),
    strip.text = element_text(size = 20),
    legend.position = "none"
  )

ggsave(width = 18, height = 8, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Prescription.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(desc(total))

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  group_by(Prescription) %>%
  summarise(Tootal = mean(total), sd = sd(total))

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1) %>%
  summarise(total = sum(total), .groups = "drop") %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(~ Prescription)

# CUMULATIVE TRADEOFFS BY MODEL
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(Model = factor(Model, levels = c("LSLV", "HSLV"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(~ Model)

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  group_by(Model) %>%
  summarise(Total = mean(total), sd = sd(total))

ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_Model.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(desc(total))

# CUMULATIVE TRADEOFFS BY RCP
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(RCP, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(RCP = factor(RCP, levels = c("NORM", "HINT"))) %>%
  ggplot(., aes(x = Var1, y = total, fill = Var1)) +
  geom_bar(stat = "identity", col = "black") +
  theme_classic() +
  facet_grid(~ RCP)

ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Tradeoff_RCP.png")

tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(RCP, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(desc(total))

# VARIABILTY PLOT
plot_data <- bind_rows(
  tradeoffDfLong %>%
    filter(Var1 != "TotalHarvest") %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(RCP, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(RCP) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITHOUT"),

  tradeoffDfLong %>%
    filter(Var1 != "TotalHarvest") %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(Prescription, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(Prescription) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITHOUT"),

  tradeoffDfLong %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(Model, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(Model) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITHOUT"),

  tradeoffDfLong %>%
    filter(Var1 != "TotalHarvest") %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(RCP, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(RCP) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITH"),

  tradeoffDfLong %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(Prescription, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(Prescription) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITH"),

  tradeoffDfLong %>%
    group_by(RCP, Model, Prescription, Var1) %>%
    summarise(total = sum(Value), .groups = "drop") %>%
    group_by(Model, Var1) %>%
    summarise(total = mean(total), .groups = "drop") %>%
    group_by(Model) %>%
    summarise(Total = mean(total), sd = sd(total)) %>%
    mutate(Type = "WITH")
) %>%
  mutate(RCP = coalesce(RCP, Prescription, Model)) %>%
  select(-Prescription, -Model) %>%
  rename(Scenario = RCP)

color_map <- c(
  "HINT" = "#08589e",
  "LSLV" = "#2b8cbe",
  "Resistance" = "#4eb3d3",
  "Transition" = "#7bccc4",
  "HSLV" = "#a8ddb5",
  "NORM" = "#ccebc5",
  "Resilience" = "#f0f9e8"
)


plot_data <- plot_data %>%
  mutate(Scenario_facet = tidytext::reorder_within(Scenario, -sd, Type))


ggplot(plot_data, aes(x = Scenario_facet, y = Total, fill = Scenario)) +
  geom_col() +
  geom_errorbar(
    aes(ymin = Total - sd, ymax = Total + sd),
    width = 0.2, linewidth = 0.6
  ) +
  scale_fill_manual(values = color_map, breaks = sort(names(color_map))) +
  facet_wrap(~Type, scales = "free_x", ncol = 1) +
  tidytext::scale_x_reordered() +
  theme_classic(base_size = 13) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "right"
  ) +
  labs(
    x = "Scenario",
    y = "Mean Tradeoff Score",
    fill = "Scenario"
  )

ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Variability_Plot.png")

# lm_df <- tradeoffDf %>%
#   mutate(Model = sub("_[^_]+$", "", Model)) %>%
#   pivot_longer(cols = starts_with("Tradeoff"), names_to = "Tradeoff_Type", values_to = "Value") %>%
#   separate(Tradeoff_Type, into = c("prefix", "Var1", "Var2"), sep = "_") %>%
#   group_by(Time, Run, RCP, Model, Prescription, Var1, Var2) %>%
#   summarise(Value = mean(Value)) %>%
#   mutate(x = factor(Var1, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
#          y = factor(Var2, levels = c("AGB","ANPP","AWB","CultureTrees","FruitTrees","H","NEEC","SOMTC","Structure","TotalC","TotalHarvest")),
#          Model = factor(Model, levels = c("LSLV", "HSLV"))) %>%
#   group_by(RCP, Model, Prescription) %>%
#   summarise(total = sum(Value) / 2, .groups = "drop") %>%
#   mutate(Scenario = paste(RCP, Model, Prescription, sep = "_"))
# 
# # Run the model to check significance and get post-hoc letters
# model <- aov(total ~ Scenario, data = lm_df)
# tukey <- agricolae::HSD.test(model, "Scenario")
# tukey_letters <- tukey$groups %>%
#   rownames_to_column("Model_RCP") %>%
#   select(Model_RCP, groups)

harvestAllDf %>%
  mutate(Prescription = factor(Prescription, levels = c("Resistance", "Resilience", "Transition"))) %>%
  group_by(RCP, Model, Prescription, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest, na.rm = TRUE), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(Mean_Harvest_Mg = mean(Total_Harvest_Mg, na.rm = TRUE), .groups = "drop") %>%
  mutate(Mean_Harvest_Tg = Mean_Harvest_Mg / 1e6) %>%
  ggplot(aes(x = Model, y = Mean_Harvest_Tg, fill = Prescription)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(name = "Total Harvest (Tg)") +
  theme_classic() +
  facet_grid(~ RCP) +
  scale_fill_manual(values = c("#66c2a5", "#fc8d62", "#542788"))


ggsave(width = 10, height = 6, dpi = 600,
       filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Cumulative_Harvest.png")

harvestAllDf %>%
  group_by(RCP, Model, Prescription, Run) %>%
  summarise(Total_Harvest_Mg = sum(Total_Harvest, na.rm = TRUE), .groups = "drop") %>%
  group_by(RCP, Model, Prescription) %>%
  summarise(Mean_Harvest_Mg = mean(Total_Harvest_Mg, na.rm = TRUE), .groups = "drop") %>%
  mutate(Mean_Harvest_Tg = Mean_Harvest_Mg / 1e6) %>%
  arrange(desc(Mean_Harvest_Tg))




```





```{r}
# CUMULATIVE TRADEOFFS BY PRESCRIPTION
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Prescription, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(desc(total))

# CUMULATIVE TRADEOFFS BY MODEL
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(Model, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  arrange(desc(total))

# CUMULATIVE TRADEOFFS BY RCP
tradeoffDfLong %>%
  group_by(RCP, Model, Prescription, Var1) %>%
  summarise(total = sum(Value), .groups = "drop") %>%
  group_by(RCP, Var1) %>%
  summarise(total = mean(total), .groups = "drop") %>%
  mutate(RCP = factor(RCP, levels = c("NORM", "HINT")))

```

# Maps

```{r}
directory <- "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/LISA"
files <- list.files(directory, pattern = "_top25\\.csv$", full.names = TRUE)
dfList <- list()
for (file in files) {
  df <- data.table::fread(file)
  name <- basename(file)
  name <- sub("^([^_]*_[^_]*_[^_]*).*$", "\\1", name)
  df$Scenario <- name
  dfList[[name]] <- df
}

mapsDf <- bind_rows(dfList)


ggplot(mapsDf) +
  geom_sf(data = Piedmont.shp, fill = "grey95", color = "black", linewidth = 0.3) +
  geom_raster(aes(x = x, y = y, fill = orig_value)) +
  scale_fill_viridis_c(name = "Tradeoff Score") +
  facet_wrap(~ Scenario, ncol = 4) +
  theme_classic() +
  theme(strip.text = element_text(size = 12, face = "bold"))

ggsave(width = 15, height = 10, dpi = 600,
      filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Images/Final_Cumulative_Maps.png")




shapefile <- st_read("C:/Users/lagoodal/Desktop/Ecoregion Level 3 Full/Full/nc_eco_l3.shp") %>% st_transform(., crs = crs(templateRaster))
plot(shapefile[1], col = NA, border = c("black", "black", "black", "black"))







n <- nrow(shapefile)

# generate distinct colors
border_cols <- rainbow(n)

plot(shapefile[1], border = border_cols, lwd = 2)

```
cumulativeStormDf <- data.table::fread("D:/Hurricane_LANDIS/hurricaneCumulative.csv")

cumulativeStormDf %>%
  mutate(Scenario = paste(Prescription, RCP, Model, sep = "_")) %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = total_hurricanes)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_classic() +
  facet_wrap(~ Scenario)

# windSpeedDf <- data.table::fread("D:/Hurricane_LANDIS/windspeedsDf.csv") %>%
#   separate(Scenario, into = c("Prescription", "Model", "RCP"), sep = "_") %>%
#   mutate(Scenario = paste(Prescription, RCP, Model, sep = "_"))


ggplot(windSpeedDf) +
  geom_raster(aes(x = x, y = y, fill = windspeed)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_classic() +
  facet_wrap(~ Scenario)

cumulativeStormDf %>%
  mutate(Scenario = paste(Prescription, RCP, Model, sep = "_")) %>%
  inner_join(windSpeedDf, by = c("x", "y", "Scenario")) %>%
  filter(windspeed >= 209) %>%
  ggplot(.) +
  geom_raster(aes(x = x, y = y, fill = windspeed)) +
  geom_sf(data = Piedmont.shp, fill = NA, color = "black", linewidth = 0.4) +
  scale_fill_viridis_c() +
  coord_sf() +
  theme_classic() +
  facet_wrap(~ Scenario)
  

#   
# hurricane_events <- hurricaneDf %>%
#   # keep only events that actually affected the study area, if desired
#   filter(ImpactsStudyArea) %>%                      
#   group_by(RCP, Model, Prescription, Run, Time, HurricaneNumber) %>%
#   summarise(MaxWS = max(LandfallMaxWindSpeed, na.rm = TRUE), .groups = "drop") %>%
#   mutate(
#     Hurricane_Category = case_when(
#       MaxWS >= 119 & MaxWS <= 153 ~ "1",
#       MaxWS >= 154 & MaxWS <= 177 ~ "2",
#       MaxWS >= 178 & MaxWS <= 208 ~ "3",
#       MaxWS >= 209 & MaxWS <= 251 ~ "4",
#       MaxWS > 251                   ~ "5",
#       TRUE                          ~ "TS"
#     )
#   )
# 
#   
```

































