---
title: "Stands Map"
output: pdf_document
date: "2024-11-12"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
templateRaster <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Three_Counties_Rasters/templateRaster.tif")
```



```{r}
# Read in 3 counties shapefile and the HUC 12 watershed of NC
threeCounties.Shp <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Three_Counties_Rasters/Shapefile/threeCounties.shp")
watershedsHUC <- st_read("C:/Users/lagoodal/Desktop/All Raster Layers/HUC 8 Watersheds/Shape/WBDHU12.shp")

# Project the shapefile to the watershed shapefile, then crop and mask
threeCounties.Shp <- threeCounties.Shp %>%
  st_transform(., crs = crs(watershedsHUC))
watershedsHUC <- watershedsHUC %>%
  st_crop(., threeCounties.Shp) %>%
  st_intersection(., threeCounties.Shp)

# Add in county borders to act as extra stand divisions which will then
# match our future management areas
countiesNC <- st_read("C:/Users/lagoodal/Desktop/nc_eco_l3/North_Carolina_State_and_County_Boundary_Polygons.shp")
threeCounties <- countiesNC %>%
  st_as_sf() %>%
  filter(County %in% c("Anson", "Montgomery", "Richmond")) %>%
  st_transform(., crs = crs(watershedsHUC))
watershedsHUC <- watershedsHUC %>% st_intersection(., threeCounties)


plot(watershedsHUC[12])
plot(threeCounties[2])

# st_write(threeCounties[2],
#          dsn = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Shapefiles/ThreeCounties.shp")
```



```{r}
# Create a shapefile that has the major roads in the 3 county region, which is
# also bounded by the 3 counties border
roadsNC <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Data/County Roads/State_Maintained_Roads.shp")
roadsNC <- roadsNC[2]
threeCounties.Shp <- threeCounties.Shp %>% st_transform(., crs = crs(roadsNC))
intersection_result <- st_intersection(roadsNC, threeCounties.Shp)
plot(intersection_result)


# st_write(intersection_result[2],
#          dsn = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Shapefiles/roadsTC.shp")

```


# Bring back from QGIS

```{r}
ManagementAreaRast <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment OG/Harvest/ManagementAreas4.tif")
standsTC <- st_read("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Shapefiles/standsTC.shp") %>%
  st_transform(., crs = "EPSG:26917") %>%
  mutate(StandID = 1:nrow(.))
plot(standsTC[7])

templateRaster <- rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/Three_Counties_Rasters/templateRaster.tif")

standRast <- rasterize(standsTC, templateRaster, field = "StandID")

# Now some more stands are straddling two management areas
# Stand 1291
x <- ifel(standRast == 1291, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 4)
ManagementAreaRast[527,810] <- 2
ManagementAreaRast[529,806] <- 2
ManagementAreaRast[529,820] <- 2
ManagementAreaRast[529,828] <- 2
ManagementAreaRast[530,806] <- 2
ManagementAreaRast[530,812] <- 2
ManagementAreaRast[530,813] <- 2
ManagementAreaRast[531,810] <- 2
ManagementAreaRast[531,811] <- 2
ManagementAreaRast[532,801] <- 2
ManagementAreaRast[532,807] <- 2
ManagementAreaRast[532,810] <- 2
ManagementAreaRast[533,800] <- 2
ManagementAreaRast[534,800] <- 2
ManagementAreaRast[534,821] <- 2
ManagementAreaRast[534,822] <- 2
ManagementAreaRast[534,829] <- 2
ManagementAreaRast[535,799] <- 2
ManagementAreaRast[535,800] <- 2
ManagementAreaRast[535,814] <- 2
ManagementAreaRast[535,823] <- 2
ManagementAreaRast[535,832] <- 2
ManagementAreaRast[535,838] <- 2
ManagementAreaRast[536,792] <- 2
ManagementAreaRast[536,802] <- 2
ManagementAreaRast[536,803] <- 2
ManagementAreaRast[536,814] <- 2
ManagementAreaRast[536,816] <- 2
ManagementAreaRast[536,831] <- 2
ManagementAreaRast[536,837] <- 2
ManagementAreaRast[536,839] <- 2
ManagementAreaRast[536,843] <- 2
ManagementAreaRast[537,791] <- 2
ManagementAreaRast[537,802] <- 2
ManagementAreaRast[537,810] <- 2
ManagementAreaRast[538,810] <- 2
ManagementAreaRast[538,819] <- 2
ManagementAreaRast[539,802] <- 2
ManagementAreaRast[539,803] <- 2
ManagementAreaRast[539,822] <- 2
ManagementAreaRast[540,787] <- 2
ManagementAreaRast[540,796] <- 2
ManagementAreaRast[540,802] <- 2
ManagementAreaRast[540,813] <- 2
ManagementAreaRast[540,836] <- 2
ManagementAreaRast[541,805] <- 2
ManagementAreaRast[541,812] <- 2
ManagementAreaRast[542,812] <- 2
ManagementAreaRast[542,818] <- 2
ManagementAreaRast[542,822] <- 2
ManagementAreaRast[543,797] <- 2
ManagementAreaRast[543,814] <- 2
ManagementAreaRast[543,824] <- 2
ManagementAreaRast[543,825] <- 2
ManagementAreaRast[543,831] <- 2
ManagementAreaRast[543,835] <- 2
ManagementAreaRast[543,837] <- 2
ManagementAreaRast[544,786] <- 2
ManagementAreaRast[544,811] <- 2
ManagementAreaRast[544,834] <- 2
ManagementAreaRast[545,784] <- 2
ManagementAreaRast[545,810] <- 2
ManagementAreaRast[546,835] <- 2
ManagementAreaRast[547,788] <- 2
ManagementAreaRast[547,817] <- 2
ManagementAreaRast[547,818] <- 2
ManagementAreaRast[547,830] <- 2
ManagementAreaRast[548,817] <- 2
ManagementAreaRast[548,819] <- 2
ManagementAreaRast[549,788] <- 2
ManagementAreaRast[549,804] <- 2
ManagementAreaRast[549,821] <- 2
ManagementAreaRast[549,829] <- 2
ManagementAreaRast[549,830] <- 2
ManagementAreaRast[549,831] <- 2
ManagementAreaRast[549,833] <- 2
ManagementAreaRast[550,803] <- 2
ManagementAreaRast[550,817] <- 2
ManagementAreaRast[550,823] <- 2
ManagementAreaRast[551,788] <- 2
ManagementAreaRast[551,804] <- 2
ManagementAreaRast[551,811] <- 2
ManagementAreaRast[551,827] <- 2
ManagementAreaRast[552,810] <- 2
ManagementAreaRast[552,818] <- 2
ManagementAreaRast[552,825] <- 2
ManagementAreaRast[552,828] <- 2
ManagementAreaRast[553,809] <- 2
ManagementAreaRast[553,822] <- 2
ManagementAreaRast[553,824] <- 2
ManagementAreaRast[554,787] <- 2
ManagementAreaRast[554,798] <- 2
ManagementAreaRast[554,826] <- 2
ManagementAreaRast[555,826] <- 2
ManagementAreaRast[556,818] <- 2
ManagementAreaRast[556,822] <- 2
ManagementAreaRast[556,824] <- 2
ManagementAreaRast[556,826] <- 2
ManagementAreaRast[557,801] <- 2
ManagementAreaRast[557,824] <- 2
ManagementAreaRast[558,786] <- 2
ManagementAreaRast[558,800] <- 2
ManagementAreaRast[558,816] <- 2
ManagementAreaRast[558,817] <- 2
ManagementAreaRast[559,785] <- 2
ManagementAreaRast[560,800] <- 2
ManagementAreaRast[563,815] <- 2
ManagementAreaRast[564,790] <- 2
ManagementAreaRast[564,814] <- 2
ManagementAreaRast[565,802] <- 2
ManagementAreaRast[566,804] <- 2

writeRaster(ManagementAreaRast,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment OG/Harvest/ManagementAreas4.tif",
            datatype = "INT1U",
            NAflag = 0,
            overwrite = TRUE)

```

# I need to edit some of the stands because they are straddling two different MAs
# Stand 1258
x <- ifel(standRast == 1258, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
standRast[562,482] <- 2
standRast[564,453] <- 2

# Stand 1259
x <- ifel(standRast == 1259, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 2)
standRast[564,470] <- 3

plot(standRast)
plot(ManagementAreaRast)

writeRaster(standRast,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment OG/Harvest/standRast.tif",
            NAflag = 0,
            datatype = "INT4S",
            overwrite = TRUE)


# There are some discrepancies between the stand raster and the management area raster.
# ManagementAreaRast had a few more active cells than standRast. I will sort those out now

maskStand <- !is.na(standRast)
ManagementAreaRast[!maskStand] <- NA

writeRaster(ManagementAreaRast,
            filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/ManagementAreas.tif",
            datatype = "INT1U",
            NAflag = 0,
            overwrite = TRUE)

# Now some more stands are straddling two management areas
# Stand 1291
x <- ifel(standRast == 1291, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[526,811] <- 2
ManagementAreaRast[527,817] <- 2

# Stand 1280
x <- ifel(standRast == 1280, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[528,652] <- 2
ManagementAreaRast[528,671] <- 2
ManagementAreaRast[529,625] <- 2
ManagementAreaRast[529,674] <- 2
ManagementAreaRast[530,628] <- 2

# Stand 1283
x <- ifel(standRast == 1283, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 2)
ManagementAreaRast[528,754] <- 3
ManagementAreaRast[531,750] <- 3

# Stand 1282
x <- ifel(standRast == 1282, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[528,762] <- 2
ManagementAreaRast[529,764] <- 2

# Stand 1345
x <- ifel(standRast == 1345, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[530,704] <- 2
ManagementAreaRast[534,728] <- 2

# Stand 1298
x <- ifel(standRast == 1298, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 2)
ManagementAreaRast[521,606] <- 3
ManagementAreaRast[532,589] <- 3
ManagementAreaRast[536,583] <- 3

# Stand 1301
x <- ifel(standRast == 1301, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[557,877] <- 2
ManagementAreaRast[557,878] <- 2
ManagementAreaRast[557,879] <- 2

# Stand 1237
x <- ifel(standRast == 1237, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 2)
ManagementAreaRast[564,434] <- 3

# Stand 1184
x <- ifel(standRast == 1184, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[576,416] <- 2
ManagementAreaRast[578,412] <- 2
ManagementAreaRast[583,406] <- 2

# Stand 1153
x <- ifel(standRast == 1153, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[591,392] <- 2

# Stand 3
x <- ifel(standRast == 3, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 2)
ManagementAreaRast[564,470] <- 1

# Stand 2
x <- ifel(standRast == 2, 1, NA)
stack <- c(x, ManagementAreaRast)
df <- as.data.frame(stack, cell = TRUE) %>%
  filter(StandID == 1) %>%
  mutate(row = (cell - 1) %/% 1121 + 1,
         col = (cell - 1) %% 1121 + 1)
df %>% filter(ID == 3)
ManagementAreaRast[562,482] <- 1
ManagementAreaRast[564,453] <- 1


# writeRaster(ManagementAreaRast,
#             filename = "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/ManagementAreas.tif",
#             datatype = "INT1U",
#             NAflag = 0,
#             overwrite = TRUE)
```


```{r}
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-5.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-10.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-15.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-20.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-25.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-30.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-35.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-40.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-45.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-50.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-55.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-60.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-65.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-70.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-75.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-80.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-85.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-90.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-95.img") %>% flip())
plot(rast("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-prescripts-100.img") %>% flip())

get_position <- function(number) {
  adjusted_number <- number - 2
  set_number <- (adjusted_number %/% 3) + 1
  position_in_set <- adjusted_number %% 3 + 1
  return(list(set_number = set_number, position_in_set = position_in_set))
}

# Example usage
get_position(40)

filepath <- "C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/"
files <- list.files(filepath, pattern = "\\.img$", full.names = TRUE)
files <- files[1:20]

rasterList <- list()
for (file in files) {
  path <- file
  raster <- rast(path)
  raster <- flip(raster)
  ext(raster) <- ext(templateRaster)
  crs(raster) <- crs(templateRaster)
  rasterList[[file]] <- raster
}

results <- list()

for (i in rasterList) {
  df <- i
  df <- as.data.frame(df)
  colnames(df) <- "Prescription"
  df <- filter(df, df$Prescription > 1)
  df <- df %>% group_by(Prescription) %>% summarise(n = n())
  df <- df %>% mutate(Timestep = varnames(i))
  results[[length(results) + 1]] <- df
}

allDf <- do.call(rbind, results)
allDf$Timestep <- gsub("[^0-9]", "", allDf$Timestep)
allDf$Timestep <- as.numeric(allDf$Timestep)

prescriptionNames <- data.frame(Index = 2:88,
  Prescription = c("Thinning_1A","Thinning_1B","Thinning_1C","Thinning_2A","Thinning_2B","Thinning_2C","Thinning_3A","Thinning_3B","Thinning_3C","Thinning_4A","Thinning_4B","Thinning_4C","Thinning_5A","Thinning_5B","Thinning_5C","Thinning_OakA","Thinning_OakB","Thinning_OakC","Thinning_PineA","Thinning_PineB","Thinning_PineC","Thinning_HardwoodA","Thinning_HardwoodB","Thinning_HardwoodC","Thinning_SoftwoodA","Thinning_SoftwoodB","Thinning_SoftwoodC","PineSeedTree_A","PineSeedTree_B","PineSeedTree_C","OakSeedTree_A","OakSeedTree_B","OakSeedTree_C","HickorySeedTree_A","HickorySeedTree_B","HickorySeedTree_C","MesicHardwoodSeedTree_A","MesicHardwoodSeedTree_B","MesicHardwoodSeedTree_C","XericHardwoodSeedTree_A","XericHardwoodSeedTree_B","XericHardwoodSeedTree_C","OakShelterwood_A","OakShelterwood_B","OakShelterwood_C","PineShelterwood_A","PineShelterwood_B","PineShelterwood_C","HickoryShelterwood_A","HickoryShelterwood_B","HickoryShelterwood_C","MesicHardwoodShelterwood_A","MesicHardwoodShelterwood_B","MesicHardwoodShelterwood_C","XericHardwoodShelterwood_A","XericHardwoodShelterwood_B","XericHardwoodShelterwood_C","OakPatchcut_A","OakPatchcut_B","OakPatchcut_C", "PinePatchcut_A","PinePatchcut_B","PinePatchcut_C","HickoryPatchcut_A","HickoryPatchcut_B","HickoryPatchcut_C","MesicHardwoodPatchcut_A","MesicHardwoodPatchcut_B","MesicHardwoodPatchcut_C","XericHardwoodPatchcut_A","XericHardwoodPatchcut_B","XericHardwoodPatchcut_C","OakVDT_A","OakVDT_B","OakVDT_C","PineVDT_A","PineVDT_B","PineVDT_C","HickoryVDT_A","HickoryVDT_B","HickoryVDT_C","MesicHardwoodVDT_A","MesicHardwoodVDT_B","MesicHardwoodVDT_C","XericHardwoodVDT_A","XericHardwoodVDT_B","XericHardwoodVDT_C"))

allDf <- inner_join(prescriptionNames, allDf, by = c("Index" = "Prescription"))

sort(unique(allDf$Prescription))

allDf <- allDf %>%
  mutate(FunctionalGroup = case_when(
    grepl("Hickory", Prescription) ~ "Hickory",
    grepl("MesicHardwood", Prescription) ~ "Mesic Hardwood",
    grepl("Oak", Prescription) ~ "Oak",
    grepl("Pine", Prescription) ~ "Pine",
    grepl("XericHardwood", Prescription) ~ "Xeric Hardwood",
    grepl("Hardwood", Prescription) ~ "Hardwood",
    grepl("Softwood", Prescription) ~ "Softwood",
    TRUE ~ "Catch All"
  ),
  PrescriptionType = case_when(
    grepl("Thinning", Prescription) ~ "Thinning",
    grepl("SeedTree", Prescription) ~ "Seed Tree",
    grepl("Shelterwood", Prescription) ~ "Shelterwood",
    grepl("Patchcut", Prescription) ~ "Patchcut",
    grepl("VDT", Prescription) ~ "Variable Density Thinning",
    TRUE ~ "Catch All"
  ))

ggplot(allDf %>% filter(Timestep == 25), aes(x = reorder(Prescription, -n), y = n / 2, fill = FunctionalGroup)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Hectares") +
  ylab("Prescription") +
  facet_wrap(~Timestep)

allDf %>%
  group_by(FunctionalGroup, Timestep) %>%
  summarise(total = sum(n)) %>%
  filter(Timestep == 25) %>%
  ggplot(., aes(x = reorder(FunctionalGroup, -total), y = total, fill = FunctionalGroup)) +
  geom_bar(stat = "identity") +
  xlab("Hectares") +
  ylab("Prescription") +
  theme_classic() +
  facet_wrap(~Timestep)

allDf %>%
  group_by(PrescriptionType, Timestep) %>%
  summarise(total = sum(n)) %>%
  filter(Timestep == 25) %>%
  ggplot(., aes(x = reorder(PrescriptionType, -total), y = total, fill = PrescriptionType)) +
  geom_bar(stat = "identity") +
  xlab("Hectares") +
  ylab("Prescription") +
  theme_classic() +
  facet_wrap(~Timestep)


ggplot(allDf %>% filter(Timestep == 75), aes(x = reorder(Prescription, -n), y = n / 2, fill = FunctionalGroup)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Hectares") +
  ylab("Prescription") +
  facet_wrap(~Timestep)

allDf %>%
  group_by(FunctionalGroup, Timestep) %>%
  summarise(total = sum(n)) %>%
  filter(Timestep == 75) %>%
  ggplot(., aes(x = reorder(FunctionalGroup, -total), y = total, fill = FunctionalGroup)) +
  geom_bar(stat = "identity") +
  xlab("Hectares") +
  ylab("Prescription") +
  theme_classic() +
  facet_wrap(~Timestep)

allDf %>%
  group_by(PrescriptionType, Timestep) %>%
  summarise(total = sum(n)) %>%
  filter(Timestep == 75) %>%
  ggplot(., aes(x = reorder(PrescriptionType, -total), y = total, fill = PrescriptionType)) +
  geom_bar(stat = "identity") +
  xlab("Hectares") +
  ylab("Prescription") +
  theme_classic() +
  facet_wrap(~Timestep)




```





