---
title: "Untitled"
output: pdf_document
date: "2025-02-28"
---

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(terra)
library(sf)
options(scipen = 999)
```



```{r}
# Make a dataframe with the specific gravities
# 0.49 is the average specific gravity in the SE

sgDf <- data.frame(
  Species = c("ACRU","CAAL27","CAGL8","CAOV2","FRPE","JUVI","LIST2","LITU","NYBI","NYSY","PIEC2","PIPA2","PITA","PIVI2","QUAL","QUCO2","QUFA","QULA2","QULA3","QUMA3","QUNI","QUPR2","QURU","QUST","QUVE","TADI2"),
  specificGravity = c(0.49,0.62,0.62,0.62,0.53,0.44,0.46,0.40,0.49,0.49,0.47,0.54,0.47,0.49,0.60,0.60,0.52,0.49,0.56,0.49,0.56,0.57,0.56,0.60,0.56,0.34))

harvestDf <- read_csv("C:/Users/lagoodal/Desktop/Dissertation Stuff/Chapter 3/SOSIEL Experiment/Harvest/biomass-harvest-summary-log.csv")
harvestDf[,c(1,2,34:59)] %>%
  pivot_longer(cols = c("BiomassHarvestedMg_ACRU":"BiomassHarvestedMg_TADI2"), names_to = "Species", values_to = "Harvested_Biomass_Mg") %>%
  group_by(Time, Species, ManagementArea) %>%
  summarise(Total_Harvest = sum(Harvested_Biomass_Mg)) %>%
  mutate(Species = str_replace(Species, "^[^_]*_", "")) %>%
  inner_join(sgDf, by = "Species") %>%
  mutate(Volume_m3 = Total_Harvest / specificGravity) %>%
  ggplot(., aes(x = Time, y = Volume_m3, col = Species)) +
  geom_line(size = 1) +
  theme_classic() +
  facet_wrap(~ ManagementArea) +
  scale_y_continuous(breaks = c(0,5e5,1e6,1.5e6), labels = c(0,0.5,1,1.5), name = "Harvested in millions of m3")


# ((Anson County Delivered Value / average price of pine sawtimber in Q4 2022) * conversion to Mg) / P. taeda specific gravity
((42358600 / 30.48) * 0.907185) / 0.47
2,682,407
# Montgomery County
((35187263 / 30.48) * 0.907185) / 0.47
2,228,274
# Richmond County
((28634301 / 30.48) * 0.907185) / 0.47
1,813,300
```










# Define the tree volume (in cubic centimeters, cm³)
volume <- 500  # example value, replace with actual volume

# Define the specific gravity (SG)
SG <- 0.65  # example value, replace with actual SG

# Convert SG to basic density (g/cm³), assuming the density of water is 1 g/cm³
basic_density_from_SG <- SG * 1  # 1 g/cm³ for water

# Calculate biomass in grams
biomass_g <- volume * basic_density_from_SG

# Convert biomass from grams to megagrams (1 Mg = 1,000,000 g)
biomass_Mg <- biomass_g / 1e6

# Print the biomass in Mg
cat("Biomass (in megagrams):", biomass_Mg, "\n")


